### 2013-05-26 draft.tex
initial

% This is paper draft
% edited by Haoruo Peng
% Date: 2013.5.27
\documentclass{llncs}
\usepackage{llncsdoc}
\usepackage{amsmath, amssymb}
\usepackage{color}
\usepackage{graphicx}
\usepackage{bbding}

\newcommand{\bw}{\mathbf{w}}
\newcommand{\bwep}{\mathbf{w}^{\varepsilon}}
\newcommand{\bwfly}{\tilde{\mathbf{w}}}
\newcommand{\bwavg}{\mathbf{wavg}}
\newcommand{\bu}{\mathbf{u}}
\newcommand{\buprev}{\mathbf{uprev}}
\newcommand{\bp}{\mathbf{p}}
\newcommand{\bq}{\mathbf{q}}
\newcommand{\bxi}{\mathbf{\xi}}
\newcommand{\dotwxb}{{\mathbf{w}}^{\mathbf{T}}\mathbf{x}_{i}+b}
\newcommand{\sumt}{\sum_{t=1}^{T} }
\newcommand{\lc}{\left(}
\newcommand{\rc}{\right)}
\newcommand{\li}{\lc i\rc}
\newcommand{\lj}{\lc j\rc}
\newcommand{\tspace}{\hspace*{2em}}
\newcommand{\tspaces}{\hspace*{1.5em}}
\newcommand{\comment}{\textcolor{red}}
\newcommand{\ti}[1]{\tilde{#1}}
\newcommand{\indep}{{\;\bot\!\!\!\!\!\!\bot\;}}

\def\A{{\bf A}}
\def\a{{\bf a}}
\def\B{{\bf B}}
\def\C{{\bf C}}
\def\c{{\bf c}}
\def\D{{\bf D}}
\def\d{{\bf d}}
\def\E{{\bf E}}
\def\e{{\bf e}}
\def\f{{\bf f}}
\def\K{{\bf K}}
\def\H{{\bf H}}
\def\G{{\bf G}}
\def\I{{\bf I}}
\def\R{{\bf R}}
\def\X{{\bf X}}
\def\Y{{\bf Y}}
\def\Q{{\bf Q}}
\def\s{{\bf s}}
\def\S{{\bf S}}
\def\x{{\bf x}}
\def\y{{\bf y}}
\def\z{{\bf z}}
\def\Z{{\bf Z}}
\def\M{{\bf M}}
\def\m{{\bf m}}
\def\n{{\bf n}}
\def\U{{\bf U}}
\def\u{{\bf u}}
\def\V{{\bf V}}
\def\v{{\bf v}}
\def\W{{\bf W}}
\def\w{{\bf w}}
\def\0{{\bf 0}}
\def\1{{\bf 1}}

\def\AM{{\mathcal A}}
\def\FM{{\mathcal F}}
\def\TM{{\mathcal T}}
\def\UM{{\mathcal U}}
\def\XM{{\mathcal X}}
\def\YM{{\mathcal Y}}
\def\NM{{\mathcal N}}
\def\OM{{\mathcal O}}
\def\IM{{\mathcal I}}
\def\GM{{\mathcal G}}
\def\RB{{\mathbb R}}

\def\tx{\tilde{\bf x}}
\def\ty{\tilde{\bf y}}
\def\tz{\tilde{\bf z}}
\def\hd{\hat{d}}
\def\HD{\hat{\bf D}}
\def\hx{\hat{\bf x}}

\def\alp{\mbox{\boldmath$\alpha$\unboldmath}}
\def\bet{\mbox{\boldmath$\beta$\unboldmath}}
\def\epsi{\mbox{\boldmath$\epsilon$\unboldmath}}
\def\etab{\mbox{\boldmath$\eta$\unboldmath}}
\def\ph{\mbox{\boldmath$\phi$\unboldmath}}
\def\pii{\mbox{\boldmath$\pi$\unboldmath}}
\def\Ph{\mbox{\boldmath$\Phi$\unboldmath}}
\def\Ps{\mbox{\boldmath$\Psi$\unboldmath}}
\def\tha{\mbox{\boldmath$\theta$\unboldmath}}
\def\Tha{\mbox{\boldmath$\Theta$\unboldmath}}
\def\muu{\mbox{\boldmath$\mu$\unboldmath}}
\def\Si{\mbox{\boldmath$\Sigma$\unboldmath}}
\def\Gam{\mbox{\boldmath$\Gamma$\unboldmath}}
\def\Lam{\mbox{\boldmath$\Lambda$\unboldmath}}
\def\De{\mbox{\boldmath$\Delta$\unboldmath}}
\def\vps{\mbox{\boldmath$\varepsilon$\unboldmath}}

\def\Ncal{\mathcal{N}}
\def\argmax{\mathop{\rm argmax}}
\def\argmin{\mathop{\rm argmin}}

\def\sgn{\mathrm{sgn}}
\def\tr{\mathrm{tr}}
\def\rk{\mathrm{rank}}
\def\diag{\mathsf{diag}}
\def\vect{\mathsf{vec}}
\def\etal{{\em et al.\/}\,}

%\newtheorem{theorem}{Theorem}
%\newtheorem{lemma}{Lemma}
%\newtheorem{definition}{Definition}
%\newtheorem{proposition}{Proposition}
%\newtheorem{corollary}{Corollary}
%\newtheorem{example}{Example}

\begin{document}
\mainmatter  % start of an individual contribution

% first the title is needed
\title{Massively Parallel Learning for Penalized Logistic Regression Model}

% a short form should be given in case it is too long for the running head
\titlerunning{Massively Parallel Learning for Penalized Logistic Regression Model}

%
%\author{Haoruo Peng\inst{1, 2}  \and Ding Liang\inst{1} \and Cyrus Choi\inst{1} \and Edward Y. Chang\inst{1} \and Yin Zhao\inst{2}}
%
%\authorrunning{Haoruo Peng \and Ding Liang \and Cyrus Choi \and Edward Y. Chang \and Yin Zhao}
% (feature abused for this document to repeat the title also on left hand pages)

%\institute %
%{
%\inst{}
%HTC Research, Beijing, China 100084 \\
%\and
%\inst{}
%Department of Computer Science and Technology\\
%Tsinghua University, Beijing, China 100084
%\email{penghaoruo@hotmail.com ...}
%}
%
%\toctitle{Lecture Notes in Computer Science}
%\tocauthor{Authors' Instructions}
\maketitle

\begin{abstract}
Penalized logistic regression (PLR) is a widely used supervised learning model.
This paper addresses the issue of computational efficiency for solving PLR in big data scenario.
We focus on algorithm level and employ three different parallel computation systems with three different types of parallel algorithms to efficiently improve scalability.
Hadoop, Mahout and Spark are existing well-known parallel frameworks that can be implemented with large scale machine learning algorithms.
Parallel gradient Descent stochastic gradient descent are two existing state-of-art algorithms for parameter optimization in PLR.
We also present a novel parallel sublinear method and make a comparison between these algorithms implemented on different systems.
As the outcome shows, we claim parallel sublinear method implemented on Spark is the most computational efficient way to solve PLR for general purpose.
Moreover, fault tolerance can be provided for those lengthy distributed computations both on algorithm level and system level.
%We have released all experiment codes to open source at https://github.com/penghaoruo/PPLR.
\end{abstract}

\section{Introduction} \label{sec:int}
The penalized logistic regression (PLR) model~\cite{HastieBook:SL} plays an important role in machine learning and data mining.
The model serves for classification problems, and enjoys a substantial body of supporting theories and algorithms.
PLR is competitive with the support vector machines (SVMs) \cite{Vapnik:1998}, because it has both high accuracy and interpretability (PLR can directly estimate a conditional class probability).
Thus, a binary classification problem modeled by PLR can be easily extended to a multi-classification problem.
We will focus on the binary PLR model in the following.
A wide variety of other classification algorithms exist in the literature.
One might ask why we are motivated to use PLR for classification instead of other usual candidates.
Our motivation for exploring PLR as a fast classifier to be used in data mining applications is its maturity.
It has a statistical foundation which, in the right circumstances, could be used to extend classification results into a deeper analysis.

Recently, large-scale applications have emerged from many modern massive datasets.
A key characteristic of these applications is that the size of their training data is very large and data dimensionality is very high.
For example, in medical diagnostic applications~\cite{tsumoto2004mining}, both doctors and patients would like to take the advantage of millions of records over hundreds of attributes. More evidently, search engines on texts or multimedia data must handle data volume in the billion scale and each data instance is characterized by a feature space of thousands of dimensions~\cite{genkin2007large}.
Large data volume and high data dimensionality pose computational challenges to machine learning problems.
Especially, PLR is a widely used model in algorithms like PageRank~\cite{page1999pagerank} and Anti-spam Filtering~\cite{androutsopoulos2000evaluation}.

We tackle these challenges on algorithm level and fully exploit the benefits of parallelization.
When developing parallel algorithms for PLR, it is unavoidable to come across the question of choosing which parallel system to use and which parallel framework to employ.
After a thorough survey, we choose three unique and best-known systems to test: Hadoop~\cite{white2012hadoop}, Mahout~\cite{mahoutscalable} and Spark~\cite{zaharia2010spark}.
Hadoop uses HDFS~\cite{borthakur2008hdfs} and MapReduce~\cite{dean2008mapreduce}, Mahout runs on Apache Hadoop~\cite{gropp1999using} and make improvements in the low level code, and Spark features for iterative algorithms and also supports HDFS.
We will introduce the features of them separately in detail in related work section.

In sequential algorithms for PLR, a classical way is to turn to stochastic approximation methods.
Stochastic approximation methods, such as stochastic gradient descent~\cite{zhang2004solving} and stochastic dual averaging~\cite{xiao2010dual}, obtain optimal generalization guarantees with only a single pass or a small number of passes over the data.
Therefore, they can achieve a desired generalization with runtime linear to the dataset size.
A best-known method of those is stochastic gradient descent. This works in an online fashion. We view the sampled data points as the come-in data stream. It is extremely hard to parallelize, but it is blazingly fast.
If we take a step back and go back to the general gradient descent to solve PLR, we can find that it can be actually embarrassingly parallel. We can take in all the data at the same iteration and just compute the gradient in a Map-Reduce fashion.
We can further speed up the runtime by employing sublinear algorithms~\cite{peng2012sublinear} for PLR via the use of stochastic approximation idea.
This methods access a single feature of training vectors instead of entire training vectors at each iteration.
We propose a parallel version of this algorithm and achieve the result of comparable accuracy while faster convergent.

The rest of the paper is organized as follows:
Section~\ref{sec:rew} discusses some related work and three different systems.
In Section~\ref{sec:plr}, we review the penalized logistic regression model.
In Section~\ref{sec:framework}, we present the parallel framework of all three different algorithms for PLR.
Section~\ref{sec:experiment} describes the datasets and the baseline of our experiments and presents the experimental results.
Finally, we offer our concluding remarks in Section~\ref{sec:concl}.

\section{Related Work} \label{sec:rew}

In big data scenario, large datasets require us to develop machine learning algorithms towards a more efficient and more parallelized end.
Researchers have already done much work to cater for the needs of massive datasets.
Early work like PSVM (Parallel Support Vector Machines)~\cite{chang2011psvm} employed an approximation matrix decomposition method based on row selections to reduce the memory when running the algorithm.
It can then increase the number of participated parallel computation nodes to several hundreds.
Later, the work of PLDA (Parallel Latent Dirichlet Allocation)~\cite{wang2009plda} further improve the computational efficiency through the use of sampling methods.
The proposed parallel algorithm in Hadoop is robust, for it has fault tolerance of machines, taking the advantage of Hadoop.
Recently, the work by Dean et al.\cite{le2011building} showed that the advantage of parallelization is fully taken in deep learning algorithms.
It pushed the limits of parallel computational nodes to a hundred-million level, and in the meantime, achieved a best learning performance ever.
Besides Hadoop, there are many other trials on parallelization in machine learning.
GraphLab~\cite{kyrola2012graphchi}, a recent developed tool in CMU\textit{(Carnegie Mellon University)} for large-scale machine learning, tried to tackle with efficiency and scalability problems of machine leaning algorithms when applied to graphs.

Three computing platforms we are working on each features for its own advantage in implementing machine learning algorithms.
The Apache Hadoop~\cite{white2012hadoop} software library is a framework that allows for the distributed processing of large data sets across clusters of computers using simple programming models. It is designed to scale up from single servers to thousands of machines, each offering local computation and storage. Rather than rely on hardware to deliver high-availability, the library itself is designed to detect and handle failures at the application layer, so delivering a highly-available service on top of a cluster of computers, each of which may be prone to failures.
It is an open-source software framework that supports data-intensive distributed applications, licensed under the Apache v2 license. It supports the running of applications on large clusters of commodity hardware. Hadoop was derived from Google's MapReduce and Google File System (GFS) papers. The Hadoop framework transparently provides both reliability and data motion to applications. Hadoop implements a computational paradigm named MapReduce~\cite{dean2008mapreduce}, where the application is divided into many small fragments of work, each of which may be executed or re-executed on any node in the cluster.
The MapReduce paradigm applies to problems where the input is a set of key-value pairs.
A \textit{map} function turns these key-value pairs into other intermediate key-value pairs. A \textit{reduce} function merges in some way all values for each intermediate key to produce output.
Actually, many problems can be framed as MapReduce problems, or as a series of them. The paradigm also lends itself quite well to parallelization: all of the processing is independent and so can be split across many machines.
In addition, it provides a distributed file system that stores data on the compute nodes, providing very high aggregate bandwidth across the cluster.
Both map/reduce and the distributed file system are designed so that node failures are automatically handled by the framework.
The entire Apache Hadoop platform is now commonly considered to consist of the Hadoop kernel, MapReduce and Hadoop Distributed File System (HDFS), as well as a number of related projects ¨C including Apache Hive, Apache HBase, and others. Hadoop is written in the Java programming language and is an Apache top-level project being built and used by a global community of contributors.

The Apache Mahout~\cite{mahoutscalable} machine learning library's goal is to build scalable machine learning libraries. It is scalable to reasonably large data sets. Their core algorithms for clustering, classification and batch based collaborative filtering are implemented on top of Apache Hadoop using the map/reduce paradigm. The core libraries are highly optimized to allow for good performance also for non-distributed algorithms.
It is also scalable to support business cases. Mahout is distributed under a commercially friendly Apache Software license. Currently Mahout supports mainly four use cases: Recommendation mining takes users' behavior and from that tries to find items users might like. Clustering takes e.g. text documents and groups them into groups of topically related documents. Classification learns from existing categorized documents what documents of a specific category look like and is able to assign unlabeled documents to the (hopefully) correct category. Frequent itemset mining takes a set of item groups (terms in a query session, shopping cart content) and identifies, which individual items usually appear together.
Mahout currently supports many machine learning algorithms including collaborative filtering, user and item based recommenders, K-Means, fuzzy K-Means clustering, mean shift clustering, dirichlet process clustering, Latent Dirichlet Allocation, singular value decomposition, parallel frequent pattern mining, complementary naive bayes classifier, random forest decision tree based classifier.

Spark~\cite{zaharia2010spark} was developed in the UC Berkeley AMPLab. It is an open source cluster computing system that aims to make data analytics fast ¡ª both fast to run and fast to write.
To run programs faster, Spark provides primitives for in-memory cluster computing: a job can load data into memory and query it repeatedly much more quickly than with disk-based systems like Hadoop MapReduce.
To make programming faster, Spark provides clean, concise APIs in Scala, Java and Python. Users can also use Spark interactively from the Scala and Python shells to rapidly query big datasets.
Spark was initially developed for two applications where keeping data in memory helps: iterative algorithms, which are common in machine learning, and interactive data mining. In both cases, Spark can run up to 100x faster than Hadoop MapReduce. Spark is also the engine behind Shark, a fully Apache Hive-compatible data warehousing system that can run 100x faster than Hive. While Spark is a new engine, it can access any data source supported by Hadoop, making it easy to run over existing data.
Spark is built on top of Mesos, a cluster operating system that lets multiple parallel applications share a cluster in a fine-grained manner and provides an API for applications to launch tasks on a cluster.
This allows Spark to run alongside existing cluster computing frameworks, such as Mesos ports of Hadoop and MPI, and share data with them.
In addition, building on Mesos greatly reduced the programming effort that had to go into Spark.
The main abstraction in Spark is that of a resilient distributed dataset\textit{(RDD)}, which represents a read-only collection of objects partitioned across a set of machines that can be rebuilt if a partition is lost.
Users can explicitly cache an RDD in memory across machines and reuse it in multiple MapReduce-like parallel operations.
RDDs achieve fault tolerance through a notion of lineage: if a partition of an RDD is lost, the RDD has enough information about how it was derived from other RDDs to be able to rebuild just that partition.

Recently, Clarkson et al. \cite{clarkson2010sublinear} proposed a new method by taking advantage of randomized algorithms.
They presented sublinear-time approximation algorithms for optimization problems arising in machine learning, such as linear classifiers and minimum enclosing balls.
The algorithm uses a combination of a novel sampling techniques and a new multiplicative update algorithm. They also proved lower bounds which show the running times to be nearly optimal on the unit-cost RAM model.
Hazan et al. \cite{hazanbeating} exploited sublinear approximation approach to the linear SVM with $\ell_2$-penalty, from which we were inspired and borrowed some of the ideas (We generally refer to them as the ETN framework in Section~\ref{sec:framework}). Later on, Cotter et al. \cite{cotter2012kernelized} extended the work to kernelized SVM cases. In \cite{hazan2011optimal}, Hazan et al. applied the sublinear approximation approach for solving ridge ($\ell_2$-regularized) and lasso ($\ell_1$-regularized) linear regression. Garber and Hazan \cite{garberapproximating} developed the method in semidenfinite programming (SDP).

\section{Penalized Logistic Regression Models and Sublinear Methods} \label{sec:plr}

Logistic regression is a widely used method for solving classification problems.
In this paper, we are mainly concerned with the binary classification problem.  	
Suppose that we are given a set of training data $\XM=\{(\x_i, y_i): i=1, \ldots, n\}$ where $\x_i \in \RB^d$ are input samples and $y_i \in \{-1, 1\}$ are the corresponding labels.
For simplicity, we let $\X=[{\x}_{1}, {\x}_{2}, \ldots, {\x}_n]^{T}$ and $\y=(y_1, y_2, \ldots, y_n)^T$.
In the logistic regression model, the expected value of $y_i$ is given by
\[
P(y_i|\x_i)= \frac{1}{1+ \exp(- y_i(\x_i^T \w + b))} \triangleq g_i(y_i),
\]
where $\w=(w_1, \ldots, w_d)^T \in \RB^d$ is a regression vector and $b\in \RB$ is an offset term.

\subsection{Penalized Logistic Regression Models}

We assume that $\w$ follows a Gaussian distribution with mean $\0$ and covariance matrix $\lambda \I_d$ where $\I_d$ is the $d{\times}d$ identity matrix, i.e. $\w \thicksim N(\0, \lambda \I_d)$.
In this case, we can formulate the optimization problem as
\begin{equation} \label{eqn:4}
	\max_{\bw ,b} \; \Big\{F(\w, b| \XM) - \frac{\lambda}{2}  \|\bw\|_2^{2} \Big\}.
\end{equation}
(\ref{eqn:4}) shows us that the problem reduces to an optimization problem with an $\ell_2$-penalty.

In another case, we impose a Laplace prior for $\w$, whose density is given by
\[	
\log\,p\lc\bw \rc=d\,\log\frac{\gamma}{2}-\gamma{\|\bw\|}_{1}.
\]
With this prior, we get an optimization problem with the $\ell_1$-penalty.
\begin{equation} \label{eqn:5}
	\max_{\bw ,b} \;  \big\{F(\w, b|\XM)- \gamma{\|\bw \|}_{1}\big\}.	
\end{equation}

The advantage of $\ell_1$-penalty over $\ell_2$-penalty is its utility in sparsity modeling \cite{tibshirani1996regression}.
Thus, $\ell_1$-penalty logistic regression can serve for both classification and feature selection simultaneously.

\subsection{Sublinear Algorithms}

The framework of sublinear algorithms is a hybrid method to handle hard margin and soft margin separately and simultaneously.
It enjoys the property of fast convergence for both hard margin and soft margin.

Each iteration of the method works in two steps.
The first one is the \textit{stochastic primal update}:
\begin{enumerate}
\item[{(1)}] \; An instance $i\in \{1,\ldots, n\}$ is chosen according to a probability vector $\bp$;
\item[{(2)}] \; The primal variable $\bw$ is updated according to the derivative of $f_i(\bw,b)$ and the soft margin, via an online update with regret.
\end{enumerate}

The second one is the \textit{stochastic dual update}:
\begin{enumerate}
\item[{(1)}] \; A stochastic estimate of $f_i(\bw,b)$ plus the soft margin is obtained, which can be computed in $O(1)$ time per term;
\item[{(2)}] \; The probability vector $\bp$ is updated based on the above computed terms by using the \textit{Multiplicative Updates} (MW) framework~\cite{arora2005multiplicative} for online optimization over the simplex.
\end{enumerate}

\subsection{Sequential Sublinear Algorithm for Logistic Regression} \label{sec:l2alg}

We use the following notations.

$clip\lc \cdot \rc$ is a projection function defined as follows:
\[
clip\lc a,b \rc \triangleq \max \lc \min \lc a,b \rc ,-b\rc \,\,\,\,\,\, a,b \in \mathbb{R}.
\]

$\sgn \lc \cdot \rc$ is the sign function; namely,
\[
\sgn \lc x \rc =
\begin{cases}
	+1 & \text{ if } x>0  \\
	0  & \text{ if } x=0  \\
	-1 & \text{ if } x<0.
\end{cases}
\]

$g\lc \cdot \rc$ is the logistic function; namely,
\[
g \lc x \rc=\frac{1}{1+e^{-x}}
\]

In Algorithm~1, we give the sequential sublinear approximation procedure for logistic regression.	
	\begin{table} [ht]
	\begin{tabular}{l}
	\hline\noalign{\smallskip}
	\textbf{Algorithm 1} SLLR \\
	\noalign{\smallskip}
	\hline
	\noalign{\smallskip}
	1:	Input parameters: $\varepsilon, \nu, X, Y$ \\
	2:	Initialize parameters: $T, \eta, {\mathbf{u}}_{0}, {\bw}_{1}, {\mathbf{\bq}}_{1}, {b}_{1}$\\
	3:	Iterations: $t=1 \sim T$ \\
	4:	\tspace ${\bp}_{t}\leftarrow{\bq}_{t}/{\|{\bq}_{t}\|}_{1}$ \\
	5:  \tspace Choose ${i}_{t}\leftarrow i$ with probability $\bp(i)$ \\
	6:	\tspace $coef\leftarrow{y}_{{i}_{t}}g\lc-{y}_{{i}_{t}}\lc {{\bw}_{t}}^{T}{\mathbf{x}}_{i_t}+{b}_{t} \rc\rc$ \\
	7:	\tspace ${\bu}_{t}\leftarrow {\bu}_{t-1}+\frac{coef}{\sqrt{2T}}{\mathbf{x}}_{{i}_{t}}$ \\
	8:	\tspace ${\bw}_{t}\leftarrow {\bu}_{t}/\max \left\{1,\|{\bu}_{t}\|_2 \right\}$ \\
    9:  \tspace ${b}_{t}\leftarrow \sgn\lc {{\bp}_{t}}^{T}\mathbf{y}\rc$ \\
	10:	\tspaces Choose ${j}_{t}\leftarrow j$ with probability ${{\bw}_{t}\lj}^{2}/{\|{\bw}_{t}\|_2}^{2} $ \\
	11:	\tspaces Iterations: $i=1 \sim n$ \\
	12:	\tspaces\tspace $\sigma \leftarrow \mathbf{x}_{i} \lc {j}_{t}\rc{\|{\bw}_{t}\|_2}^{2}/{\bw}_{t}\lc {j}_{t} \rc+{\bxi}_{t}\li+{y}_{i}{b}_{t}$ \\
	13:	\tspaces\tspace $\hat{\sigma} \leftarrow clip\lc \sigma,1/\eta \rc$ \\
	14:	\tspaces\tspace ${\bq}_{t+1}\li \leftarrow {\bp}_{t}\li\lc 1-\eta\hat{\sigma} + {\eta}^{2}{\hat{\sigma}}^{2} \rc$ \\
	15:	Output: $\bar{\bw}=\frac{1}{T}\sum_{t}{\bw}_{t},\bar{b}=\frac{1}{T}\sum_{t}{b}_{t}$ \\
	\hline
	\end{tabular} 	
	\label{alg:1}
	\end{table}

\section{Parallel Framework of Learning Algorithms for PLR} \label{sec:framework}

\subsection{Parallel Sublinear algorithms in Hadoop (MapReduce)}
    In this section, we develop an approach to solve sublinear learning for penalized logistic regression using the architecture of MapReduce.
	\begin{table}[ht]
	\begin{tabular}{l}
	\hline\noalign{\smallskip}
	\textbf{Algorithm 2} PSUBPLR-MR \\
	\noalign{\smallskip}
	\hline
	\noalign{\smallskip}
    1:  Input parameters: $\varepsilon, \nu~or~\gamma, X, Y, n, d$ \\
    2:	Initialize parameters: $T, \eta, {\mathbf{u}}_{0}, {\bw}_{1}, {\mathbf{\bq}}_{1}, {b}_{1}$\\
    3:	Iterations: $t=1 \sim T$ \\
    4:  \tspace $\bw_t \rightarrow$ storeInHdfsFile("hdfs://paraw").addToDistributedCache() \\
    5:  \tspace $\bp_t \rightarrow$ storeInHdfsFile("hdfs://parap").addToDistributedCache() \\
    6:  \tspace conf\_primal $\leftarrow$ new Configuration() \\
    7:  \tspace job\_primal $\leftarrow$ new MapReduce-Job(conf\_primal) \\
    8:  \tspace conf\_primal.passParameters($T, n, d, b_t$) \\
    9:  \tspace job\_primal.setInputPath("...") \\
	10:	\tspaces job\_primal.setOutputPath("tmp/primal$t$") \\
    11: \tspaces job\_primal.run() \\
    12: \tspaces ($\bw_{t+1}, b_{t+1}$)$\leftarrow$PrimalUpdate($\bw_t, b_t$) \\
    13: \tspaces Choose $j_t \leftarrow j$ with probability ${{\bw}_{t+1}\lj}^{2}/{\|{\bw}_{t+1}\|_2}^{2} $ \\
    14: \tspaces $\bw_{t+1} \rightarrow$ storeInHdfsFile("hdfs://paraw").addToDistributedCache() \\
    15: \tspaces conf\_dual $\leftarrow$ new Configuration() \\
    16: \tspaces job\_dual $\leftarrow$ new MapReduce-Job(conf\_dual) \\
    17: \tspaces conf\_dual.passParameters($d, jt, b_{t+1}, \eta$) \\
    18: \tspaces job\_primal.setInputPath("...") \\	
    19:	\tspaces job\_dual.setOutputPath("tmp/dual$t$") \\
    20: \tspaces job\_dual.run() \\	
    21: \tspaces $\bp_{t+1}$$\leftarrow$DualUpdate($\bp_t$) \\
    22: Output: $\bar{\bw}=\frac{1}{T}\sum_{t}{\bw}_{t},\bar{b}=\frac{1}{T}\sum_{t}{b}_{t}$ \\
	\hline
	\end{tabular}
	\end{table}

    \begin{table}[ht]
	\begin{tabular}{l}
	\hline\noalign{\smallskip}
	\textbf{Procedure} Primal-Map(inputfile) \\
	\noalign{\smallskip}
	\hline
	\noalign{\smallskip}
    1:  ~Configuration.getParameters($T, n, d, b_t$) \\
    2:  ~$\bw_t \leftarrow$ readCachedHdfsFile("paraw") \\
    3:  ~$\bp_t \leftarrow$ readCachedHdfsFile("parap") \\
    4:  ~$i_t \leftarrow$ parseRowIndx(inputfile)\\
    5:  ~$\mathbf{x}_{i_t} \leftarrow$ parseRowVector(inputfile) \\
    6:  ~$y_{i_t} \leftarrow$ parseRowLabel(inputfile) \\
    7:  ~$r \leftarrow$ \textit{random(seed)} \\
    8:  ~\textbf{if} $\bp_t(i_t) > \frac{r}{n}$ \\
    9:  ~\tspace $tmp\_coef=\bp_t(i_t){y}_{{i}_{t}}g\lc-{y}_{{i}_{t}}\lc {{\bw}_{t}}^{T}{\mathbf{x}}_{i_t}+{b}_{t} \rc\rc$ \\
    10: \textbf{else} \\
    11: \tspace $tmp\_coef=0$ \\
    12: Iterations: $j=1 \sim d$ \\
    13: \tspace Set $key \leftarrow j$ \\
    14: \tspace Set $value \leftarrow \frac{tmp\_coef}{\sqrt{2T}}\mathbf{x}_{i_t}(j) $ \\
    15: \tspace \textbf{Output}(key, value) \\
	\hline
	\end{tabular}
	\end{table}

    \begin{table}[ht]
	\begin{tabular}{l}
	\hline\noalign{\smallskip}
	\textbf{Procedure} Primal-Reduce(key\_in, value\_in) \\
	\noalign{\smallskip}
	\hline
	\noalign{\smallskip}
    1:  $key\_out \leftarrow key\_in$ \\
    2:  $value\_out \leftarrow \sum_{for~same~key\_in}{value\_in} $ \\
    3:  \textbf{Output}(key\_out, value\_out) \\
	\hline
	\end{tabular}
	\end{table}

    \begin{table}[ht]
	\begin{tabular}{l}
	\hline\noalign{\smallskip}
	\textbf{Procedure} PrimalUpdate($\bw_t, b_t$) \\
	\noalign{\smallskip}
	\hline
	\noalign{\smallskip}
    1:  $\Delta \bw_t \leftarrow$ readFromHdfsFile("tmp/primal$t$") \\
    2:  $\bw_{t+1} \leftarrow \bw_t+\Delta \bw_t$ \\
	3:	${\bw}_{t+1}\leftarrow {\bw}_{t+1}/\max \left\{1,\|{\bw}_{t+1}\|_2 \right\}$ \\
    4:  ${b}_{t+1}\leftarrow \sgn\lc {{\bp}_{t}}^{T}\mathbf{y}\rc$ \\
	\hline
	\end{tabular}
	\end{table}

    \begin{table}[ht]
	\begin{tabular}{l}
	\hline\noalign{\smallskip}
	\textbf{Procedure} Dual-Map(inputfile) \\
	\noalign{\smallskip}
	\hline
	\noalign{\smallskip}
    1:  ~Configuration.getParameters($d, j_t, b_{t+1}, \eta$) \\
    2:  ~$\bw_{t+1} \leftarrow$ readCachedHdfsFile("paraw") \\
    3:  ~$i_t \leftarrow$ parseRowIndx(inputfile)\\
    4:  ~$\mathbf{x}_{i_t} \leftarrow$ parseRowVector(inputfile) \\
    5:  ~$y_{i_t} \leftarrow$ parseRowLabel(inputfile) \\
    6:  ~$\sigma \leftarrow \mathbf{x}_{i_t} \lc {j}_{t}\rc{\|{\bw}_{t+1}\|_2}^{2}/{\bw}_{t+1}\lc {j}_{t} \rc+{y}_{i_t}{b}_{t+1}$ \\
	7:	~$\hat{\sigma} \leftarrow clip\lc \sigma,1/\eta \rc$ \\
	8:	~$res \leftarrow 1-\eta\hat{\sigma} + {\eta}^{2}{\hat{\sigma}}^{2} $ \\
    9:  ~$key \leftarrow i_t$ \\
    10: $value \leftarrow res $ \\
    11: \textbf{Output}(key, value) \\
	\hline
	\end{tabular}
	\end{table}

    \begin{table}[ht]
	\begin{tabular}{l}
	\hline\noalign{\smallskip}
	\textbf{Procedure} DualUpdate($\bp_t$) \\
	\noalign{\smallskip}
	\hline
	\noalign{\smallskip}
    1:  $\mathbf{var} \leftarrow$ readFromHdfsFile("tmp/dual$t$") \\
    2:  Iterations: $j=1 \sim n$ \\
    3:  \tspace $\bp_{t+1}(j) \leftarrow \bp_t(j)*\mathbf{var}(j)$ \\
	\hline
	\end{tabular}
	\end{table}

    \comment{Will add more on algorithm design explanation later in next version of draft}

    \comment{1: Parameter passing Issues}

    \comment{2: L1 and L2 small changes}

    \comment{3: code details to cater to sparsity}

    \comment{4: A possible level2 parallelization}

    \comment{5: The randomization design in primal map}

    \comment{Maybe a graph to illustrate sequential part and parallelization part}

\subsection{Parallel Sublinear algorithms in Spark}
    \begin{table}[ht]
	\begin{tabular}{l}
    \hline\noalign{\smallskip}
	\textbf{Algorithm 3} PSUBPLR-SPARK \\
	\noalign{\smallskip}
	\hline
	\noalign{\smallskip}
    1:  ~Input parameters: $\varepsilon, \nu~or~\gamma, X, Y, n, d$ \\
    2:	~Initialize parameters: $T, \eta, {\mathbf{u}}_{0}, {\bw}_{1}, {\mathbf{\bq}}_{1}, {b}_{1}$\\
    3:  ~points $\leftarrow$ spark.textFile(inputfile).map(parsePoint()).cache() \\
    4:  ~Iterations: $t=1 \sim T$ \\
    5:  ~\tspace gradient $\leftarrow$ points.map($(\frac{1}{1+e^{-y((\bw^T \textbf{x})+b)}}-1) * y * \bp [index]$).reduce( \_ + \_ ) \\
    6:  ~\tspace ($\bw_{t+1}, b_{t+1}$)$\leftarrow$PrimalUpdate($\bw_t, b_t$) \\
    7:  ~\tspace Choose $j_t \leftarrow j$ with probability ${{\bw}_{t+1}\lj}^{2}/{\|{\bw}_{t+1}\|_2}^{2} $ \\
    8:  ~\tspace pAdjust $\leftarrow$ points.map(MW-Update()).reduce(copy()) \\
    9:  ~\tspace $\bp_{t+1}$$\leftarrow$DualUpdate($\bp_t$)  \\
    10: \textbf{Output}($\bw, b$) \\
    \hline
    \end{tabular}
	\end{table}

    \comment{Will add more on algorithm design explanation later in next version of draft}

    \comment{1: Parsed Data Structure Design}

    \comment{2: L1 and L2 small changes}

    \comment{3: code details to cater to sparsity}

    \comment{4: Emphasis on .cahche() }

    \comment{5: Similarity with PSUBPLR-MR}

\subsection{Parallel Gradient Descent in Spark}
    \begin{table}[ht]
	\begin{tabular}{l}
    \hline\noalign{\smallskip}
	\textbf{Algorithm 4} PGDPLR-SPARK \\
	\noalign{\smallskip}
	\hline
	\noalign{\smallskip}
    1:  Input parameters: $\varepsilon, \nu~or~\gamma, X, Y, n, d$ \\
    2:	Initialize parameters: $T, \eta, {\mathbf{u}}_{0}, {\bw}_{1}, {\mathbf{\bq}}_{1}, {b}_{1}$\\
    3:  points $\leftarrow$ spark.textFile(inputfile).map(parsePoint()).cache() \\
    4:  Iterations: $t=1 \sim T$ \\
    5:  \tspace gradient $\leftarrow$ points.map($(\frac{1}{1+e^{-y((\bw^T \textbf{x})+b)}}-1) * y * \bp [index]$).reduce( \_ + \_ ) \\
    6:  \tspace $\bw_{t+1} = \bw_t - gradient * \textbf{x}$ \\
    7:  \tspace $b = b - gradient$ \\
    8:  \textbf{Output}($\bw, b$) \\
    \hline
    \end{tabular}
	\end{table}

    \comment{Will add more on algorithm design explanation later in next version of draft}

    \comment{1: L1 and L2 small changes}

    \comment{2: Similarity with PSUBPLR-SPARK}

\subsection{Online Stochastic Gradient Descent in Mahout}
Though SGD is an inherently sequential algorithm, it is blazingly fast and thus it is not a problem for Mahout's implementation to handle training sets of tens of millions of examples.
With the down-sampling typical in many data-sets, this is equivalent to a dataset with billions of raw training examples.
The SGD system in Mahout is an online learning algorithm which means that you can learn models in an incremental fashion and that you can do performance testing as your system runs. Often this means that you can stop training when a model reaches a target level of performance. The SGD framework includes classes to do on-line evaluation using cross validation (the CrossFoldLearner) and an evolutionary system to do learning hyper-parameter optimization on the fly (the AdaptiveLogisticRegression). The AdaptiveLogisticRegression system makes heavy use of threads to increase machine utilization. The way it works is that it runs 20 CrossFoldLearners in separate threads, each with slightly different learning parameters. As better settings are found, these new settings are propagating to the other learners.

Because the SGD algorithms need to have fixed length feature vectors and because it is a pain to build a dictionary ahead of time, most SGD applications use the hashed feature vector encoding system that is rooted at FeatureVectorEncoder. The basic idea is that you create a vector, typically a RandomAccessSparseVector, and then you use various feature encoders to progressively add features to that vector. The size of the vector should be large enough to avoid feature collisions as features are hashed. There are specialized encoders for a variety of data types. You can normally encode either a string representation of the value you want to encode or you can encode a byte level representation to avoid string conversion. In the case of ContinuousValueEncoder and ConstantValueEncoder, it is also possible to encode a null value and pass the real value in as a weight. This avoids numerical parsing entirely in case you are getting your training data from a system like Avro.

    \comment{Will add more on algorithm design explanation later in next version of draft}

    \comment{1: Add presudo code}

    \comment{2: function call by OnlineLogisticRegression() and corresponding feature vector encoding (will ask Liang Ding to help to write)}

\section{Experiments} \label{sec:experiment}
In this section, we conduct an empirical analysis of our algorithms.
Particularly, we illustrate test errors in terms of accuracy and convergence in terms of MAP, both with respect to running time.

We choose five open datasets to run all four test programs:	
The	Simulated \textbf{2d} dataset has 2 features and 200 instances.
The	\textbf{20NewsGroup} dataset has 16428 features and 1988 instances. We split it into a training set of 1800 instances and a test set of 188 instances.	
The	third test dataset is the \textbf{Gisette}~\cite{guyon2004result} dataset, which has 5000 features and 7000 instances. We split it into a training set of 6000 instances and a test set of 1000 instances.
The	fourth test dataset is the \textbf{ECUESpam}~\cite{DelanyKBS05} dataset, which has 100249 features and 10678 instances (after proper preprocessing). We split it into a training set of 9000 instances and a test set of 1687 instances.
Finally, we have the \textbf{URL-Reputation}~\cite{ma2009identifying} dataset, which has 3231961 features and 2376130 instances. We split it into a training set of 2356130 instances and a test set of 20000 instances.
We randomly repeat such split 20 times and our analysis is based on the average performance of 20 repetitions.

\begin{table}[h]
\centering
\caption{Datasets}\label{tab:table1}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
    Name           & \# of Feat. & \# of Inst. & Sparsity & \# of Nonzeros & \# of +1 Inst. / \# of -1 Inst.\\
\hline
    2d             & 2             & 200            & ...      & ...                 & 1.000 \\
\hline
    20NewsGroup    & 16428         & 1988           & ...      & ...                 & 1.006 \\
\hline
    Gisette        & 5000          & 7000           & ...      & ...                 & 1.000 \\
\hline
    ECUESpam       & 100249        & 10678          & ...      & ...                 & 5.882 \\
\hline
    URL-Reputation & 3231961       & 2376130        & ...      & ...                 & ... \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Cluster Information}\label{tab:table2}
\begin{tabular}{|c|c|}
\hline
    CPU Model & ... \\
\hline
    Number of node & 6 \\
\hline
    Number of CPU per node & 8\\
\hline
    Memory per node & 12G \\
\hline
    Disk per node & 2T \\
\hline
    Cache Size per node & ... \\
\hline
\end{tabular}
\end{table}

\comment{Will add more on experimental results later in next version of draft}

\comment{1: add 5 line graphs;one dataset each;x:iteration number;y:accuracy;6 lines}

\comment{2: add 1 bar graphs;x:different algorithms;y:time;one dataset as a group}

\comment{3: add 5 line graphs;one dataset each;x:iteration number;y:MAP;6 lines}

\comment{4: add 5 bar graph;one dataset each;x:number of node used;y:time per iteration;each algorithm as a group}

\comment{5: Fault tolerance-add 1 bar graph;x:number of maps failed;y:time of the iteration;each algorithm as a group}

Analysis points:

1: liblinear always performs the best; It fully utilizes memory; Single machine does not require communication; Disadvantage: cannot run large datasets, eg. ...(detailed statistics)

2: Mahout precision not good; especially for those positive and negative instances are not balanced datasets perform poorly; sequential algorithm that can run large data in an acceptable time; Advantage: running memory is low, scalability is good

3: Sublinear methods' accuracy is acceptable.; Parallel-sublinear has a small drop in precision.

4: Hadoop's big drawback: Most current cluster programming models are based on acyclic data flow from stable storage to stable storage. Benefits of data flow: runtime can decide where to run tasks and can automatically recover from failures. But acyclic data flow is inefficient. eg. ... (detailed statistics)

5: Spark's in memory strategy; not to use hdfs file; system maybe even improved

6: fast convergent

7: In general, different algorithms for different datasets and system requirement. For general purpose, we recommend subSpark.

\begin{table}[h]
\centering
\caption{Accuracy Result}\label{tab:table3}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
           & 2d   & 20NewsGroup & Gisette & ECUESpam & URL-Reputation \\
\hline
Mahout     & 93.5\% & 71.3\% & 91.5\% & 85.2\% & 91.5\% \\
\hline
Liblinear  & 93.0\% & 92.0\% & 97.4\% & 97.1\% & 96.2\% \\
\hline
Sublinear  & 93.5\% & 91.5\% & 94.8\% & 92.3\% & 94.2\% \\
\hline
PSublinear & 93.5\% & 90.5\% & 94.6\% & 91.7\% & 93.8\% \\
\hline
Spark      & 93.5\% & 92.0\% & 97.0\% & 93.7\% & 96.0\% \\
\hline
subSpark   & 93.5\% & 90.5\% & 95.8\% & 91.7\% & 94.0\% \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Running Time Result}\label{tab:table4}
\begin{tabular}{|c|c|c|c|c|c|}
\hline
           & 2d   & 20NewsGroup & Gisette & ECUESpam & URL-Reputation \\
\hline
Mahout     & 0.595s & 9.827s & 131.807s & 96.611s & 10100.209s \\
\hline
Liblinear  & 0.078s & 0.793s & 2.364s & 13.161s & 519.115s \\
\hline
Sublinear  & 1.761s & 20.046s & 130.451s & 1028.185s & 3248.473s \\
\hline
PSublinear & 120.186s & 1360.854s & 3687.941s & 11478.706s & 16098.260s \\
\hline
Spark      & 0.681s & 10.517s & 99.156s & 924.020s & 3615.780s \\
\hline
subSpark   & 1.325s & 8.571s & 89.094s & 796.802s & 2918.470s \\
\hline
\end{tabular}
\end{table}

\begin{table}[h]
\centering
\caption{Fault Tolerance}\label{tab:table5}
\begin{tabular}{|c|c|c|}
\hline
           & System Level & Algorithm Level \\
\hline
Mahout     & \Checkmark & \XSolid  \\
\hline
Liblinear  & \XSolid & \XSolid \\
\hline
Sublinear  & \XSolid & \Checkmark \\
\hline
PSublinear & \Checkmark & \Checkmark \\
\hline
Spark      & \Checkmark & \XSolid \\
\hline
subSpark   & \Checkmark &  \Checkmark \\
\hline
\end{tabular}
\end{table}

\comment{Will add explanation for table 5 later in next version of draft}

%Current URL-reputation Dataset Status
%\begin{figure}[tb] \label{fig:01}
%\center \includegraphics[height=5cm,width=10cm]{show1.png}
%\caption{URL-reputation Dataset, Performance Result}
%\end{figure}

2d-dataset (separation graph)
\begin{figure}[tb] \label{fig:02}
\center \includegraphics[height=5cm,width=7cm]{show-2d.png}
\caption{2d Dataset, Visual Result}
\end{figure}

\section{Conclusion} \label{sec:concl}
%conclusion & contribution & future work
In this paper we analyzed three approaches along with three systems to fitting PLR models for large-volume, high-dimensional data for classification.
The dataset size ranges from KB to GB.
Hadoop, Mahout and Spark are existing well-known parallel frameworks that can be implemented with large scale machine learning algorithms.
Parallel gradient Descent stochastic gradient descent are two existing state-of-art algorithms for parameter optimization in PLR.
We also present a novel parallel sublinear method and make a comparison between these algorithms implemented on different systems.
As the outcome shows, we claim parallel sublinear method implemented on Spark is the most computational efficient way to solve PLR for general purpose.
Moreover, fault tolerance can be provided for those lengthy distributed computations both on algorithm level and system level.
We discussed the balance between dataset size, choosing parallel system, and choosing parallel algorithm through concrete experimental results.
Also, fault tolerance can be provided for those lengthy distributed computations both on algorithm level and system level.
As the outcome shows, we recommend parallel sublinear method implemented on Spark is the most computational efficient way to solve PLR for general purpose.

\begin{small}
\bibliographystyle{plain}
\bibliography{mlpaper}
\end{small}
\end{document}

### 2013-05-26 sample.tex
initial

% This is paper draft for ECML
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
% edited by Haoruo Peng 
\documentclass{llncs}
\usepackage{llncsdoc}

\begin{document}
\markboth{\LaTeXe{} Class for Lecture Notes in Computer Science}{\LaTeXe{} Class for Lecture Notes in Computer Science}
\thispagestyle{empty}
\begin{flushleft}
\LARGE\bfseries Instructions for Authors\\
Coding with \LaTeX\\[2cm]
\end{flushleft}
\rule{\textwidth}{1pt}
\vspace{2pt}
\begin{flushright}
\Huge
\begin{tabular}{@{}l}
\LaTeXe{} Class\\
for Lecture Notes\\
in Computer Science\\[6pt]
{\Large Version 2.4}
\end{tabular}
\end{flushright}
\rule{\textwidth}{1pt}
\vfill

\newpage
%
\section*{For further information please contact us:}
%
\begin{flushleft}
\begin{tabular}{l@{\quad}l@{\hspace{3mm}}l@{\qquad}l}
$\bullet$&\multicolumn{3}{@{}l}{\bfseries LNCS Editorial Office}\\[1mm]
&\multicolumn{3}{@{}l}{Springer-Verlag}\\
&\multicolumn{3}{@{}l}{Computer Science Editorial}\\
&\multicolumn{3}{@{}l}{Tiergartenstrae 17}\\
&\multicolumn{3}{@{}l}{69121 Heidelberg}\\
&\multicolumn{3}{@{}l}{Germany}\\[0.5mm]
 & Tel:       & +49-6221-487-8706\\
 & Fax:       & +49-6221-487-8588\\
 & e-mail:    & \tt lncs@springer.com    & for editorial questions\\
 &            & \tt texhelp@springer.de & for \TeX{} problems\\[2mm]
\noalign{\rule{\textwidth}{1pt}}
\noalign{\vskip2mm}
%
%{\tt svserv@vax.ntp.springer.de}\hfil first try the \verb|help|
%command.
%
$\bullet$&\multicolumn{3}{@{}l}{\bfseries We are also reachable through the world wide web:}\\[1mm]
         &\multicolumn{2}{@{}l}{\texttt{http://www.springer.com}}&Springer Global Website\\
         &\multicolumn{2}{@{}l}{\texttt{http://www.springer.com/lncs}}&LNCS home page\\
         &\multicolumn{2}{@{}l}{\texttt{http://www.springerlink.com}}&data repository\\
         &\multicolumn{2}{@{}l}{\texttt{ftp://ftp.springer.de}}&FTP server
\end{tabular}
\end{flushleft}

%
\newpage
\tableofcontents
\newpage
%
\section{Introduction}
%
Authors wishing to code their contribution
with \LaTeX{}, as well as those who have already coded with \LaTeX{},
will be provided with a document class that will give the text the
desired layout. Authors are requested to
adhere strictly to these instructions; {\em the class
file must not be changed}.

The text output area is automatically set within an area of
12.2\,cm horizontally  and 19.3\,cm vertically.

If you are already familiar with \LaTeX{}, then the
LLNCS class should not give you any major difficulties.
It will change the layout to the required LLNCS style
(it will for instance define the layout of \verb|\section|).
We had to invent some extra commands,
which are not provided by \LaTeX{} (e.g.\
\verb|\institute|, see also Sect.\,\ref{contbegin})

For the main body of the paper (the text) you
should use the commands of the standard \LaTeX{} ``article'' class.
Even if you are familiar with those commands, we urge you to read
this entire documentation thoroughly. It contains many suggestions on
how to use our commands properly; thus your paper
will be formatted exactly to LLNCS standard.
For the input of the references at the end of your contribution,
please follow our instructions given in Sect.\,\ref{refer} References.

The majority of these hints are not specific for LLNCS; they may improve
your use of \LaTeX{} in general.
Furthermore, the documentation provides suggestions about the proper
editing and use
of the input files (capitalization, abbreviation etc.) (see
Sect.\,\ref{refedit} How to Edit Your Input File).
%
\section{How to Proceed}
%
The package consists of the following files:
\begin{flushleft}
\begin{tabular}{@{}p{2.5cm}l}
{\tt history.txt}& the version history of the package\\[2pt]
{\tt llncs.cls}  & class file for \LaTeX{}\\[2pt]
{\tt llncs.dem}  & an example showing how to code the text\\[2pt]
{\tt llncs.doc}  & general instructions (source of this document),\\
        & {\tt llncs.doc} means {\itshape l\/}atex {\itshape doc\/}umentation for\\
        & {\itshape L\/}ecture {\itshape N}otes in {\itshape C\/}omputer {\itshape S\/}cience\\
{\tt llncsdoc.pdf}& the documentation of the class (PDF version),\\
{\tt llncs.doc}  & general instructions (source of this document),\\
{\tt llncsdoc.sty}  & class modifications to help for the instructions\\
{\tt llncs.ind} & an external (faked) author index file\\
{\tt subjidx.ind} & subject index demo from the Springer book package\\
{\tt llncs.dvi}    & the resultig DVI file (remember to use binary transfer!)\\[2pt]
{\tt sprmindx.sty} & supplementary style file for MakeIndex\\
                   & (usage: {\tt makeindex -s sprmindx.sty <yourfile.idx>})
\end{tabular}
\end{flushleft}
%
\subsection{How to Invoke the LLNCS Document Class}
%
The LLNCS class is an extension of the standard \LaTeX{} ``article''
document class. Therefore you may use all ``article'' commands for the
body of your contribution to prepare your manuscript.
LLNCS class is invoked by replacing ``article'' by ``llncs'' in the
first line of your document:
\begin{verbatim}
\documentclass{llncs}
%
\begin{document}
  <Your contribution>
\end{document}
\end{verbatim}
%
\subsection{Contributions Already Coded with \protect\LaTeX{} without
the LLNCS document class}
%
If your file is already coded with \LaTeX{} you can easily
adapt it a posteriori to the LLNCS document class.

Please refrain from using any \LaTeX{} or \TeX{} commands
that affect the layout or formatting of your document (i.e. commands
like \verb|\textheight|, \verb|\vspace|, \verb|\headsep| etc.).
There may nevertheless be exceptional occasions on which to
use some of them.

The LLNCS document class has been carefully designed to produce the
right layout from your \LaTeX{} input. If there is anything specific you
would like to do and for which the style file does not provide a
command, {\em please contact us}. Same holds for any error and bug you
discover (there is however no reward for this -- sorry).
%
\section{General Rules for Coding Formulas}
%
With mathematical formulas you may proceed as described
in Sect.\,3.3 of the {\em \LaTeX{} User's Guide \& Reference
Manual\/} by Leslie Lamport (2nd~ed. 1994), Addison-Wesley Publishing
Company, Inc.

Equations are automatically numbered sequentially throughout your
contribution using arabic numerals in parentheses on the right-hand
side.

When you are working in math mode everything is typeset in italics.
Sometimes you need to insert non-mathematical elements (e.g.\
words or phrases). Such insertions should be coded in roman
(with \verb|\mbox|) as illustrated in the following example:
\begin{flushleft}
{\itshape Sample Input}
\end{flushleft}
\begin{verbatim}
\begin{equation}
  \left(\frac{a^{2} + b^{2}}{c^{3}} \right) = 1 \quad
  \mbox{ if } c\neq 0 \mbox{ and if } a,b,c\in \bbbr \enspace .
\end{equation}
\end{verbatim}
{\itshape Sample Output}
\begin{equation}
  \left(\frac{a^{2} + b^{2}}{c^{3}} \right) = 1 \quad
  \mbox{ if } c\neq 0 \mbox{ and if } a,b,c\in \bbbr \enspace .
\end{equation}

If you wish to start a new paragraph immediately after a displayed
equation, insert a blank line so as to produce the required
indentation. If there is no new paragraph either do not insert
a blank line or code \verb|\noindent| immediately before
continuing the text.

Please punctuate a displayed equation in the same way as other
ordinary text but with an \verb|\enspace| before end punctuation.

Note that the sizes of the parentheses or other delimiter
symbols used in equations should ideally match the height of the
formulas being enclosed. This is automatically taken care of by
the following \LaTeX{} commands:\\[2mm]
\verb|\left(| or \verb|\left[| and
\verb|\right)| or \verb|\right]|.
%
\subsection{Italic and Roman Type in Math Mode}
%
\begin{alpherate}
\item
In math mode \LaTeX{} treats all letters as though they
were mathematical or physical variables, hence they are typeset as
characters of their own in
italics. However, for certain components of formulas, like short texts,
this would be incorrect and therefore coding in roman is required.
Roman should also be used for
subscripts and superscripts {\em in formulas\/} where these are
merely labels and not in themselves variables,
e.g. $T_{\mathrm{eff}}$ \emph{not} $T_{eff}$,
$T_{\mathrm K}$ \emph{not} $T_K$ (K = Kelvin),
$m_{\mathrm e}$ \emph{not} $m_e$ (e = electron).
However, do not code for roman
if the sub/superscripts represent variables,
e.g.\ $\sum_{i=1}^{n} a_{i}$.
\item
Please ensure that {\em physical units\/} (e.g.\ pc, erg s$^{-1}$
K, cm$^{-3}$, W m$^{-2}$ Hz$^{-1}$, m kg s$^{-2}$ A$^{-2}$) and
{\em abbreviations\/} such as Ord, Var, GL, SL, sgn, const.\
are always set in roman type. To ensure
this use the \verb|\mathrm| command: \verb|\mathrm{Hz}|.
On p.\ 44 of the {\em \LaTeX{} User's Guide \& Reference
Manual\/} by Leslie Lamport you will find the names of
common mathe\-matical functions, such as log, sin, exp, max and sup.
These should be coded as \verb|\log|,
\verb|\sin|, \verb|\exp|, \verb|\max|, \verb|\sup|
and will appear in roman automatically.
\item
Chemical symbols and formulas should be coded for roman,
e.g.\ Fe not $Fe$, H$_2$O not {\em H$_2$O}.
\item
Familiar foreign words and phrases, e.g.\ et al.,
a priori, in situ, brems\-strah\-lung, eigenvalues should not be
italicized.
\end{alpherate}
%
\section{How to Edit Your Input (Source) File}
\label{refedit}
%
\subsection{Headings}\label{headings}
%
All words in headings should be capitalized except for conjunctions,
prepositions (e.g.\ on, of, by, and, or, but, from, with, without,
under) and definite and indefinite articles (the, a, an) unless they
appear at the beginning. Formula letters must be typeset as in the text.
%
\subsection{Capitalization and Non-capitalization}
%
\begin{alpherate}
\item
The following should always be capitalized:
\begin{itemize}
\item
Headings (see preceding Sect.\,\ref{headings})
\item
Abbreviations and expressions
in the text such as  Fig(s)., Table(s), Sect(s)., Chap(s).,
Theorem, Corollary, Definition etc. when used with numbers, e.g.\
Fig.\,3, Table\,1, Theorem 2.
\end{itemize}
Please follow the special rules in Sect.\,\ref{abbrev} for referring to
equations.
\item
The following should {\em not\/} be capitalized:
\begin{itemize}
\item
The words figure(s), table(s), equation(s), theorem(s) in the text when
used without an accompanying number.
\item
Figure legends and table captions except for names and abbreviations.
\end{itemize}
\end{alpherate}
%
\subsection{Abbreviation of Words}\label{abbrev}
%
\begin{alpherate}
\item
The following {\em should} be abbreviated when they appear in running
text {\em unless\/} they come at the beginning of a sentence: Chap.,
Sect., Fig.; e.g.\ The results are depicted in Fig.\,5. Figure 9 reveals
that \dots .\\
{\em Please note\/}: Equations should usually be referred to solely by
their number in parentheses: e.g.\ (14). However, when the reference
comes at the beginning of a sentence, the unabbreviated word
``Equation'' should be used: e.g.\ Equation (14) is very important.
However, (15) makes it clear that \dots .
\item
If abbreviations of names or concepts are used
throughout the text, they should be defined at first occurrence,
e.g.\ Plurisubharmonic (PSH) Functions, Strong Optimization (SOPT)
Problem.
\end{alpherate}
%
\section{How to Code the Beginning of Your Contribution}
\label{contbegin}
%
The title of a single contribution (it is mandatory) should be coded as
follows:
\begin{verbatim}
\title{<Your contribution title>}
\end{verbatim}
All words in titles should be capitalized except for conjunctions,
prepositions (e.g.\ on, of, by, and, or, but, from, with, without,
under) and definite and indefinite articles (the, a, an) unless they
appear at the beginning. Formula letters must be typeset as in the text.
Titles have no end punctuation.

If a long \verb|\title| must be divided please use the code \verb|\\|
(for new line).

If you are to produce running heads for a specific volume the standard
(of no such running heads) is overwritten with the \verb|[runningheads]|
option in the \verb|\documentclass| line. For long titles that do not
fit in the single line of the running head a warning is generated.
You can specify an abbreviated title for the running head on odd pages
with the command
\begin{verbatim}
\titlerunning{<Your abbreviated contribution title>}
\end{verbatim}

There is also a possibility to change the text of the title that goes
into the table of contents (that's for volume editors only -- there is
no table of contents for a single contribution). For this use the
command
\begin{verbatim}
\toctitle{<Your changed title for the table of contents>}
\end{verbatim}

An optional subtitle may follow then:
\begin{verbatim}
\subtitle{<subtitle of your contribution>}
\end{verbatim}

Now the name(s) of the author(s) must be given:
\begin{verbatim}
\author{<author(s) name(s)>}
\end{verbatim}
Numbers referring to different addresses or affiliations are
to be attached to each author with the \verb|\inst{<no>}| command.
If there is more than one author, the order is up to you;
the \verb|\and| command provides for the separation.

If you have done this correctly, this entry now reads, for example:
\begin{verbatim}
\author{Ivar Ekeland\inst{1} \and Roger Temam\inst{2}}
\end{verbatim}
The first name\footnote{Other initials are optional
and may be inserted if this is the usual
way of writing your name, e.g.\ Alfred J.~Holmes, E.~Henry Green.}
is followed by the surname.

As for the title there exist two additional commands (again for volume
editors only) for a different author list. One for the running head
(on odd pages) -- if there is any:
\begin{verbatim}
\authorrunning{<abbreviated author list>}
\end{verbatim}
And one for the table of contents where the
affiliation of each author is simply added in braces.
\begin{verbatim}
\tocauthor{<enhanced author list for the table of contents>}
\end{verbatim}

Next the address(es) of institute(s), company etc. is (are) required.
If there is more than one address, the entries are numbered
automatically with \verb|\and|, in the order in which you type them.
Please make sure that the numbers match those placed next to
to the authors' names to reflect the affiliation.
\begin{verbatim}
\institute{<name of an institute>
\and <name of the next institute>
\and <name of the next institute>}
\end{verbatim}

In addition, you can use
\begin{verbatim}
\email{<email address>}
\end{verbatim}
to provide your email address within \verb|\institute|. If you need to
typeset the tilde character -- e.g. for your web page in your unix
system's home directory -- the \verb|\homedir| command will happily do
this. Please note that, if your email address is given in your paper, 
it will also be included in the meta data of the online version.
\enlargethispage*{6mm}

\medskip
If footnote like things are needed anywhere in the contribution heading
please code
(immediately after the word where the footnote indicator should be
placed):
\begin{verbatim}
\thanks{<text>}
\end{verbatim}
\verb|\thanks| may only appear in \verb|\title|, \verb|\author|
and \verb|\institute| to footnote anything. If there are two or more
footnotes or affiliation marks to a specific item separate them with
\verb|\fnmsep| (i.e. {\itshape f}oot\emph note \emph mark
\emph{sep}arator).

\medskip\noindent
The command
\begin{verbatim}
\maketitle
\end{verbatim}
then formats the complete heading of your article. If you leave
it out the work done so far will produce \emph{no} text.

Then the abstract should follow. Simply code
\begin{verbatim}
\begin{abstract}
<Text of the summary of your article>
\end{abstract}
\end{verbatim}
or refer to the demonstration file {\tt llncs.dem} for an example or
to the {\em Sample Input\/} on p.~\pageref{samppage}.

\subsubsection{Remark to Running Heads and the Table of Contents}
\leavevmode\\[\medskipamount]
If you are the author of a single contribution you normally have no
running heads and no table of contents. Both are done only by the editor
of the volume or at the printers.
%
\section{Special Commands for the Volume Editor}
The volume editor can produce a complete camera ready output including
running heads, a table of contents, preliminary text (frontmatter), and
index or glossary. For activating the running heads there is the class
option \verb|[runningheads]|.

The table of contents of the volume is printed wherever
\verb|\tableofcontents| is placed. A simple compilation of all
contributions (fields \verb|\title| and \verb|\author|) is done. If you
wish to change this automatically produced list use the commands
\begin{verbatim}
\titlerunning  \toctitle
\authorrunning \tocauthor
\end{verbatim}
to enhance the information in the specific contributions. See the
demonstration file \verb|llncs.dem| for examples.

An additional structure can be added to the table of contents with the
\verb|\addtocmark{<text>}| command. It has an optional numerical
argument, a digit from 1 through 3. 3 (the default) makes an unnumbered
chapter like entry in the table of contents. If you code
\verb|\addtocmark[2]{text}| the corresponding page number is listed
also, \verb|\addtocmark[1]{text}| even introduces a chapter number
beyond it.
%
\section{How to Code Your Text}
%
The contribution title and all headings should be capitalized
except for conjunctions, prepositions (e.g.\ on, of, by, and, or, but,
from, with, without, under) and definite and indefinite articles (the,
a, an) unless they appear at the beginning. Formula letters must be
typeset as in the text.

Headings will be automatically numbered by the following codes.\\[2mm]
{\itshape Sample Input}
\begin{verbatim}
\section{This is a First-Order Title}
\subsection{This is a Second-Order Title}
\subsubsection{This is a Third-Order Title.}
\paragraph{This is a Fourth-Order Title.}
\end{verbatim}
\verb|\section| and \verb|\subsection| have no end punctuation.\\
\verb|\subsubsection| and \verb|\paragraph|
need to be punctuated at the end.

In addition to the above-mentioned headings your text may be structured
by subsections indicated by run-in headings (theorem-like environments).
All the theorem-like environments are numbered automatically
throughout the sections of your document -- each with its own counter.
If you want the theorem-like environments to use the same counter
just specify the documentclass option \verb|envcountsame|:
\begin{verbatim}
\documentclass[envcountsame]{llncs}
\end{verbatim}
If your first call for a theorem-like environment then is e.g.
\verb|\begin{lemma}|, it will be numbered 1; if corollary follows,
this will be numbered 2; if you then call lemma again, this will be
numbered 3.

But in case you want to reset such counters to 1 in each section,
please specify the documentclass option \verb|envcountreset|:
\begin{verbatim}
\documentclass[envcountreset]{llncs}
\end{verbatim}

Even a numbering on section level (including the section counter) is
possible with the documentclass option \verb|envcountsect|.

\section{Predefined Theorem like Environments}\label{builtintheo}
The following variety of run-in headings are at your disposal:
\begin{alpherate}
\item
{\bfseries Bold} run-in headings with italicized text
as built-in environments:
\begin{verbatim}
\begin{corollary} <text> \end{corollary}
\begin{lemma} <text> \end{lemma}
\begin{proposition} <text> \end{proposition}
\begin{theorem} <text> \end{theorem}
\end{verbatim}
\item
The following generally appears as {\itshape italic} run-in heading:
\begin{verbatim}
\begin{proof} <text>    \qed    \end{proof}
\end{verbatim}
It is unnumbered and may contain an eye catching square (call for that
with \verb|\qed|) before the environment ends.
\item
Further {\itshape italic} or {\bfseries bold} run-in headings with roman
environment body may also occur:
\begin{verbatim}
\begin{definition} <text> \end{definition}
\begin{example} <text> \end{example}
\begin{exercise} <text> \end{exercise}
\begin{note} <text> \end{note}
\begin{problem} <text> \end{problem}
\begin{question} <text> \end{question}
\begin{remark} <text> \end{remark}
\begin{solution} <text> \end{solution}
\end{verbatim}
\end{alpherate}

\section{Defining your Own Theorem like Environments}
We have enhanced the standard \verb|\newtheorem| command and slightly
changed its syntax to get two new commands \verb|\spnewtheorem| and
\verb|\spnewtheorem*| that now can be used to define additional
environments. They require two additional arguments namely the type
style in which the keyword of the environment appears and second the
style for the text of your new environment.

\verb|\spnewtheorem| can be used in two ways.
\subsection{Method 1 {\itshape (preferred)}}
You may want to create an environment that shares its counter
with another environment, say {\em main theorem\/} to be numbered like
the predefined {\em theorem\/}. In this case, use the syntax
\begin{verbatim}
\spnewtheorem{<env_nam>}[<num_like>]{<caption>}
{<cap_font>}{<body_font>}
\end{verbatim}

\noindent
Here the environment with which the new environment should share its
counter is specified with the optional argument \verb|[<num_like>]|.

\paragraph{Sample Input}
\begin{verbatim}
\spnewtheorem{mainth}[theorem]{Main Theorem}{\bfseries}{\itshape}
\begin{theorem} The early bird gets the worm. \end{theorem}
\begin{mainth} The early worm gets eaten. \end{mainth}
\end{verbatim}
\medskip\noindent
{\em Sample Output}

\medskip\noindent
{\bfseries Theorem 3.}\enspace {\em The early bird gets the worm.}

\medskip\noindent
{\bfseries Main Theorem 4.} The early worm gets eaten.

\bigskip
The sharing of the default counter (\verb|[theorem]|) is desired. If you
omit the optional second argument of \verb|\spnewtheorem| a separate
counter for your new environment is used throughout your document.

\subsection[Method 2]{Method 2 {\itshape (assumes {\tt[envcountsect]}
documentstyle option)}}
\begin{verbatim}
\spnewtheorem{<env_nam>}{<caption>}[<within>]
{<cap_font>}{<body_font>}
\end{verbatim}

\noindent
This defines a new environment \verb|<env_nam>| which prints the caption
\verb|<caption>| in the font \verb|<cap_font>| and the text itself in
the font \verb|<body_font>|. The environment is numbered beginning anew
with every new sectioning element you specify with the optional
parameter \verb|<within>|.

\medskip\noindent
\paragraph{Example} \leavevmode

\medskip\noindent
\verb|\spnewtheorem{joke}{Joke}[subsection]{\bfseries}{\rmfamily}|

\medskip
\noindent defines a new environment called \verb|joke| which prints the
caption {\bfseries Joke} in boldface and the text in roman. The jokes are
numbered starting from 1 at the beginning of every subsection with the
number of the subsection preceding the number of the joke e.g. 7.2.1 for
the first joke in subsection 7.2.

\subsection{Unnumbered Environments}
If you wish to have an unnumbered environment, please
use the syntax
\begin{verbatim}
\spnewtheorem*{<env_nam>}{<caption>}{<cap_font>}{<body_font>}
\end{verbatim}

\section{Program Codes}
In case you want to show pieces of program code, just use the
\verb|verbatim| environment or the \verb|verbatim| package of \LaTeX.
(There also exist various pretty printers for some programming
languages.)
%
\noindent
\subsection*{Sample Input {\rmfamily(of a simple
contribution)}}\label{samppage}
\begin{verbatim}
\title{Hamiltonian Mechanics}

\author{Ivar Ekeland\inst{1} \and Roger Temam\inst{2}}

\institute{Princeton University, Princeton NJ 08544, USA
\and
Universit\'{e} de Paris-Sud,
Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
F-91405 Orsay Cedex, France}

\maketitle
%
\begin{abstract}
This paragraph shall summarize the contents of the paper
in short terms.
\end{abstract}
%
\section{Fixed-Period Problems: The Sublinear Case}
%
With this chapter, the preliminaries are over, and we begin the
search for periodic solutions \dots
%
\subsection{Autonomous Systems}
%
In this section we will consider the case when the Hamiltonian
$H(x)$ \dots
%
\subsubsection*{The General Case: Nontriviality.}
%
We assume that $H$ is
$\left(A_{\infty}, B_{\infty}\right)$-subqua\-dra\-tic
at infinity, for some constant \dots
%
\paragraph{Notes and Comments.}
The first results on subharmonics were \dots
%
\begin{proposition}
Assume $H'(0)=0$ and $ H(0)=0$. Set \dots
\end{proposition}
\begin{proof}[of proposition]
Condition (8) means that, for every $\delta'>\delta$, there is
some $\varepsilon>0$ such that \dots \qed
\end{proof}
%
\begin{example}[\rmfamily (External forcing)]
Consider the system \dots
\end{example}
\begin{corollary}
Assume $H$ is $C^{2}$ and
$\left(a_{\infty}, b_{\infty}\right)$-subquadratic
at infinity. Let \dots
\end{corollary}
\begin{lemma}
Assume that $H$ is $C^{2}$ on $\bbbr^{2n}\backslash \{0\}$
and that $H''(x)$ is \dots
\end{lemma}
\begin{theorem}[(Ghoussoub-Preiss)]
Let $X$ be a Banach Space and $\Phi:X\to\bbbr$ \dots
\end{theorem}
\begin{definition}
We shall say that a $C^{1}$ function $\Phi:X\to\bbbr$
satisfies \dots
\end{definition}
\end{verbatim}
{\itshape Sample Output\/} (follows on the next page together with
examples of the above run-in headings)
\newcounter{save}\setcounter{save}{\value{section}}
{\def\addtocontents#1#2{}%
\def\addcontentsline#1#2#3{}%
\def\markboth#1#2{}%
%
\title{Hamiltonian Mechanics}

\author{Ivar Ekeland\inst{1} \and Roger Temam\inst{2}}

\institute{Princeton University, Princeton NJ 08544, USA
\and
Universit\'{e} de Paris-Sud,
Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
F-91405 Orsay Cedex, France}

\maketitle
%
\begin{abstract}
This paragraph shall summarize the contents of the paper
in short terms.
\end{abstract}
%
\section{Fixed-Period Problems: The Sublinear Case}
%
With this chapter, the preliminaries are over, and we begin the search
for periodic solutions \dots
%
\subsection{Autonomous Systems}
%
In this section we will consider the case when the Hamiltonian
$H(x)$ \dots
%
\subsubsection{The General Case: Nontriviality.}
%
We assume that $H$ is
$\left(A_{\infty}, B_{\infty}\right)$-subqua\-dra\-tic at
infinity, for some constant \dots
%
\paragraph{Notes and Comments.}
The first results on subharmonics were \dots
%
\begin{proposition}
Assume $H'(0)=0$ and $ H(0)=0$. Set \dots
\end{proposition}
\begin{proof}[of proposition]
Condition (8) means that, for every $\delta'>\delta$, there is
some $\varepsilon>0$ such that \dots \qed
\end{proof}
%
\begin{example}[{{\rmfamily External forcing}}]
Consider the system \dots
\end{example}
\begin{corollary}
Assume $H$ is $C^{2}$ and
$\left(a_{\infty}, b_{\infty}\right)$-subquadratic
at infinity. Let \dots
\end{corollary}
\begin{lemma}
Assume that $H$ is $C^{2}$ on $\bbbr^{2n}\backslash \{0\}$
and that $H''(x)$ is \dots
\end{lemma}
\begin{theorem}[Ghoussoub-Preiss]
Let $X$ be a Banach Space and $\Phi:X\to\bbbr$ \dots
\end{theorem}
\begin{definition}
We shall say that a $C^{1}$ function $\Phi:X\to\bbbr$ satisfies \dots
\end{definition}
%
}\setcounter{section}{\value{save}}
\section{Fine Tuning of the Text}
%
The following should be used to improve the readability of the text:
\begin{flushleft}
\begin{tabular}{@{}p{.19\textwidth}p{.79\textwidth}}
\verb|\,|   & a thin space, e.g.\ between numbers or between units
              and num\-bers; a line division will not be made
              following this space\\
\verb|--|   & en dash; two strokes, without a space at either end\\
\verb*| -- |& en dash; two strokes, with  a space at either end\\
\verb|-|    & hyphen; one stroke, no space at either end\\
\verb|$-$|  & minus, in the text {\em only} \\[8mm]
{\em Input} & \verb|21\,$^{\circ}$C etc.,|\\
            &  \verb|Dr h.\,c.\,Rockefellar-Smith \dots|\\
            & \verb|20,000\,km and  Prof.\,Dr Mallory \dots|\\
            & \verb|1950--1985 \dots|\\
            & \verb|this -- written on a computer -- is now printed|\\
            & \verb|$-30$\,K \dots|\\[3mm]
{\em Output}& 21\,$^{\circ}$C etc., Dr h.\,c.\,Rockefellar-Smith \dots\\
            & 20,000\,km and  Prof.\,Dr Mallory \dots\\
            & 1950--1985 \dots\\
            & this -- written on a computer -- is now printed\\
            & $-30$\,K \dots
\end{tabular}
\end{flushleft}
%
\section {Special Typefaces}
%
Normal type (roman text) need not be coded. {\itshape Italic}
(\verb|{\em <text>}| better still \verb|\emph{<text>}|) or, if
necessary, {\bfseries boldface} should be used for emphasis.\\[6pt]
\begin{minipage}[t]{\textwidth}
\begin{flushleft}
\begin{tabular}{@{}p{.25\textwidth}@{\hskip6pt}p{.73\textwidth}@{}}
\verb|{\itshape Text}|   & {\itshape Italicized Text}\\[2pt]
\verb|{\em Text}|   & {\em Emphasized Text --
   if you would like to emphasize a {\em definition} within an
   italicized text (e.g.\ of a {\em theorem)} you should code the
   expression to be emphasized by} \verb|\em|.\\[2pt]
\verb|{\bfseries Text}|& {\bfseries Important Text}\\[2pt]
\verb|\vec{Symbol}| & Vectors may only appear in math mode. The default
   \LaTeX{} vector symbol has been adapted\footnotemark\
 to LLNCS conventions.\\[2pt]
 & \verb|$\vec{A \times B\cdot C}| yields $\vec{A\times B\cdot C}$\\
 & \verb|$\vec{A}^{T} \otimes \vec{B} \otimes|\\
 & \verb|\vec{\hat{D}}$|yields $\vec{A}^{T} \otimes \vec{B} \otimes
\vec{\hat{D}}$
\end{tabular}
\end{flushleft}
\end{minipage}

\footnotetext{If you absolutely must revive the original \LaTeX{}
design of the vector symbol (as an arrow accent), please specify the
option \texttt{[orivec]} in the \texttt{documentclass} line.}
\newpage
%
\section {Footnotes}
%
Footnotes within the text should be coded:
\begin{verbatim}
\footnote{Text}
\end{verbatim}
{\itshape Sample Input}
\begin{flushleft}
Text with a footnote\verb|\footnote{The |{\tt footnote is automatically
numbered.}\verb|}| and text continues \dots
\end{flushleft}
{\itshape Sample Output}
\begin{flushleft}
Text with a footnote\footnote{The footnote is automatically numbered.}
and text continues \dots
\end{flushleft}
%
\section {Lists}
%
Please code lists as described below:\\[2mm]
{\itshape Sample  Input}
\begin{verbatim}
\begin{enumerate}
  \item First item
  \item Second item
  \begin{enumerate}
    \item First nested item
    \item Second nested item
  \end{enumerate}
  \item Third item
\end{enumerate}
\end{verbatim}
{\itshape Sample Output}
 \begin{enumerate}
\item First item
\item Second item
  \begin{enumerate}
    \item First nested item
    \item Second nested item
  \end{enumerate}
\item Third item
\end{enumerate}
%
\section {Figures}
%
Figure environments should be inserted after (not in)
the  paragraph in which the figure is first mentioned.
They will be numbered automatically.

Preferably the images should be enclosed as PostScript files -- best as
EPS data using the epsfig package.

If you cannot include them into your output this way and use other
techniques for a separate production,
the figures (line drawings and those containing halftone inserts
as well as halftone figures) {\em should not be pasted into your
laserprinter output}. They should be enclosed separately in camera-ready
form (original artwork, glossy prints, photographs and/or slides). The
lettering should be suitable for reproduction, and after a
probably necessary reduction the height of capital letters should be at
least 1.8\,mm and not more than 2.5\,mm.
Check that lines and other details are uniformly black and
that the lettering on figures is clearly legible.

To leave the desired amount of space for the height of
your figures, please use the coding described below.
As can be seen in the output, we will automatically
provide 1\,cm space above and below the figure,
so that you should only leave the space equivalent to the size of the
figure itself. Please note that ``\verb|x|'' in the following
coding stands for the actual height of the figure:
\begin{verbatim}
\begin{figure}
\vspace{x cm}
\caption[ ]{...text of caption...}          (Do type [ ])
\end{figure}
\end{verbatim}
\begin{flushleft}
{\itshape Sample Input}
\end{flushleft}
\begin{verbatim}
\begin{figure}
\vspace{2.5cm}
\caption{This is the caption of the figure displaying a white
eagle and a white horse on a snow field}
\end{figure}
\end{verbatim}
\begin{flushleft}
{\itshape Sample Output}
\end{flushleft}
\begin{figure}
\vspace{2.5cm}
\caption{This is the caption of the figure displaying a white eagle and
a white horse on a snow field}
\end{figure}
%
\section{Tables}
%
Table captions should be treated
in the same way as figure legends, except that
the table captions appear {\itshape above} the tables. The tables
will be numbered automatically.
%
\subsection{Tables Coded with \protect\LaTeX{}}
%
Please use the following coding:\\[2mm]
{\itshape Sample Input}
\begin{verbatim}
\begin{table}
\caption{Critical $N$ values}
\begin{tabular}{llllll}
\hline\noalign{\smallskip}
${\mathrm M}_\odot$ & $\beta_{0}$ & $T_{\mathrm c6}$ & $\gamma$
  & $N_{\mathrm{crit}}^{\mathrm L}$
  & $N_{\mathrm{crit}}^{\mathrm{Te}}$\\
\noalign{\smallskip}
\hline
\noalign{\smallskip}
 30 & 0.82 & 38.4 & 35.7 & 154 & 320 \\
 60 & 0.67 & 42.1 & 34.7 & 138 & 340 \\
120 & 0.52 & 45.1 & 34.0 & 124 & 370 \\
\hline
\end{tabular}
\end{table}
\end{verbatim}

\medskip\noindent{\itshape Sample Output}
\begin{table}
\caption{Critical $N$ values}
\begin{center}
\renewcommand{\arraystretch}{1.4}
\setlength\tabcolsep{3pt}
\begin{tabular}{llllll}
\hline\noalign{\smallskip}
${\mathrm M}_\odot$ & $\beta_{0}$ & $T_{\mathrm c6}$ & $\gamma$
  & $N_{\mathrm{crit}}^{\mathrm L}$
  & $N_{\mathrm{crit}}^{\mathrm{Te}}$\\
\noalign{\smallskip}
\hline
\noalign{\smallskip}
 30 & 0.82 & 38.4 & 35.7 & 154 & 320 \\
 60 & 0.67 & 42.1 & 34.7 & 138 & 340 \\
120 & 0.52 & 45.1 & 34.0 & 124 & 370 \\
\hline
\end{tabular}
\end{center}
\end{table}

Before continuing your text you need an empty line. \dots

\vspace{3mm}
For further information you will find a complete description of
the tabular environment
on p.~62~ff. and p.~204 of the {\em \LaTeX{} User's Guide \& Reference
Manual\/} by Leslie Lamport.
%
\subsection{Tables Not Coded with \protect\LaTeX{}}
%
If you do not wish to code your table using \LaTeX{}
but prefer to have it reproduced separately,
proceed as for figures and use the following coding:\\[2mm]
{\itshape Sample Input}
\begin{verbatim}
\begin{table}
\caption{text of your caption}
\vspace{x cm}     % the actual height needed for your table
\end{table}
\end{verbatim}
%
\subsection{Signs and Characters}
%
\subsubsection*{Special Signs.}
%
You may need to use special signs.  The available ones are listed in the
{\em \LaTeX{} User's Guide \& Reference Manual\/} by Leslie Lamport,
pp.~41\,ff.
We have created further symbols for math mode (enclosed in \$):
\begin{center}
\begin{tabular}{l@{\hspace{1em}yields\hspace{1em}}
c@{\hspace{3em}}l@{\hspace{1em}yields\hspace{1em}}c}
\verb|\grole| & $\grole$ & \verb|\getsto| & $\getsto$\\
\verb|\lid|   & $\lid$   & \verb|\gid|    & $\gid$
\end{tabular}
\end{center}
%
\subsubsection*{Gothic (Fraktur).}
%
If gothic letters are {\itshape necessary}, please use those of the
relevant \AmSTeX{} alphabet which are available using the amstex
package of the American Mathematical Society.

In \LaTeX{} only the following gothic letters are available:
\verb|$\Re$| yields $\Re$ and \verb|$\Im$| yields $\Im$. These should
{\itshape not\/} be used when you need gothic letters for your contribution.
Use \AmSTeX{} gothic as explained above. For the real and the imaginary
parts of a complex number within math mode you should use instead:
\verb|$\mathrm{Re}$| (which yields Re) or \verb|$\mathrm{Im}$| (which
yields Im).
%
\subsubsection*{Script.}
%
For script capitals use the coding
\begin{center}
\begin{tabular}{l@{\hspace{1em}which yields\hspace{1em}}c}
\verb|$\mathcal{AB}$| & $\mathcal{AB}$
\end{tabular}
\end{center}
(see p.~42 of  the \LaTeX{} book).
%
\subsubsection*{Special Roman.}
%
If you need other symbols than those below, you could use
the blackboard bold characters of \AmSTeX{},  but there might arise
capacity problems
in loading additional \AmSTeX{} fonts. Therefore  we created
the blackboard bold characters listed below.
Some of them are not esthetically
satisfactory. This need not deter you from using them:
in the final printed form they will be
replaced by the well-designed MT (monotype) characters of
the phototypesetting machine.
\begin{flushleft}
\begin{tabular}{@{}ll@{ yields }
c@{\hspace{1.em}}ll@{ yields }c}
\verb|\bbbc| & (complex numbers)   & $\bbbc$
  & \verb|\bbbf| & (blackboard bold F) & $\bbbf$\\
\verb|\bbbh| & (blackboard bold H) & $\bbbh$
  & \verb|\bbbk| & (blackboard bold K) & $\bbbk$\\
\verb|\bbbm| & (blackboard bold M) & $\bbbm$
  & \verb|\bbbn| & (natural numbers N) & $\bbbn$\\
\verb|\bbbp| & (blackboard bold P) & $\bbbp$
  & \verb|\bbbq| & (rational numbers)  & $\bbbq$\\
\verb|\bbbr| & (real numbers)      & $\bbbr$
  & \verb|\bbbs| & (blackboard bold S) & $\bbbs$\\
\verb|\bbbt| & (blackboard bold T) & $\bbbt$
  & \verb|\bbbz| & (whole numbers)     & $\bbbz$\\
\verb|\bbbone| & (symbol one)      & $\bbbone$
\end{tabular}
\end{flushleft}
\begin{displaymath}
\begin{array}{c}
\bbbc^{\bbbc^{\bbbc}} \otimes
\bbbf_{\bbbf_{\bbbf}} \otimes
\bbbh_{\bbbh_{\bbbh}} \otimes
\bbbk_{\bbbk_{\bbbk}} \otimes
\bbbm^{\bbbm^{\bbbm}} \otimes
\bbbn_{\bbbn_{\bbbn}} \otimes
\bbbp^{\bbbp^{\bbbp}}\\[2mm]
\otimes
\bbbq_{\bbbq_{\bbbq}} \otimes
\bbbr^{\bbbr^{\bbbr}} \otimes
\bbbs^{\bbbs_{\bbbs}} \otimes
\bbbt^{\bbbt^{\bbbt}} \otimes
\bbbz \otimes
\bbbone^{\bbbone_{\bbbone}}
\end{array}
\end{displaymath}
%
\section{References}
\label{refer}
%
There are three reference systems available; only one, of course,
should be used for your contribution. With each system (by
number only, by letter-number or by author-year) a reference list
containing all citations in the
text, should be included at the end of your contribution placing the
\LaTeX{} environment \verb|thebibliography| there.
For an overall information on that environment
see the {\em \LaTeX{} User's Guide \& Reference
Manual\/} by Leslie Lamport, p.~71.

There is a special {\sc Bib}\TeX{} style for LLNCS that works along
with the class: \verb|splncs.bst|
-- call for it with a line \verb|\bibliographystyle{splncs}|.
If you plan to use another {\sc Bib}\TeX{} style you are customed to,
please specify the option \verb|[oribibl]| in the
\verb|documentclass| line, like:
\begin{verbatim}
\documentclass[oribibl]{llncs}
\end{verbatim}
This will retain the original \LaTeX{} code for the bibliographic
environment and the \verb|\cite| mechanism that many {\sc Bib}\TeX{}
applications rely on.
%
\subsection{References by Letter-Number or by Number Only}
%
References are cited in the text -- using the \verb|\cite|
command of \LaTeX{} -- by number or by letter-number in square
brackets, e.g.\ [1] or [E1, S2], [P1], according to your use of the
\verb|\bibitem| command in the \verb|thebibliography| environment. The
coding is as follows: if you choose your own label for the sources by
giving an optional argument to the \verb|\bibitem| command the citations
in the text are marked with the label you supplied. Otherwise a simple
numbering is done, which is preferred.
\begin{verbatim}
The results in this section are a refined version
of \cite{clar:eke}; the minimality result of Proposition~14
was the first of its kind.
\end{verbatim}
The above input produces the citation: ``\dots\ refined version of
[CE1]; the min\-i\-mality\dots''. Then the \verb|\bibitem| entry of
the \verb|thebibliography| environment should read:
\begin{verbatim}
\begin{thebibliography}{[MT1]}
.
.
\bibitem[CE1]{clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and boundary-value problems for
Hamiltonian systems.
Arch. Rat. Mech. Anal. {\bfseries 78} (1982) 315--333
.
.
\end{thebibliography}
\end{verbatim}
The complete bibliography looks like this:
%
\begin{thebibliography}{[MT1]}
%
\bibitem[CE1]{clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and
boundary-value problems for Hamiltonian systems.
Arch. Rat. Mech. Anal. {\bfseries 78} (1982) 315--333
%
\bibitem[CE2]{clar:eke:2}
Clarke, F., Ekeland, I.:
Solutions p\'{e}riodiques, du
p\'{e}riode donn\'{e}e, des \'{e}quations hamiltoniennes.
Note CRAS Paris {\bfseries 287} (1978) 1013--1015
%
\bibitem[MT1]{mich:tar}
Michalek, R., Tarantello, G.:
Subharmonic solutions with prescribed minimal
period for nonautonomous Hamiltonian systems.
J. Diff. Eq. {\bfseries 72} (1988) 28--55
%
\bibitem[Ta1]{tar}
Tarantello, G.:
Subharmonic solutions for Hamiltonian
systems via a $\bbbz_{p}$ pseudoindex theory.
Annali di Matematica Pura (to appear)
%
\bibitem[Ra1]{rab}
Rabinowitz, P.:
On subharmonic solutions of a Hamiltonian system.
Comm. Pure Appl. Math. {\bfseries 33} (1980) 609--633
\end{thebibliography}
%
\subsubsection*{Number-Only System.}
%
For this preferred system do not use the optional argument
in the \verb|\bibitem| command: then, only numbers will
appear for the citations in the text (enclosed in square brackets)
as well as for the marks in your
bibliography (here the number is only end-punctuated without
square brackets).

Subsequent citation numbers in the text are collapsed to ranges.
Non-numeric and undefined labels are handled correctly but no sorting is
done.

E.g., \verb|\cite{n1,n3,n2,n3,n4,n5,foo,n1,n2,n3,?,n4,n5}| -- where
\verb|n|$x$ is the key of the $x^{\mathrm{th}}$ \verb|\bibitem|
command in sequence, \verb|foo| is the key of a \verb|\bibitem| with an
optional argument, and \verb|?| is an undefined reference -- gives
1,3,2-5,foo,1-3,?,4,5 as the citation reference.

\begin{verbatim}
\begin{thebibliography}{1}
\bibitem {clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and boundary-value problems for
Hamiltonian systems.
Arch. Rat. Mech. Anal. {\bfseries 78} (1982) 315--333
\end{thebibliography}
\end{verbatim}
%
\subsection{Author-Year System}
%
References are cited in the text by name and year in parentheses
and should look as follows:
(Smith 1970, 1980), (Ekeland et al. 1985, Theorem 2), (Jones and Jaffe
1986; Farrow 1988, Chap.\,2). If the name is part of the sentence
only the year may appear in parentheses,
e.g.\ Ekeland et al. (1985, Sect.\,2.1)
The reference list should contain all citations occurring in the text,
ordered alphabetically by surname (with initials following). If there
are several works by the same author(s) the references should be listed
in the appropriate order indicated below:
\begin{alpherate}
\setlength{\hfuzz}{5pt}
\item
One author: list works chronologically;
\item
Author and same co-author(s): list works chronologically;
\item
Author and different co-authors: list works alphabetically
according to co-authors.
\end{alpherate}
If there are several works by the same author(s) and in the same year,
but which are cited separately, they should be distinguished by the use
of ``a'', ``b'' etc., e.g.\ (Smith 1982a), (Ekeland et al. 1982b).
%
\subsubsection*{How to Code Author-Year System.}
%
If you want to use this system you have to specify the option
\verb|[citeauthoryear]| in the \verb|documentclass|, like:
\begin{verbatim}
\documentclass[citeauthoryear]{llncs}
\end{verbatim}
Write your citations in the text explicitly except for the year, leaving
that up to \LaTeX{} with the \verb|\cite| command. Then give only the
appropriate year as the optional argument (i.e. the label in square
brackets) with the \verb|\bibitem| command(s).\\[2mm]
{\itshape Sample Input}
\begin{verbatim}
The results in this section are a refined version
of Clarke and Ekeland (\cite{clar:eke}); the minimality result of
Proposition~14 was the first of its kind.
\end{verbatim}
The above input produces the citation: ``\dots\ refined version of
Clarke and Ekeland (1982); the minimality\dots''. Then the
\verb|\bibitem| entry of \verb|clar:eke| in the \verb|thebibliography|
environment should read:
\begin{verbatim}
\begin{thebibliography}{}  % (do not forget {})
.
.
\bibitem[1982]{clar:eke}
Clarke, F., Ekeland, I.:
Nonlinear oscillations and boundary-value problems for
Hamiltonian systems.
Arch. Rat. Mech. Anal. {\bfseries 78} (1982) 315--333
.
.
\end{thebibliography}
\end{verbatim}
{\itshape Sample Output}
\bibauthoryear
%
\end{document}

### 2013-05-30 draft.tex
add some

@@
 
+The primal update contains a $\ell_1$-sampling process for the choice of $i_t$, which takes $O(n)$ time, and the update of $w_t$ takes $O(d)$ time.
+The update of t can be done using a simple greedy algorithm which takes O(n) time. The primal update contains
+a `2-sampling process for the choice of jt (O(d) time), and an update of
+p (O(n) time). Altogether, each iteration takes O(n + d) time
+    \comment{Will add more on algorithm design explanation later in next version of draft}
+
 \section{Parallel Framework of Learning Algorithms for PLR} \label{sec:framework}
@@
 
-    \comment{Will add more on algorithm design explanation later in next version of draft}
+This parallel design generally follows the framework of sequential sublinear algorithm.
+It remains to have two computational components in each iteration: the primal update part from line 4 to line 12 and dual update part from line 13 to line 21.
+Within the primal update part, there has been a parallel implementation period from line 4 to line 11, and also a unavoidable sequential period as illustrated in line 12.
+Within the dual part, it is the same situation that a parallel implementation period from line 14 to 20 is surrounded by sequential periods for line 13 and line 21.
+
+For the parallelization period in the \textit{primal mapreduce job}, we take advantage of the MapReduce design that takes in every data instance in the training matrix.
+Instead of the fashion in the sequential algorithm that we only sample a data instance in the primal update step, we compute gradients from "almost" all data instances and make the weighted average value according to vector $\bp$ as the output gradient for update.
+The details of this algorithm design is shown in \textbf{Procedure Primal-Map(inputfile)} and \textbf{Procedure Primal-Reduce(key in, value in)}.
+Here, we employ a randomization when we compute those "almost" all gradients.
+As you can interpret from line 7 and 8 from \textbf{Procedure Primal-Map(inputfile)}, if $r=0$, then all data instances are computed.
+As the expectation value for $\bp_t{i_t}$ is $\frac{1}{n}$, we normally set $r$ to range from 0 to 1.
+For the parallelization period in the \textit{dual mapreduce job}, we actually implement an embarrasingly
 
@@
     \comment{4: A possible level2 parallelization}
-
-    \comment{5: The randomization design in primal map}
 

### 2013-06-01 draft.tex
add some 2

@@
 We focus on algorithm level and employ three different parallel computation systems with three different types of parallel algorithms to efficiently improve scalability.
-Hadoop, Mahout and Spark are existing well-known parallel frameworks that can be implemented with large scale machine learning algorithms.
-Parallel gradient Descent stochastic gradient descent are two existing state-of-art algorithms for parameter optimization in PLR.
-We also present a novel parallel sublinear method and make a comparison between these algorithms implemented on different systems.
+Hadoop, Mahout and Spark are three existing well-known parallel systems that can be implemented with large scale machine learning algorithms.
+Parallel gradient Descent and stochastic gradient descent are two existing state-of-art algorithms for parameter optimization in PLR.
+We also present a novel parallel sublinear method based on its sequential version.
+We then make a comparison between these algorithms implemented on different systems.
 As the outcome shows, we claim parallel sublinear method implemented on Spark is the most computational efficient way to solve PLR for general purpose.
@@
 Our motivation for exploring PLR as a fast classifier to be used in data mining applications is its maturity.
-It has a statistical foundation which, in the right circumstances, could be used to extend classification results into a deeper analysis.
+It has a statistical foundation which could be used to extend classification results into a deeper analysis.
 
@@
 After a thorough survey, we choose three unique and best-known systems to test: Hadoop~\cite{white2012hadoop}, Mahout~\cite{mahoutscalable} and Spark~\cite{zaharia2010spark}.
-Hadoop uses HDFS~\cite{borthakur2008hdfs} and MapReduce~\cite{dean2008mapreduce}, Mahout runs on Apache Hadoop~\cite{gropp1999using} and make improvements in the low level code, and Spark features for iterative algorithms and also supports HDFS.
+Hadoop employs HDFS~\cite{borthakur2008hdfs} and MapReduce~\cite{dean2008mapreduce}.
+Mahout runs on Apache Hadoop~\cite{gropp1999using} and make improvements in the low level code.
+Spark features for iterative algorithms and also supports HDFS.
 We will introduce the features of them separately in detail in related work section.
@@
 If we take a step back and go back to the general gradient descent to solve PLR, we can find that it can be actually embarrassingly parallel.
-We can take in all the data at the same iteration and just compute the gradient in a Map-Reduce fashion.
+We can take in all the data at the same iteration and just compute the gradient in a MapReduce fashion.
 We can further speed up the runtime by employing sublinear algorithms~\cite{peng2012sublinear} for PLR via the use of stochastic approximation idea.
 This methods access a single feature of training vectors instead of entire training vectors at each iteration.
-We propose a parallel version of this algorithm and achieve the result of comparable accuracy while faster convergent.
+We propose a parallel version of this algorithm and achieve the result of comparable accuracy while being faster convergent.
 
@@
 Section~\ref{sec:rew} discusses some related work and three different systems.
-In Section~\ref{sec:plr}, we review the penalized logistic regression model.
+In Section~\ref{sec:plr}, we review the penalized logistic regression model and the sublinear method.
 In Section~\ref{sec:framework}, we present the parallel framework of all three different algorithms for PLR.
@@
 \section{Related Work} \label{sec:rew}
-
 In big data scenario, large datasets require us to develop machine learning algorithms towards a more efficient and more parallelized end.
 Researchers have already done much work to cater for the needs of massive datasets.
-Early work like PSVM (Parallel Support Vector Machines)~\cite{chang2011psvm} employed an approximation matrix decomposition method based on row selections to reduce the memory when running the algorithm.
+Early work like PSVM \textit{(Parallel Support Vector Machines)}~\cite{chang2011psvm} employed an approximation matrix decomposition method based on row selections to reduce the memory when running the algorithm.
 It can then increase the number of participated parallel computation nodes to several hundreds.
-Later, the work of PLDA (Parallel Latent Dirichlet Allocation)~\cite{wang2009plda} further improve the computational efficiency through the use of sampling methods.
-The proposed parallel algorithm in Hadoop is robust, for it has fault tolerance of machines, taking the advantage of Hadoop.
+Later, the work of PLDA \textit{(Parallel Latent Dirichlet Allocation)}~\cite{wang2009plda} further improve the computational efficiency of the LDA model through the use of sampling methods.
+The proposed parallel algorithm in Hadoop is robust, for it has fault tolerance of machine failures, taking the advantage of Hadoop.
 Recently, the work by Dean et al.\cite{le2011building} showed that the advantage of parallelization is fully taken in deep learning algorithms.
@@
 The Apache Hadoop~\cite{white2012hadoop} software library is a framework that allows for the distributed processing of large data sets across clusters of computers using simple programming models.
-It is designed to scale up from single servers to thousands of machines, each offering local computation and storage.
-Rather than rely on hardware to deliver high-availability, the library itself is designed to detect and handle failures at the application layer, so delivering a highly-available service on top of a cluster of computers, each of which may be prone to failures.
 It is an open-source software framework that supports data-intensive distributed applications, licensed under the Apache v2 license.
@@
 Hadoop was derived from Google's MapReduce and Google File System (GFS) papers.
+Hadoop is written in the Java programming language and is an Apache top-level project being built and used by a global community of contributors.
+The entire Apache Hadoop platform is now commonly considered to consist of the Hadoop kernel, MapReduce and Hadoop Distributed File System (HDFS), as well as a number of related projects, including Apache Hive and Apache HBase.
+Hadoop is designed to scale up from single servers to thousands of machines, each offering local computation and storage.
 The Hadoop framework transparently provides both reliability and data motion to applications.
@@
 Both map/reduce and the distributed file system are designed so that node failures are automatically handled by the framework.
-The entire Apache Hadoop platform is now commonly considered to consist of the Hadoop kernel, MapReduce and Hadoop Distributed File System (HDFS), as well as a number of related projects ¨C including Apache Hive, Apache HBase, and others.
-Hadoop is written in the Java programming language and is an Apache top-level project being built and used by a global community of contributors.
+Rather than rely on hardware to deliver high-availability, the library itself is designed to detect and handle failures at the application layer, so delivering a highly-available service on top of a cluster of computers, each of which may be prone to failures.
 
 The Apache Mahout~\cite{mahoutscalable} machine learning library's goal is to build scalable machine learning libraries.
-It is scalable to reasonably large data sets.
+It is scalable to reasonably large datasets.
 Their core algorithms for clustering, classification and batch based collaborative filtering are implemented on top of Apache Hadoop using the map/reduce paradigm.
 The core libraries are highly optimized to allow for good performance also for non-distributed algorithms.
-It is also scalable to support business cases.
-Mahout is distributed under a commercially friendly Apache Software license.
+It is also scalable to support business cases. Mahout is distributed under a commercially friendly Apache Software license.
 Currently Mahout supports mainly four use cases: Recommendation mining takes users' behavior and from that tries to find items users might like.
@@
 text documents and groups them into groups of topically related documents.
-Classification learns from existing categorized documents what documents of a specific category look like and is able to assign unlabeled documents to the (hopefully) correct category.
+Classification learns from existing categorized documents what documents of a specific category look like and is able to assign unlabeled documents to the correct category.
 Frequent itemset mining takes a set of item groups (terms in a query session, shopping cart content) and identifies, which individual items usually appear together.
-Mahout currently supports many machine learning algorithms including collaborative filtering, user and item based recommenders, K-Means, fuzzy K-Means clustering, mean shift clustering, dirichlet process clustering, Latent Dirichlet Allocation, singular value decomposition, parallel frequent pattern mining, complementary naive bayes classifier, random forest decision tree based classifier.
+Mahout currently supports many machine learning algorithms including collaborative filtering, user and item based recommenders, K-Means, fuzzy K-Means clustering, mean shift clustering, dirichlet process clustering, Latent Dirichlet Allocation, singular value decomposition, parallel frequent pattern mining, complementary naive bayes classifier and random forest decision tree based classifier.
 
-Spark~\cite{zaharia2010spark} was developed in the UC Berkeley AMPLab. It is an open source cluster computing system that aims to make data analytics fast ¡ª both fast to run and fast to write.
+Spark~\cite{zaharia2010spark} is developed in the UC Berkeley AMPLab. It is an open source cluster computing system that aims to make data analytics fast: both fast to run and fast to write.
 To run programs faster, Spark provides primitives for in-memory cluster computing: a job can load data into memory and query it repeatedly much more quickly than with disk-based systems like Hadoop MapReduce.
@@
 
-Recently, Clarkson et al. \cite{clarkson2010sublinear} proposed a new method by taking advantage of randomized algorithms.
+Recently, Clarkson et al.~\cite{clarkson2010sublinear} proposed a new method by taking advantage of randomized algorithms.
 They presented sublinear-time approximation algorithms for optimization problems arising in machine learning, such as linear classifiers and minimum enclosing balls.
@@
 They also proved lower bounds which show the running times to be nearly optimal on the unit-cost RAM model.
-Hazan et al.
-\cite{hazanbeating} exploited sublinear approximation approach to the linear SVM with $\ell_2$-penalty, from which we were inspired and borrowed some of the ideas (We generally refer to them as the ETN framework in Section~\ref{sec:framework}).
-Later on, Cotter et al.
-\cite{cotter2012kernelized} extended the work to kernelized SVM cases.
-In \cite{hazan2011optimal}, Hazan et al.
+Hazan et al.~\cite{hazanbeating} exploited sublinear approximation approach to the linear SVM with $\ell_2$-penalty, from which we were inspired and borrowed some of the ideas.
+Later on, Cotter et al.~\cite{cotter2012kernelized} extended the work to kernelized SVM cases.
+In~\cite{hazan2011optimal}, Hazan et al.
 applied the sublinear approximation approach for solving ridge ($\ell_2$-regularized) and lasso ($\ell_1$-regularized) linear regression.
-Garber and Hazan \cite{garberapproximating} developed the method in semidenfinite programming (SDP).
+Garber and Hazan~\cite{garberapproximating} developed the method in semidenfinite programming (SDP).
+Peng et al.~\cite{peng2012sublinear} applied the method in PLR and developed sequential sublinear algorithms for both $\ell_1$-penalty and $\ell_2$-penalty.
+% can change the style to have {items} to be more organized
 
 \section{Penalized Logistic Regression Models and Sublinear Methods} \label{sec:plr}
-
 Logistic regression is a widely used method for solving classification problems.
@@
 \subsection{Penalized Logistic Regression Models}
-
 We assume that $\w$ follows a Gaussian distribution with mean $\0$ and covariance matrix $\lambda \I_d$ where $\I_d$ is the $d{\times}d$ identity matrix, i.e. $\w \thicksim N(\0, \lambda \I_d)$.
@@
 \subsection{Sublinear Algorithms}
-
 The framework of sublinear algorithms is a hybrid method to handle hard margin and soft margin separately and simultaneously.
@@
 \item[{(1)}] \; An instance $i\in \{1,\ldots, n\}$ is chosen according to a probability vector $\bp$;
-\item[{(2)}] \; The primal variable $\bw$ is updated according to the derivative of $f_i(\bw,b)$ and the soft margin, via an online update with regret.
+\item[{(2)}] \; The primal variable $\bw$ is updated according to the gradient computed based on the sampled instance $\textbf{x}_i$, via an online update with regret.
 \end{enumerate}
@@
 \begin{enumerate}
-\item[{(1)}] \; A stochastic estimate of $f_i(\bw,b)$ plus the soft margin is obtained, which can be computed in $O(1)$ time per term;
+\item[{(1)}] \; A stochastic estimate of hard margin plus soft margin is obtained, which can be computed in $O(1)$ time per term;
 \item[{(2)}] \; The probability vector $\bp$ is updated based on the above computed terms by using the \textit{Multiplicative Updates} (MW) framework~\cite{arora2005multiplicative} for online optimization over the simplex.
@@
 \subsection{Sequential Sublinear Algorithm for Logistic Regression} \label{sec:l2alg}
-
-We use the following notations.
+We use the following notations to define sequential sublinear algorithm for penalized logistic regression.
+Much of them are borrowed from~\cite{peng2012sublinear}.
+We will also use these notations in other algorithm definitions in the following.
 
@@
 	\noalign{\smallskip}
-	1:	Input parameters: $\varepsilon, \nu, X, Y$ \\
+	1:	Input parameters: $\varepsilon, \nu~or~\gamma, X, Y$ \\
 	2:	Initialize parameters: $T, \eta, {\mathbf{u}}_{0}, {\bw}_{1}, {\mathbf{\bq}}_{1}, {b}_{1}$\\
@@
 	7:	\tspace ${\bu}_{t}\leftarrow {\bu}_{t-1}+\frac{coef}{\sqrt{2T}}{\mathbf{x}}_{{i}_{t}}$ \\
-	8:	\tspace ${\bw}_{t}\leftarrow {\bu}_{t}/\max \left\{1,\|{\bu}_{t}\|_2 \right\}$ \\
-    9:  \tspace ${b}_{t}\leftarrow \sgn\lc {{\bp}_{t}}^{T}\mathbf{y}\rc$ \\
-	10:	\tspaces Choose ${j}_{t}\leftarrow j$ with probability ${{\bw}_{t}\lj}^{2}/{\|{\bw}_{t}\|_2}^{2} $ \\
-	11:	\tspaces Iterations: $i=1 \sim n$ \\
-	12:	\tspaces\tspace $\sigma \leftarrow \mathbf{x}_{i} \lc {j}_{t}\rc{\|{\bw}_{t}\|_2}^{2}/{\bw}_{t}\lc {j}_{t} \rc+{\bxi}_{t}\li+{y}_{i}{b}_{t}$ \\
-	13:	\tspaces\tspace $\hat{\sigma} \leftarrow clip\lc \sigma,1/\eta \rc$ \\
-	14:	\tspaces\tspace ${\bq}_{t+1}\li \leftarrow {\bp}_{t}\li\lc 1-\eta\hat{\sigma} + {\eta}^{2}{\hat{\sigma}}^{2} \rc$ \\
-	15:	Output: $\bar{\bw}=\frac{1}{T}\sum_{t}{\bw}_{t},\bar{b}=\frac{1}{T}\sum_{t}{b}_{t}$ \\
+    8:  \tspace Update soft margin $\bxi_t$ if input $\nu$ for $\ell_2$-penalty \\
+    9:  \tspace Update $\bu_t$ by soft-thresholding operations if input $\gamma$ for $\ell_1$-penalty \\
+	10:	\tspaces ${\bw}_{t}\leftarrow {\bu}_{t}/\max \left\{1,\|{\bu}_{t}\|_2 \right\}$ \\
+    11: \tspaces ${b}_{t}\leftarrow \sgn\lc {{\bp}_{t}}^{T}\mathbf{y}\rc$ \\
+	12:	\tspaces Choose ${j}_{t}\leftarrow j$ with probability ${{\bw}_{t}\lj}^{2}/{\|{\bw}_{t}\|_2}^{2} $ \\
+	13:	\tspaces Iterations: $i=1 \sim n$ \\
+	14:	\tspaces\tspace $\sigma \leftarrow \mathbf{x}_{i} \lc {j}_{t}\rc{\|{\bw}_{t}\|_2}^{2}/{\bw}_{t}\lc {j}_{t} \rc+{\bxi}_{t}\li+{y}_{i}{b}_{t}$ \\
+	15:	\tspaces\tspace $\hat{\sigma} \leftarrow clip\lc \sigma,1/\eta \rc$ \\
+	16:	\tspaces\tspace ${\bq}_{t+1}\li \leftarrow {\bp}_{t}\li\lc 1-\eta\hat{\sigma} + {\eta}^{2}{\hat{\sigma}}^{2} \rc$ \\
+	17:	Output: $\bar{\bw}=\frac{1}{T}\sum_{t}{\bw}_{t},\bar{b}=\frac{1}{T}\sum_{t}{b}_{t}$ \\
 	\hline
@@
 
-The primal update contains a $\ell_1$-sampling process for the choice of $i_t$, which takes $O(n)$ time, and the update of $w_t$ takes $O(d)$ time.
-The update of t can be done using a simple greedy algorithm which takes O(n) time. The primal update contains
-a `2-sampling process for the choice of jt (O(d) time), and an update of
-p (O(n) time). Altogether, each iteration takes O(n + d) time
-    \comment{Will add more on algorithm design explanation later in next version of draft}
+In the pseudo-code of Algorithm 1, line 4 to line 11 is the primal part, where $coef$ is the estimator of the gradient.
+Line 12 to line 16 is the dual part, where $\sigma$ serves as an estimator of hard margin plus soft margin.
+$\sigma$ also serves as the derivative of $\bp(i)$.
+Although the computation of line 15 and 16 makes $\hat{\sigma}$ a biased approximation, it is critical to the stability of the algorithm. The resulting bias is negligible in our approach.
+We show the sublinear algorithm in a uniform way for both $\ell_2$-penalty and $\ell_1$-penalty concisely.
+For more details, you can refer to paper~\cite{peng2012sublinear} to expand on line 8 and line 9.
+
+In the sequential mode, the primal update contains a $\ell_1$-sampling process for the choice of $i_t$, which takes $O(n)$ time, and the update of $w_t$ takes $O(d)$ time.
+And the dual update contains a $\ell_2$-sampling process for the choice of $j_t$ in $O(d)$ time, and an update of $\bp$ in $O(n) time$.
+Altogether, each iteration takes $O(n+d)$ time, which is sublinear to the dataset size.
 
 \section{Parallel Framework of Learning Algorithms for PLR} \label{sec:framework}
+In this section, we will first describe our parallel sublinear algorithm implemented in Hadoop MapReduce.
+Then we will show a slightly different version implemented in Spark.
+We will also formally introduce the traditional parallel gradient algorithm we use in Spark and describe the online stochastic gradient descent method used in Mahout.
 
-\subsection{Parallel Sublinear algorithms in Hadoop (MapReduce)}
-    In this section, we develop an approach to solve sublinear learning for penalized logistic regression using the architecture of MapReduce.
+\subsection{Parallel Sublinear algorithms in Hadoop MapReduce}
+We develop an approach to solve sublinear learning for penalized logistic regression using the architecture of MapReduce.
+The pseudo-code of Algorithm 2, Procedure for Primal-Map, Procedure for Primal-Reduce, Procedure for PrimalUpdate, Procedure for Dual-Map, and Procedure for DualUpdate explain the critical parts of this algorithm.
 	\begin{table}[ht]
@@
     16: \tspaces job\_dual $\leftarrow$ new MapReduce-Job(conf\_dual) \\
-    17: \tspaces conf\_dual.passParameters($d, jt, b_{t+1}, \eta$) \\
+    17: \tspaces conf\_dual.passParameters($d, j_t, b_{t+1}, \eta$) \\
     18: \tspaces job\_primal.setInputPath("...") \\	
@@
 Within the dual part, it is the same situation that a parallel implementation period from line 14 to 20 is surrounded by sequential periods for line 13 and line 21.
+Moreover, as the primal part and dual part are decoupled in the sense of the parameters that they affect. We can start these two separate MapReduce jobs in a iteration simultaneously.
+This brings us further parallelization and makes the algorithm more efficient. 
+This framework is shown explicitly in Fig.~\ref{fig:frame}.
+
+\begin{figure}[tb] \label{fig:frame}
+\center \includegraphics[height=3.5cm,width=6cm]{img/framework.png}
+\caption{Parallel implementation flow chart for PSUBPLR-MR}
+\end{figure}
 
@@
 As you can interpret from line 7 and 8 from \textbf{Procedure Primal-Map(inputfile)}, if $r=0$, then all data instances are computed.
-As the expectation value for $\bp_t{i_t}$ is $\frac{1}{n}$, we normally set $r$ to range from 0 to 1.
-For the parallelization period in the \textit{dual mapreduce job}, we actually implement an embarrasingly
+As the expectation value for $\bp_t(i_t)$ is $\frac{1}{n}$, we normally set $r$ to range from 0 to 1.
+For the parallelization period in the \textit{dual mapreduce job}, we actually implement an embarrassingly parallel operation.
+It simply computes an individual value for each data instance in a parallel mode. It does not even need a reduce session.
 
-    \comment{1: Parameter passing Issues}
+There are also three more things that have to be addressed here.
+First is the parameter passing issues. It critical to choose an efficient way to pass the updated parameters between iteration and even between different MapReduce jobs.
+It is even more challenging when we have to deal with HDFS. It is clear that the fastest communication way is to pass parameters by \textit{Configuration()}.
+However, it always has memory buffer size limits, and will greatly impair scalability when the number of parameters is huge.
+Another way is to compress the parameter sequence in a string when sending and uncompress them when receiving.
+It has computational overhead and it still can not avoid the issue of memory buffer limit.
+Thinking back on the philosophy of the design of Hadoop, the natural thing is to pass parameters by file, the same way to pass all the data.
+We admit that it is inefficient, but it is the only way to support for large datasets.
 
-    \comment{2: L1 and L2 small changes}
+The second issue is the small changes we make to cater for the $\ell_2$-penalty and $\ell_1$-penalty. The changes is only made in \textbf{Procedure PrimalUpdate}.
+It does not affect little for the implementation, and the extension is just the same as that in \textbf{Algorithm SLLR}.
+To have a brief and standard framework, we omit the explanation here.
 
-    \comment{3: code details to cater to sparsity}
-
-    \comment{4: A possible level2 parallelization}
-
-    \comment{Maybe a graph to illustrate sequential part and parallelization part}
+The datasets are always sparse for PLR is when data dimensionally is high. This makes us focus on dealing with data sparsity issue when writing code.
+This is the third important thing for the algorithm, though it reflects nowhere from the pseudo-code.
+Instead of naively writing the simple code for data intensive situations, we assign the index value for each data value in the sparse vector, and all computations are changed accordingly.
+This gives us great efficiency improvement, and all results in section~\ref{sec:experiment} are using the code for sparsity.
 
 \subsection{Parallel Sublinear algorithms in Spark}
+The algorithm to solve sublinear learning for penalized logistic regression in Spark is shown below.
+In the pseudo-code of Algorithm 3, Procedure for PrimalUpdate and Procedure for Dual-Map are the same as those in \textbf{Algorithm  PSUBPLR-MR}.
     \begin{table}[ht]
@@
 
-    \comment{Will add more on algorithm design explanation later in next version of draft}
+This parallel design is very similar to that of \textbf{Algorithm  PSUBPLR-MR}.
+The most important difference is the \textit{cache()} operation in line 3.
+To make it work in Spark, we follow the rules to construct an RDD for each data instance.
+Also to cater for data sparsity, the design is the every data value correspond to its individual index. And the index also participate in the computation along with the value.
+We also omit the changes for $\ell_2$-penalty and $\ell_1$-penalty here to make the algorithm easier to be understood.
 
-    \comment{1: Parsed Data Structure Design}
-
-    \comment{2: L1 and L2 small changes}
-
-    \comment{3: code details to cater to sparsity}
-
-    \comment{4: Emphasis on .cahche() }
-
-    \comment{5: Similarity with PSUBPLR-MR}
+We can now study the running time of parallel sublinear method for PLR.
+In parallel mode, the primal update contains an update of $w_t$, which takes $O(n)$ time.
+And the dual update contains a $\ell_2$-sampling process for the choice of $j_t$ in $O(d)$ time, and an update of $\bp$ in $O(1) time$.
+Altogether, each iteration takes $O(n+d)$ time, which is sublinear to the dataset size.
+Compared to the analysis of sequential algorithm, parallelization does not change computational complexity.
+However, by reducing the constant coefficient from 2 to 1 in each iteration, it can be two times faster than sequential sublinear algorithm theoretically.
+Moreover, by starting two separate MapReduce jobs in a iteration simultaneously, the running time can be reduced to $O(max\{n,d\})$.
 
 \subsection{Parallel Gradient Descent in Spark}
+The parallel gradient descent method to solve PLR in Spark is shown below.
     \begin{table}[ht]
@@
 
-    \comment{Will add more on algorithm design explanation later in next version of draft}
-
-    \comment{1: L1 and L2 small changes}
-
-    \comment{2: Similarity with PSUBPLR-SPARK}
+In the pseudo-code of Algorithm 4, we can find that it is implemented in an embarrassingly parallel mode.
+We can take in all the data at the same iteration and just compute the gradient in a MapReduce fashion.
+As for the \textit{cache()} operation and RDD design for data sparsity, it is the same as \textbf{Algorithm PSUBPLR-SPARK}.
 
@@
 Though SGD is an inherently sequential algorithm, it is blazingly fast and thus it is not a problem for Mahout's implementation to handle training sets of tens of millions of examples.
-With the down-sampling typical in many data-sets, this is equivalent to a dataset with billions of raw training examples.
-The SGD system in Mahout is an online learning algorithm which means that you can learn models in an incremental fashion and that you can do performance testing as your system runs.
-Often this means that you can stop training when a model reaches a target level of performance.
-The SGD framework includes classes to do on-line evaluation using cross validation (the CrossFoldLearner) and an evolutionary system to do learning hyper-parameter optimization on the fly (the AdaptiveLogisticRegression).
-The AdaptiveLogisticRegression system makes heavy use of threads to increase machine utilization.
-The way it works is that it runs 20 CrossFoldLearners in separate threads, each with slightly different learning parameters.
+With the down-sampling typical in many datasets, this is equivalent to a dataset with billions of raw training examples.
+The SGD system in Mahout is an online learning algorithm which means that you can learn models in an incremental fashion and that we can do performance testing as your system runs.
+This also means that we can stop training when a model reaches a target level of performance.
+The SGD framework includes classes to do online evaluation using cross validation (the \textit{CrossFoldLearner}) and an evolutionary system to do learning hyper-parameter optimization on the fly (the \textit{AdaptiveLogisticRegression}).
+The \textit{AdaptiveLogisticRegression} system makes heavy use of threads to increase machine utilization.
+The way it works is that it runs 20 \textit{CrossFoldLearners} in separate threads, each with slightly different learning parameters.
 As better settings are found, these new settings are propagating to the other learners.
 
-Because the SGD algorithms need to have fixed length feature vectors and because it is a pain to build a dictionary ahead of time, most SGD applications use the hashed feature vector encoding system that is rooted at FeatureVectorEncoder.
-The basic idea is that you create a vector, typically a RandomAccessSparseVector, and then you use various feature encoders to progressively add features to that vector.
+Because the SGD algorithms need to have fixed length feature vectors and because it is a pain to build a dictionary ahead of time, most SGD applications use the hashed feature vector encoding system that is rooted at \textit{FeatureVectorEncoder}.
+The basic idea is that you create a vector, typically a \textit{RandomAccessSparseVector}, and then you use various feature encoders to progressively add features to that vector.
 The size of the vector should be large enough to avoid feature collisions as features are hashed.
@@
 You can normally encode either a string representation of the value you want to encode or you can encode a byte level representation to avoid string conversion.
-In the case of ContinuousValueEncoder and ConstantValueEncoder, it is also possible to encode a null value and pass the real value in as a weight.
-This avoids numerical parsing entirely in case you are getting your training data from a system like Avro.
+In the case of \textit{ContinuousValueEncoder} and \textit{ConstantValueEncoder}, it is also possible to encode a null value and pass the real value in as a weight.
 
-    \comment{Will add more on algorithm design explanation later in next version of draft}
-
-    \comment{1: Add presudo code}
-
-    \comment{2: function call by OnlineLogisticRegression() and corresponding feature vector encoding (will ask Liang Ding to help to write)}
+In our implementation, we use \textit{RandomAccessSparseVector} for data sparsity and the function call by \textit{OnlineLogisticRegression} to train.
+We also do the cross validation part. However, to be synchronized with other methods, we write our own code to do cross validation.
 
@@
 
+\comment{further parallelization in PSUBPLR-MR, Primal Map is the bottleneck}
+\comment{parameter passing issues in PSUBPLR-MR, the effect in small dataset}
+\comment{MR job start time}
 Analysis points:

### 2013-06-02 draft.tex
add graphs

@@
 In this section, we conduct an empirical analysis of our algorithms.
-Particularly, we illustrate test errors in terms of accuracy and convergence in terms of MAP, both with respect to running time.
 
-We choose five open datasets to run all four test programs:	
+We choose five open datasets to run all six test programs:	
 The	Simulated \textbf{2d} dataset has 2 features and 200 instances.
@@
 We split it into a training set of 2356130 instances and a test set of 20000 instances.
+Apart from the Simulated \textbf{2d} dataset, other four datasets are all sparse. Details are shown in Table~\ref{tab:table1}.
 We randomly repeat such split 20 times and our analysis is based on the average performance of 20 repetitions.
+
+%Particularly, we illustrate test errors in terms of accuracy and convergence in terms of MAP, both with respect to running time.
 
@@
 \hline
-    2d             & 2             & 200            & ...      & ...                 & 1.000 \\
+    2d             & 2             & 200            & 1.0                  & 400                 & 1.000 \\
 \hline
-    20NewsGroup    & 16428         & 1988           & ...      & ...                 & 1.006 \\
+    20NewsGroup    & 16428         & 1988           & $7.384\times10^{-3}$ & 238511              & 1.006 \\
 \hline
-    Gisette        & 5000          & 7000           & ...      & ...                 & 1.000 \\
+    Gisette        & 5000          & 7000           & 0.12998              & 4549319             & 1.000 \\
 \hline
-    ECUESpam       & 100249        & 10678          & ...      & ...                 & 5.882 \\
+    ECUESpam       & 100249        & 10687          & $2.563\times10^{-3}$ & 2746159             & 5.882 \\
 \hline
-    URL-Reputation & 3231961       & 2376130        & ...      & ...                 & ... \\
+    URL-Reputation & 3231961       & 2376130        & $3.608\times10^{-35}$ & 277058644           & 0.500 \\
 \hline
@@
 
+The cluster that we implement on has the following configurations shown in Table~\ref{tab:table2}.
 \begin{table}[h]
@@
 \hline
-    CPU Model & ... \\
+    CPU Model & Intel Xeon E5-1410: 2.80GHz \\
 \hline
@@
 \hline
-    Number of CPU per node & 8\\
+    Number of CPU per node & 4 Cores, 8 Threads \\
 \hline
-    Memory per node & 12G \\
+    RAM per node & 16G \\
 \hline
-    Disk per node & 2T \\
+    Disk per node & 4T HDD\\
 \hline
-    Cache Size per node & ... \\
+    Interconnection Method & Gigabyte Ethernet  \\
 \hline
@@
 
-\comment{Will add more on experimental results later in next version of draft}
+2d-dataset (separation graph)
+\begin{figure}[tb] \label{fig:02}
+\center \includegraphics[height=5cm,width=7cm]{img/show-2d.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:03}
+\center \includegraphics[height=4.5cm,width=6cm]{img/2d_accuracy_iteration.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:04}
+\center \includegraphics[height=4.5cm,width=6cm]{img/20NewsGroup_accuracy_iteration.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:05}
+\center \includegraphics[height=4.5cm,width=6cm]{img/Gisette_accuracy_iteration.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:6}
+\center \includegraphics[height=4.5cm,width=6cm]{img/ECUESpam_accuracy_iteration.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:07}
+\center \includegraphics[height=4.5cm,width=6cm]{img/URL-Reputation_accuracy_iteration.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:08}
+\center \includegraphics[height=5cm,width=10cm]{img/all_time.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:09}
+\center \includegraphics[height=5cm,width=10cm]{img/2d_time.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:10}
+\center \includegraphics[height=5cm,width=10cm]{img/20NewsGroup_time.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:11}
+\center \includegraphics[height=5cm,width=10cm]{img/Gisette_time.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:12}
+\center \includegraphics[height=5cm,width=10cm]{img/ECUESpam_time.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:13}
+\center \includegraphics[height=5cm,width=10cm]{img/URL-Reputation_time.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:14}
+\center \includegraphics[height=5cm,width=10cm]{img/fault_tolerance.png}
+\caption{2d Dataset, Visual Result}
+\end{figure}
 
@@
 
-\comment{3: add 5 line graphs;one dataset each;x:iteration number;y:MAP;6 lines}
+%\comment{3: add 5 line graphs;one dataset each;x:iteration number;y:MAP;6 lines}
 
@@
 \comment{MR job start time}
+\comment{baseline liblinear}
+\comment{2d test method}
+\comment{not all converge at the iteration shown}
+\comment{symbol review}
+\comment{single reducer of spark}
+\comment{Iteration Number for SLLR explain}
+\comment{Liblinear Url result}
+\comment{fault tolerance: on url dataset,6 nodes}
 Analysis points:
@@
 \hline
-Liblinear  & 93.0\% & 92.0\% & 97.4\% & 97.1\% & 96.2\% \\
+Liblinear  & 93.0\% & 92.0\% & 97.4\% & 97.1\% & $96.2\%^*$ \\
 \hline
-Sublinear  & 93.5\% & 91.5\% & 94.8\% & 92.3\% & 94.2\% \\
+SLLR       & 93.5\% & 91.5\% & 94.8\% & 92.3\% & 94.2\% \\
 \hline
-PSublinear & 93.5\% & 90.5\% & 94.6\% & 91.7\% & 93.8\% \\
+PSUBPLR-MR & 93.5\% & 90.5\% & 94.6\% & 91.7\% & 93.8\% \\
 \hline
-Spark      & 93.5\% & 92.0\% & 97.0\% & 93.7\% & 96.0\% \\
+PGDPLR-SPARK & 93.5\% & 92.0\% & 97.0\% & 93.7\% & 96.0\% \\
 \hline
-subSpark   & 93.5\% & 90.5\% & 95.8\% & 91.7\% & 94.0\% \\
+PSUBPLR-SPARK & 93.5\% & 90.5\% & 95.8\% & 91.7\% & 94.0\% \\
 \hline
@@
 \hline
-Liblinear  & 0.078s & 0.793s & 2.364s & 13.161s & 519.115s \\
+Liblinear  & 0.078s & 0.793s & 2.364s & 13.161s & $519.115s^*$ \\
 \hline
-Sublinear  & 1.761s & 20.046s & 130.451s & 1028.185s & 3248.473s \\
+SLLR       & 1.761s & 20.046s & 130.451s & 1028.185s & 3248.473s \\
 \hline
-PSublinear & 120.186s & 1360.854s & 3687.941s & 11478.706s & 16098.260s \\
+PSUBPLR-MR & 120.186s & 1360.854s & 3687.941s & 11478.706s & 16098.260s \\
 \hline
-Spark      & 0.681s & 10.517s & 99.156s & 924.020s & 3615.780s \\
+PGDPLR-SPARK & 0.681s & 10.517s & 99.156s & 924.020s & 3615.780s \\
 \hline
-subSpark   & 1.325s & 8.571s & 89.094s & 796.802s & 2918.470s \\
+PSUBPLR-SPARK & 1.325s & 8.571s & 89.094s & 796.802s & 2918.470s \\
 \hline
@@
 \hline
-Sublinear  & \XSolid & \Checkmark \\
+SLLR  & \XSolid & \Checkmark \\
 \hline
-PSublinear & \Checkmark & \Checkmark \\
+PSUBPLR-MR & \Checkmark & \Checkmark \\
 \hline
-Spark      & \Checkmark & \XSolid \\
+PGDPLR-SPARK & \Checkmark & \XSolid \\
 \hline
-subSpark   & \Checkmark &  \Checkmark \\
+PSUBPLR-SPARK & \Checkmark &  \Checkmark \\
 \hline
@@
 %\end{figure}
-
-2d-dataset (separation graph)
-\begin{figure}[tb] \label{fig:02}
-\center \includegraphics[height=5cm,width=7cm]{show-2d.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
 

### 2013-06-02 draft.tex
final version v0

@@
 In Section~\ref{sec:framework}, we present the parallel framework of all three different algorithms for PLR.
-Section~\ref{sec:experiment} describes the datasets and the baseline of our experiments and presents the experimental results.
+Section~\ref{sec:setup} describes the datasets and the baseline of our experiments and Section~\ref{sec:experiment} presents the experimental results.
 Finally, we offer our concluding remarks in Section~\ref{sec:concl}.
@@
 
-\section{Experiments} \label{sec:experiment}
-In this section, we conduct an empirical analysis of our algorithms.
+\section{Experiments Setup} \label{sec:setup}
+In this section, we explains details of the datasets information, cluster information, and the test programs of our experiments.
 
+\subsection{Datasets Information}
 We choose five open datasets to run all six test programs:	
@@
 We randomly repeat such split 20 times and our analysis is based on the average performance of 20 repetitions.
-
-%Particularly, we illustrate test errors in terms of accuracy and convergence in terms of MAP, both with respect to running time.
 
@@
 \hline
-    URL-Reputation & 3231961       & 2376130        & $3.608\times10^{-35}$ & 277058644           & 0.500 \\
+    URL-Reputation & 3231961       & 2376130        & $3.608\times10^{-5}$ & 277058644           & 0.500 \\
 \hline
@@
 \end{table}
+We carefully select these five datasets.
+The Simulated \textbf{2d} dataset can be viewed for visual result and serves for initial test of correctness of implementation.
+The \textbf{20NewsGroup} dataset is best-known for the test of PLR model, which has a balanced distribution between positive and negative data instances.
+The \textbf{Gisette} dataset is relatively larger, and data is less sparse. Thus it requires more computation theoretically.
+The \textbf{ECUESpam} dataset features for its inbalanced distribution between positive and negative data instances.
+It has a higher data dimensionality than textbf{Gisette} dataset.
+However, because of data sparsity, it has fewer nonzero values involved in the computation.
+Finally, the \textbf{URL-Reputation} dataset contains millions of data instances and features.
+The raw data is stored in the svmlight format, which has the size of more than 2GB.
+It achieves the current level for massive dataset, and exceed the scalability of Liblinear, which will be shown below.
 
+\subsection{Cluster Information}
 The cluster that we implement on has the following configurations shown in Table~\ref{tab:table2}.
@@
 \end{table}
+This kind of cluster configuration is now more and more common in research labs. Hence our results reported in the following can have a real impact in the research community.
 
-2d-dataset (separation graph)
+\subsection{Test Programs}
+There are all together 6 test programs for comparison.
+Online stochastic gradient descent method is run on Mahout in a sequential mode.
+Liblinear~\cite{fan2008liblinear} is the baseline test program we choose. It is sequential and it outperforms many other programs for PLR on a single machine.
+SLLR performs sequential sublinear algorithm on a single machine.
+PSUBPLR-MR performs parallel sublinear algorithm on Hadoop on cluster.
+PGDPLR-SPARK is the test program for parallel gradient descent run on Spark.
+PSUBPLR-SPARK implements parallel sublinear algorithm run on Spark.
+
+\section{Experimental Results} \label{sec:experiment}
+In this section, we conduct an empirical analysis of our algorithms.
+
+\subsection{Results on Simulated 2d Dataset}
 \begin{figure}[tb] \label{fig:02}
-\center \includegraphics[height=5cm,width=7cm]{img/show-2d.png}
-\caption{2d Dataset, Visual Result}
+\center \includegraphics[height=5cm,width=7cm]{img/2d-show.png}
+\caption{Visual Result on Simulated \textbf{2d} Dataset}
 \end{figure}
+Fig.~\ref{fig:02} shows the visual result for Simulated \textbf{2d} Dataset.
+Here we use all data for training and testing, thus "Test Error" here can be interpreted as "Training Error".
+The blue line represents the learned separation vector of Mahout.
+The black line indicates the result for Liblinear.
+The green line shows the result for all sublinear methods, including SLLR, PSUBPLR-MR and PSUBPLR-SPARK.
+The red line is the result for PGDPLR-SPARK.
+The results on the Simulated \textbf{2d} Dataset proves the correctness of all test programs.
 
-\begin{figure}[tb] \label{fig:03}
-\center \includegraphics[height=4.5cm,width=6cm]{img/2d_accuracy_iteration.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:04}
-\center \includegraphics[height=4.5cm,width=6cm]{img/20NewsGroup_accuracy_iteration.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:05}
-\center \includegraphics[height=4.5cm,width=6cm]{img/Gisette_accuracy_iteration.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:6}
-\center \includegraphics[height=4.5cm,width=6cm]{img/ECUESpam_accuracy_iteration.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:07}
-\center \includegraphics[height=4.5cm,width=6cm]{img/URL-Reputation_accuracy_iteration.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:08}
-\center \includegraphics[height=5cm,width=10cm]{img/all_time.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:09}
-\center \includegraphics[height=5cm,width=10cm]{img/2d_time.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:10}
-\center \includegraphics[height=5cm,width=10cm]{img/20NewsGroup_time.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:11}
-\center \includegraphics[height=5cm,width=10cm]{img/Gisette_time.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:12}
-\center \includegraphics[height=5cm,width=10cm]{img/ECUESpam_time.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:13}
-\center \includegraphics[height=5cm,width=10cm]{img/URL-Reputation_time.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:14}
-\center \includegraphics[height=5cm,width=10cm]{img/fault_tolerance.png}
-\caption{2d Dataset, Visual Result}
-\end{figure}
-
-\comment{1: add 5 line graphs;one dataset each;x:iteration number;y:accuracy;6 lines}
-
-\comment{2: add 1 bar graphs;x:different algorithms;y:time;one dataset as a group}
-
-%\comment{3: add 5 line graphs;one dataset each;x:iteration number;y:MAP;6 lines}
-
-\comment{4: add 5 bar graph;one dataset each;x:number of node used;y:time per iteration;each algorithm as a group}
-
-\comment{5: Fault tolerance-add 1 bar graph;x:number of maps failed;y:time of the iteration;each algorithm as a group}
-
-\comment{further parallelization in PSUBPLR-MR, Primal Map is the bottleneck}
-\comment{parameter passing issues in PSUBPLR-MR, the effect in small dataset}
-\comment{MR job start time}
-\comment{baseline liblinear}
-\comment{2d test method}
-\comment{not all converge at the iteration shown}
-\comment{symbol review}
-\comment{single reducer of spark}
-\comment{Iteration Number for SLLR explain}
-\comment{Liblinear Url result}
-\comment{fault tolerance: on url dataset,6 nodes}
-Analysis points:
-
-1: liblinear always performs the best; It fully utilizes memory; Single machine does not require communication; Disadvantage: cannot run large datasets, eg. ...(detailed statistics)
-
-2: Mahout precision not good; especially for those positive and negative instances are not balanced datasets perform poorly; sequential algorithm that can run large data in an acceptable time; Advantage: running memory is low, scalability is good
-
-3: Sublinear methods' accuracy is acceptable.; Parallel-sublinear has a small drop in precision.
-
-4: Hadoop's big drawback: Most current cluster programming models are based on acyclic data flow from stable storage to stable storage.
-Benefits of data flow: runtime can decide where to run tasks and can automatically recover from failures.
-But acyclic data flow is inefficient.
-eg.
-...
-(detailed statistics)
-
-5: Spark's in memory strategy; not to use hdfs file; system maybe even improved
-
-6: fast convergent
-
-7: In general, different algorithms for different datasets and system requirement. For general purpose, we recommend subSpark.
-
+\subsection{Results on Precision} \label{sec:precision}
 \begin{table}[h]
 \centering
-\caption{Accuracy Result}\label{tab:table3}
+\caption{Accuracy Results}\label{tab:table3}
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 \end{table}
+Accuracy of six test programs achieved on five datasets are shown in Table~\ref{tab:table3}. These are averaged results of cross validation.
+From Fig.~\ref{fig:03} to Fig.~\ref{fig:07}, we show the test error as a function of iteration number on each dataset for all six test programs.
+Note that, Liblinear can not be fully implemented the \textbf{URL-Reputation} dataset on our machine due to memory limit.
+This proves the scalability issue of Liblinear.
+However, if we take in just $\frac{1}{3}$ of the \textbf{URL-Reputation} dataset, it can return result in a very short time.
+Because of the data instances are distributed randomly, the returned result can also enjoy a very high accuracy.
 
+\begin{figure}[tb] \label{fig:03}
+\center \includegraphics[height=4.5cm,width=6cm]{img/2d_accuracy_iteration.png}
+\caption{Test error, as a function of iteration number on Simulated \textbf{2d} Dataset}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:04}
+\center \includegraphics[height=4.5cm,width=6cm]{img/20NewsGroup_accuracy_iteration.png}
+\caption{Test error, as a function of iteration number on \textbf{20NewsGroup} Dataset}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:05}
+\center \includegraphics[height=4.5cm,width=6cm]{img/Gisette_accuracy_iteration.png}
+\caption{Test error, as a function of iteration number on \textbf{Gisette} Dataset}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:06}
+\center \includegraphics[height=4.5cm,width=6cm]{img/ECUESpam_accuracy_iteration.png}
+\caption{Test error, as a function of iteration number on \textbf{ECUESpam} Dataset}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:07}
+\center \includegraphics[height=4.5cm,width=6cm]{img/URL-Reputation_accuracy_iteration.png}
+\caption{Test error, as a function of iteration number on \textbf{URL-Reputation} Dataset}
+\end{figure}
+
+\subsection{Results on Running Time} \label{sec:time}
 \begin{table}[h]
 \centering
-\caption{Running Time Result}\label{tab:table4}
+\caption{Running Time Results}\label{tab:table4}
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 \end{table}
+Running Time of six test programs used on five datasets are shown in Table~\ref{tab:table4}.
+These are averaged results corresponding to the accuracy we achieved in Table~\ref{tab:table3}.
 
+\begin{figure}[tb] \label{fig:08}
+\center \includegraphics[height=5cm,width=10cm]{img/all_time.png}
+\caption{All running times}
+\end{figure}
+In another way, we show the running time results in Fig.~\ref{fig:08} for comparison.
+
+From the accuracy results in section~\ref{sec:precision} and running time results in section~\ref{sec:time}.
+We can come up with following conclusions.
+\begin{enumerate}
+    \item Liblinear always performs the best. It fully utilizes memory and single machine implementation does not require any communication between machines, which causes overhead.
+          However, its scalability is limited by the memory size of the single machine that it runs on. This prevents its use in massive datasets.
+          Nevertheless, if the dataset can be fully loaded into a single machine's memory, this efficient and direct sequential way of implementation is still recommended. 
+    \item Mahout's precision is not good, especially for those datasets in which positive and negative instances are not balanced.
+          However, it is a representative of sequential algorithm that can train massive data in acceptable time.
+          When we monitor its memory when running, it is much lower than Liblinear. This is the advantage that the online algorithm brings.
+          Thus, it provides good scalability guarantee. If you are in the situation of single machine and limited memory, sequential online training like Mahout is recommended. 
+    \item The precision of all sublinear methods is acceptable. The developed parallel sublinear algorithm only has a small drop in precision.
+    \item Hadoop system has a great drawback for running PLR optimization methods. Its cluster programming model is based on acyclic data flow from stable storage to stable storage.
+          Though it has the benefits of deciding where to run tasks and can automatically recover from failures in runtime, acyclic data flow is inefficient for iterative algorithms.
+          All six test programs contains a number of iterations, thus making PSUBPLR-MR performs poorly, even worse than sequential algorithms.
+          When we study the details of Hadoop implementation, we find the MapReduce job starting time in PSUBPLR-MR is about 20s. It consists of task configuration time and parameter passing time.
+          This running time overhead is not negligible, especially when dataset is relatively small.
+          We also identify the running of "Primal-Map" dominates the whole iteration time (more than 66\%). It is the same situation for PSUBPLR-SPARK.
+    \item Spark employs the "all-in-memory" strategy, and it constructs RDD on demand. We implement PGDPLR-SPARK and PSUBPLR-SPARK in normal file system instead of HDFS.
+          Current results on Spark show that it is much more efficient than Hadoop, and performs better than Mahout.
+          In the parallel situation, and have massive data to process, we recommend using Spark, and can choose PSUBPLR-SPARK for less time in exchange for a little bit precision loss.
+          As the system is premature and still under developing process, we expect our running time results for PGDPLR-SPARK and PSUBPLR-SPARK can still be improved.
+          For example, Spark currently only supports for one reducer, thus it does not use full CPU power when doing reduce jobs.
+    \item Another interesting point we would like to raise is about dataset. If we compare \textbf{ECUESpam} dataset and \textbf{GISETTE} dataset.
+          The former has has higher data dimensionality but more sparse.
+          We can find that algorithms on \textbf{ECUESpam} dataset enjoy less running time per iteration as the dataset has fewer nonzero values involved in the computation.
+          However, algorithms on \textbf{ECUESpam} dataset need more iteration number, which is related to its higher data dimensionality. This even causes more running time in total.
+          To sum up, to get a general sense of running time for individual dataset, we have to consider both data volume and sparsity.
+\end{enumerate}
+
+\subsection{Results on Changing Cluster}
+From Fig.~\ref{fig:09} to Fig.~\ref{fig:13}, we show the running time as a function of used node number on each dataset for all three parallel test programs.
+\begin{figure}[tb] \label{fig:09}
+\center \includegraphics[height=5cm,width=10cm]{img/2d_time.png}
+\caption{Running time, as a function of used node number on Simulated \textbf{2d} Dataset}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:10}
+\center \includegraphics[height=5cm,width=10cm]{img/20NewsGroup_time.png}
+\caption{Running time, as a function of used node number on \textbf{20NewsGroup} Dataset}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:11}
+\center \includegraphics[height=5cm,width=10cm]{img/Gisette_time.png}
+\caption{Running time, as a function of used node number on \textbf{Gisette} Dataset}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:12}
+\center \includegraphics[height=5cm,width=10cm]{img/ECUESpam_time.png}
+\caption{Running time, as a function of used node number on \textbf{ECUESpam} Dataset}
+\end{figure}
+
+\begin{figure}[tb] \label{fig:13}
+\center \includegraphics[height=5cm,width=10cm]{img/URL-Reputation_time.png}
+\caption{Running time, as a function of used node number on \textbf{URL-Reputation} Dataset}
+\end{figure}
+
+As we can see from the results, fewer computation resources provided, longer the implementation process will take.
+However, this trend is not in a consistent fashion. When number of machines gets higher, the less impact it will make.
+We may reach a point for every algorithm when running time stops decreasing as machine number increases.
+This shows the true scalability of the designed algorithm, which we can study in our future work.
+
+\subsection{Fault Tolerance}
+There are both system level techniques and algorithm level techniques to provide fault tolerance in parallel computation.
+Results are shown in Table~\ref{tab:table5}.
 \begin{table}[h]
 \centering
-\caption{Fault Tolerance}\label{tab:table5}
+\caption{Fault Tolerance Analysis}\label{tab:table5}
 \begin{tabular}{|c|c|c|}
@@
 \hline
-Mahout     & \Checkmark & \XSolid  \\
+Mahout     & \XSolid & \XSolid  \\
 \hline
@@
 \end{table}
+Here, randomization is employed in all sublinear methods, thus provides algorithm level fault tolerance for SLLR, PSUBPLR-MR and PSUBPLR-SPARK.
+Hadoop and Spark can both provide fault tolerance, but in different ways. Hadoop employs HDFS while Spark has RDDs.
+Of all six test programs, PSUBPLR-MR and PSUBPLR-SPARK are fault tolerant in both system level and algorithm level.
 
-\comment{Will add explanation for table 5 later in next version of draft}
-
-%Current URL-reputation Dataset Status
-%\begin{figure}[tb] \label{fig:01}
-%\center \includegraphics[height=5cm,width=10cm]{show1.png}
-%\caption{URL-reputation Dataset, Performance Result}
-%\end{figure}
+We show the iteration time as a function of percentage of failed maps on \textbf{URL-Reputation} dataset for all three parallel test programs in Fig.~\ref{fig:14}.
+This is tested on 6 nodes.
+\begin{figure}[tb] \label{fig:14}
+\center \includegraphics[height=5cm,width=10cm]{img/fault_tolerance.png}
+\caption{Iteration time, as a function of percentage of failed maps, on \textbf{URL-Reputation} Dataset, run on 6 nodes}
+\end{figure}
+As the outcome shows, PSUBPLR-MR suffers no running time increase per iteration when maps failed. But it takes the cost of precision loss if we enforce no additional iterations are implemented.
+PGDPLR-SPARK and PSUBPLR-SPARK will increase iteration time right after the maps failed. It is due to RDD reconstruction. The increase is not significant.
+This difference also proves the different mechanism of fault tolerance between Hadoop and Spark.
 
@@
 We also present a novel parallel sublinear method and make a comparison between these algorithms implemented on different systems.
-As the outcome shows, we claim parallel sublinear method implemented on Spark is the most computational efficient way to solve PLR for general purpose.
+As the outcome shows, we claim parallel sublinear method implemented on Spark is the most computational efficient way to solve PLR in parallel for massive datasets.
 Moreover, fault tolerance can be provided for those lengthy distributed computations both on algorithm level and system level.
 We discussed the balance between dataset size, choosing parallel system, and choosing parallel algorithm through concrete experimental results.
-Also, fault tolerance can be provided for those lengthy distributed computations both on algorithm level and system level.
-As the outcome shows, we recommend parallel sublinear method implemented on Spark is the most computational efficient way to solve PLR for general purpose.
 

### 2013-06-02 plot_script/src/draw_accuracy_iteration.m

@@ -1,0 +1,32 @@
+clc, clear
+%dataset = '2d';
+%dataset = '20NewsGroup';
+%dataset = 'Gisette';
+%dataset = 'ECUESpam';
+dataset = 'URL-Reputation';
+mat = [dataset,'_accuracy_iteration.mat'];
+load(mat);
+%if STRCMP(dataset,'URL-Reputation')
+    x=[10 20 30 40 50];
+%end
+figure; 
+set(gcf,'Position',[100,100,1000,750], 'color','w');
+LineWidth=3;
+MarkerSize=8;
+plot(x,a,'-ok','LineWidth',LineWidth,'MarkerSize',MarkerSize);
+hold on;
+plot(x,b,'--xb','LineWidth',LineWidth,'MarkerSize',MarkerSize);
+hold on;
+plot(x,c,'-vr','LineWidth',LineWidth,'MarkerSize',MarkerSize);
+hold on;
+plot(x,d,'-.^g','LineWidth',LineWidth,'MarkerSize',MarkerSize);
+hold on;
+plot(x,e,'-*y','LineWidth',LineWidth,'MarkerSize',MarkerSize);
+hold on;
+plot(x,f,'-+c','LineWidth',LineWidth,'MarkerSize',MarkerSize);
+hold on;
+xlabel('Iteration Number','Fontsize',25,'fontweight','b');
+ylabel('Test Error','Fontsize',25,'fontweight','b');
+set(gca,'fontsize',25,'fontweight','b');
+%axis([10 50 0 0.3]);
+legend('Mahout','Liblinear','SLLR','PSUBPLR-MR','PGDPLR-SPARK','PSUBPLR-SPARK');

### 2013-06-02 plot_script/src/draw_fault_tolerance.m

@@ -1,0 +1,13 @@
+clc, clear
+mat = 'fault_tolerance.mat';
+load(mat);
+figure; 
+set(gcf,'Position',[10,10,2000,1000], 'color','w');
+y=y*4;
+b=bar(y);
+grid on;
+set(gca,'XTickLabel',{'PSUBPLR-MR','PGDPLR-SPARK','PSUBPLR-SPARK'})
+xlabel('Number of Failed Maps','Fontsize',25,'fontweight','b');
+ylabel('Iteration Time(after failures)/s','Fontsize',25,'fontweight','b');
+set(gca,'fontsize',25,'fontweight','b');
+legend('1%','5%','10%','15%','30%');

### 2013-06-02 plot_script/src/draw_time.m

@@ -1,0 +1,14 @@
+clc, clear
+dataset = 'all';
+mat = [dataset,'_time.mat'];
+load(mat);
+figure; 
+set(gcf,'Position',[10,10,2000,1000], 'color','w');
+b=bar(y);
+grid on;
+ch = get(b,'children');
+set(gca,'XTickLabel',{'2d','20NewsGroup','Gisette','ECUESpam','URL-Reputation'})
+xlabel('Algorithms','Fontsize',25,'fontweight','b');
+ylabel('Running Time/s','Fontsize',25,'fontweight','b');
+set(gca,'fontsize',25,'fontweight','b');
+legend('Mahout','Liblinear','SLLR','PSUBPLR-MR','PGDPLR-SPARK','PSUBPLR-SPARK');

### 2013-06-02 plot_script/src/draw_time_variation.m

@@ -1,0 +1,19 @@
+clc, clear
+%dataset = '2d';
+%dataset = '20NewsGroup';
+%dataset = 'Gisette';
+%dataset = 'ECUESpam';
+dataset = 'URL-Reputation';
+mat = [dataset,'_time.mat'];
+load(mat);
+figure; 
+set(gcf,'Position',[10,10,1800,900], 'color','w');
+x=y(4:6,:);
+x=x*4;
+b=bar(x);
+grid on;
+set(gca,'XTickLabel',{'PSUBPLR-MR','PGDPLR-SPARK','PSUBPLR-SPARK'})
+xlabel('Number of Nodes Used','Fontsize',25,'fontweight','b');
+ylabel('Running Time per Iteration/s','Fontsize',25,'fontweight','b');
+set(gca,'fontsize',18,'fontweight','b');
+legend('1 node','2 nodes','3 nodes','4 nodes','5 nodes','6 nodes');

### 2013-06-02 plot_script/src/save_data.m

@@ -1,0 +1,19 @@
+clc, clear
+%x = [30	60	90	120	150];
+%a =	1-[0.835	0.878	0.897	0.911	0.915];
+%b =    1-[0.926	0.951	0.958	0.962	0.962];
+%c =	1-[0.872	0.915	0.930	0.939	0.942];
+%d =	1-[0.876	0.911	0.925	0.933	0.938];
+%e =	1-[0.920	0.940	0.952	0.958	0.960];
+%f =	1-[0.876	0.911	0.926	0.936	0.940];
+% y=[45934.57741	26121.23017	20200.418	15150.3135	12120.25	10100.209;
+% 2376.293664	1342.538793	1038.23	778.6725	622.94	519.115;
+% 14570.1652	8401.223276	6496.946	4872.7095	3898.17	3248.473;
+% 73391.17293	41633.43103	32196.52	24147.39	19317.91	16098.26;
+% 16251.54466	9351.155172	7231.56	5423.67	4338.94	3615.78;
+% 13059.54802	7547.767241	5836.94	4377.705	3502.16	2918.47];
+% y=y/150;
+y=[108	108	108	108	108;
+24.5	25	26	28	30;
+19.5	21	23	24	25];
+save fault_tolerance.mat;

### 2013-06-04 draft.tex
add a few comments

@@
 %We have released all experiment codes to open source at https://github.com/penghaoruo/PPLR.
+\comment{change description of Mahout}
 \end{abstract}
@@
 We will focus on the binary PLR model in the following.
-A wide variety of other classification algorithms exist in the literature.
+A wide variety of other classification algorithms exist in the literature. \commnet{change}
 One might ask why we are motivated to use PLR for classification instead of other usual candidates.
@@
 When developing parallel algorithms for PLR, it is unavoidable to come across the question of choosing which parallel system to use and which parallel framework to employ.
-After a thorough survey, we choose three unique and best-known systems to test: Hadoop~\cite{white2012hadoop}, Mahout~\cite{mahoutscalable} and Spark~\cite{zaharia2010spark}.
+After a thorough survey, we choose three unique and best-known systems to test: Hadoop~\cite{white2012hadoop}, Mahout~\cite{mahoutscalable} and Spark~\cite{zaharia2010spark}. \comment{change}
 Hadoop employs HDFS~\cite{borthakur2008hdfs} and MapReduce~\cite{dean2008mapreduce}.

### 2013-06-12 draft.tex
backup

@@
 % edited by Haoruo Peng
-% Date: 2013.5.27
+% Date: 2013.6.12
 \documentclass{llncs}
@@
 % first the title is needed
-\title{Massively Parallel Learning for Penalized Logistic Regression Model}
+\title{Learning for Penalized Logistic Regression Model in Parallel}
 
 % a short form should be given in case it is too long for the running head
-\titlerunning{Massively Parallel Learning for Penalized Logistic Regression Model}
+\titlerunning{Learning for Penalized Logistic Regression Model in Parallel}
 
@@
 \begin{abstract}
-Penalized logistic regression (PLR) is a widely used supervised learning model.
-This paper addresses the issue of computational efficiency for solving PLR in big data scenario.
-We focus on algorithm level and employ three different parallel computation systems with three different types of parallel algorithms to efficiently improve scalability.
+Logistic regression (LR) model has a variety of applications in the field of machine learning.
+It is a supervised learning model, and can be extended to models with regularization, which enjoy the benefits of solid statistical base. 
+This paper addresses the issue of computational efficiency for solving LR in big data scenario.
+We focus both on algorithm level and system level. employ three different parallel computation systems with three different types of parallel algorithms to efficiently improve scalability.
 Hadoop, Mahout and Spark are three existing well-known parallel systems that can be implemented with large scale machine learning algorithms.

### 2013-06-13 draft.tex
bab
IEEE version

@@
 % edited by Haoruo Peng
-% Date: 2013.6.12
-\documentclass{llncs}
-\usepackage{llncsdoc}
+% Date: 2013.6.14
+\documentclass[10pt, conference, compsocconf]{IEEEtran}
 \usepackage{amsmath, amssymb}
@@
 \usepackage{bbding}
+\usepackage{epstopdf}
 
@@
 \begin{document}
-\mainmatter  % start of an individual contribution
+%\mainmatter  % start of an individual contribution
 
@@
 % a short form should be given in case it is too long for the running head
-\titlerunning{Learning for Penalized Logistic Regression Model in Parallel}
+%\titlerunning{Learning for Penalized Logistic Regression Model in Parallel}
 
+\author{\IEEEauthorblockN{Authors Name/s per 1st Affiliation (Author)}
+\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
+line 2: name of organization, acronyms acceptable\\
+line 3: City, Country\\
+line 4: Email: name@xyz.com}
+\and
+\IEEEauthorblockN{Authors Name/s per 2nd Affiliation (Author)}
+\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
+line 2: name of organization, acronyms acceptable\\
+line 3: City, Country\\
+line 4: Email: name@xyz.com}
+}
 %
@@
 This paper addresses the issue of computational efficiency for solving LR in big data scenario.
-We focus both on algorithm level and system level. employ three different parallel computation systems with three different types of parallel algorithms to efficiently improve scalability.
-Hadoop, Mahout and Spark are three existing well-known parallel systems that can be implemented with large scale machine learning algorithms.
-Parallel gradient Descent and stochastic gradient descent are two existing state-of-art algorithms for parameter optimization in PLR.
+We focus on both algorithm level and computation platform level of task parallelism.
+We study three different parallel computation platforms along with three different types of parallel algorithms to efficiently improve scalability.
+Hadoop, Mahout and Spark are three existing well-known parallel computing platforms that can be implemented with large scale machine learning algorithms.
+Parallel gradient Descent and stochastic gradient descent are two state-of-art algorithms for parameter optimization in LR.
 We also present a novel parallel sublinear method based on its sequential version.
-We then make a comparison between these algorithms implemented on different systems.
-As the outcome shows, we claim parallel sublinear method implemented on Spark is the most computational efficient way to solve PLR for general purpose.
-Moreover, fault tolerance can be provided for those lengthy distributed computations both on algorithm level and system level.
-%We have released all experiment codes to open source at https://github.com/penghaoruo/PPLR.
-\comment{change description of Mahout}
+We then make a comparison between these algorithms implemented in different platforms.
+As the outcome shows, we can choose different algorithms in different situations in terms of datasets and machine resources for tradeoff between efficiency and precision.
+To enhance practicality, we provide fault tolerance for those  parallel distributed computations.
 \end{abstract}
 
+\begin{IEEEkeywords}
+Logistic Regression Model; Parallel Computing; Sublinear Method; Big Data;
+\end{IEEEkeywords}
+
 \section{Introduction} \label{sec:int}
-The penalized logistic regression (PLR) model~\cite{HastieBook:SL} plays an important role in machine learning and data mining.
+Logistic regression model~\cite{HastieBook:SL} plays a vital role in machine learning and data mining.
+It is a widely used model in algorithms like PageRank~\cite{page1999pagerank} and Anti-spam Filtering~\cite{androutsopoulos2000evaluation}.
 The model serves for classification problems, and enjoys a substantial body of supporting theories and algorithms.
-PLR is competitive with the support vector machines (SVMs) \cite{Vapnik:1998}, because it has both high accuracy and interpretability (PLR can directly estimate a conditional class probability).
-Thus, a binary classification problem modeled by PLR can be easily extended to a multi-classification problem.
-We will focus on the binary PLR model in the following.
-A wide variety of other classification algorithms exist in the literature. \commnet{change}
-One might ask why we are motivated to use PLR for classification instead of other usual candidates.
-Our motivation for exploring PLR as a fast classifier to be used in data mining applications is its maturity.
-It has a statistical foundation which could be used to extend classification results into a deeper analysis.
+Thus, a binary classification problem modeled by LR can be easily extended to a multi-classification problem.
+Also, due to the strong statistical foundation of LR model, we can extend results into a deeper analysis which may apply to other classification models.
+We will focus on the binary LR model in the rest of the paper.
 
-Recently, large-scale applications have emerged from many modern massive datasets.
-A key characteristic of these applications is that the size of their training data is very large and data dimensionality is very high.
-For example, in medical diagnostic applications~\cite{tsumoto2004mining}, both doctors and patients would like to take the advantage of millions of records over hundreds of attributes.
-More evidently, search engines on texts or multimedia data must handle data volume in the billion scale and each data instance is characterized by a feature space of thousands of dimensions~\cite{genkin2007large}.
-Large data volume and high data dimensionality pose computational challenges to machine learning problems.
-Especially, PLR is a widely used model in algorithms like PageRank~\cite{page1999pagerank} and Anti-spam Filtering~\cite{androutsopoulos2000evaluation}.
+In recent years, many modern massive datasets are getting larger and larger.
+A most identifiable characteristic of these datasets is that the size of their training data is very large and data dimensionality is very high.
+Large data volume and high data dimensionality bring unavoidable computational challenges to machine learning problems.
+For example, in social networks, we have datasets~\cite{lewis2008tastes} covering multiple dimensions like friendship relationship, share of common interests.
+They generally include of millions of records over millions of attributes.
+More evidently, for the task of text categorization, we usually have to face a dataset with data volume in the billion scale and each data instance is characterized by thousands of feature dimensions~\cite{lewis2004rcv1}.
+We tackle these challenges on both algorithm level and computing platform level via parallelization methods.
+For many applications, in order to have speedup in performance, we can employ not only task parallelism, but also data parallelism~\cite{subhlok1993exploiting}.
+In this paper, we mainly discuss issues in task parallelism.
 
-We tackle these challenges on algorithm level and fully exploit the benefits of parallelization.
-When developing parallel algorithms for PLR, it is unavoidable to come across the question of choosing which parallel system to use and which parallel framework to employ.
-After a thorough survey, we choose three unique and best-known systems to test: Hadoop~\cite{white2012hadoop}, Mahout~\cite{mahoutscalable} and Spark~\cite{zaharia2010spark}. \comment{change}
+When developing parallel algorithms for LR, it is unavoidable to come across the question of choosing which parallel computing platform to employ.
+After a thorough survey, we choose three unique and best-known computing platforms to test: Hadoop~\cite{white2012hadoop}, Mahout~\cite{mahoutscalable} and Spark~\cite{zaharia2010spark}.
 Hadoop employs HDFS~\cite{borthakur2008hdfs} and MapReduce~\cite{dean2008mapreduce}.
-Mahout runs on Apache Hadoop~\cite{gropp1999using} and make improvements in the low level code.
+Mahout runs on Apache Hadoop and makes improvements in the low level code.
 Spark features for iterative algorithms and also supports HDFS.
-We will introduce the features of them separately in detail in related work section.
+We will compare design features of them separately in related work section.
 
-In sequential algorithms for PLR, a classical way is to turn to stochastic approximation methods.
-Stochastic approximation methods, such as stochastic gradient descent~\cite{zhang2004solving} and stochastic dual averaging~\cite{xiao2010dual}, obtain optimal generalization guarantees with only a single pass or a small number of passes over the data.
-Therefore, they can achieve a desired generalization with runtime linear to the dataset size.
-A best-known method of those is stochastic gradient descent.
-This works in an online fashion.
-We view the sampled data points as the come-in data stream.
-It is extremely hard to parallelize, but it is blazingly fast.
-If we take a step back and go back to the general gradient descent to solve PLR, we can find that it can be actually embarrassingly parallel.
+In sequential parameter optimization algorithms for LR model, a classical way is to turn to stochastic approximation methods.
+Stochastic approximation methods, such as stochastic gradient descent~\cite{zhang2004solving} and stochastic dual averaging~\cite{xiao2010dual}, obtain optimal generalization guarantees with a small number of passes over the data with runtime linear to the dataset size.
+The stochastic gradient descent method can work in an online fashion, as we view the sampled data points as the come-in data stream.
+It is hard to be changed to task-parallelism, but it is blazingly fast.
+If we take a step back and go back to the general gradient descent to solve LR model, we can find that it can be actually embarrassingly parallel.
 We can take in all the data at the same iteration and just compute the gradient in a MapReduce fashion.
-We can further speed up the runtime by employing sublinear algorithms~\cite{peng2012sublinear} for PLR via the use of stochastic approximation idea.
+We can further speed up the runtime by employing sublinear algorithms~\cite{peng2012sublinear} via the use of stochastic approximation idea.
 This methods access a single feature of training vectors instead of entire training vectors at each iteration.
@@
 The rest of the paper is organized as follows:
-Section~\ref{sec:rew} discusses some related work and three different systems.
-In Section~\ref{sec:plr}, we review the penalized logistic regression model and the sublinear method.
-In Section~\ref{sec:framework}, we present the parallel framework of all three different algorithms for PLR.
+Section~\ref{sec:rew} discusses some related work.
+In Section~\ref{sec:plr}, we review the logistic regression model and the sequential sublinear algorithm.
+In Section~\ref{sec:framework}, we present the parallel framework of all three different algorithms for LR model.
 Section~\ref{sec:setup} describes the datasets and the baseline of our experiments and Section~\ref{sec:experiment} presents the experimental results.
@@
 \section{Related Work} \label{sec:rew}
+
+\subsection{Scalability Improvement in Big Data Research}
 In big data scenario, large datasets require us to develop machine learning algorithms towards a more efficient and more parallelized end.
 Researchers have already done much work to cater for the needs of massive datasets.
-Early work like PSVM \textit{(Parallel Support Vector Machines)}~\cite{chang2011psvm} employed an approximation matrix decomposition method based on row selections to reduce the memory when running the algorithm.
+Early work like PSVM (\textit{Parallel Support Vector Machines})~\cite{chang2011psvm} employed an approximation matrix decomposition method based on row selections to reduce the memory when running the algorithm.
 It can then increase the number of participated parallel computation nodes to several hundreds.
-Later, the work of PLDA \textit{(Parallel Latent Dirichlet Allocation)}~\cite{wang2009plda} further improve the computational efficiency of the LDA model through the use of sampling methods.
+Later, the work of PLDA (\textit{Parallel Latent Dirichlet Allocation})~\cite{wang2009plda} further improve the computational efficiency of the LDA model through the use of sampling methods.
 The proposed parallel algorithm in Hadoop is robust, for it has fault tolerance of machine failures, taking the advantage of Hadoop.
@@
 It pushed the limits of parallel computational nodes to a hundred-million level, and in the meantime, achieved a best learning performance ever.
-Besides Hadoop, there are many other trials on parallelization in machine learning.
-GraphLab~\cite{kyrola2012graphchi}, a recent developed tool in CMU\textit{(Carnegie Mellon University)} for large-scale machine learning, tried to tackle with efficiency and scalability problems of machine leaning algorithms when applied to graphs.
+GraphLab~\cite{kyrola2012graphchi}, a recent developed tool for large-scale machine learning. It tackles with efficiency and scalability problems of machine leaning algorithms when applied to graphs.
 
+\subsection{Three Computing Platforms}
 Three computing platforms we are working on each features for its own advantage in implementing machine learning algorithms.
-The Apache Hadoop~\cite{white2012hadoop} software library is a framework that allows for the distributed processing of large data sets across clusters of computers using simple programming models.
-It is an open-source software framework that supports data-intensive distributed applications, licensed under the Apache v2 license.
-It supports the running of applications on large clusters of commodity hardware.
-Hadoop was derived from Google's MapReduce and Google File System (GFS) papers.
-Hadoop is written in the Java programming language and is an Apache top-level project being built and used by a global community of contributors.
-The entire Apache Hadoop platform is now commonly considered to consist of the Hadoop kernel, MapReduce and Hadoop Distributed File System (HDFS), as well as a number of related projects, including Apache Hive and Apache HBase.
-Hadoop is designed to scale up from single servers to thousands of machines, each offering local computation and storage.
-The Hadoop framework transparently provides both reliability and data motion to applications.
-Hadoop implements a computational paradigm named MapReduce~\cite{dean2008mapreduce}, where the application is divided into many small fragments of work, each of which may be executed or re-executed on any node in the cluster.
-The MapReduce paradigm applies to problems where the input is a set of key-value pairs.
-A \textit{map} function turns these key-value pairs into other intermediate key-value pairs. A \textit{reduce} function merges in some way all values for each intermediate key to produce output.
-Actually, many problems can be framed as MapReduce problems, or as a series of them.
-The paradigm also lends itself quite well to parallelization: all of the processing is independent and so can be split across many machines.
-In addition, it provides a distributed file system that stores data on the compute nodes, providing very high aggregate bandwidth across the cluster.
-Both map/reduce and the distributed file system are designed so that node failures are automatically handled by the framework.
-Rather than rely on hardware to deliver high-availability, the library itself is designed to detect and handle failures at the application layer, so delivering a highly-available service on top of a cluster of computers, each of which may be prone to failures.
+The Apache Hadoop~\cite{white2012hadoop} software library allows for distributed processing of large datasets across clusters of computers using simple programming models.
+Hadoop utilizes MapReduce~\cite{dean2008mapreduce} as its computational paradigm.
+MapReduce paradigm takes a set of key-value pairs as its input.
+Then a user-defined \textit{map} function turns input key-value pairs into some intermediate key-value pairs.
+A user-defined \textit{reduce} function merges values for the same intermediate key to produce output.
+All of the processing is independent and it makes MapReduce paradigm easy to be parallelized.
+In addition, Hadoop provides a distributed file system (HDFS).
+Both MapReduce and HDFS are designed to handle node failures in an automatical way, making Hadoop support large clusters built on commodity hardware.
+The goal of Apache Mahout~\cite{mahoutscalable} is to build scalable machine learning libraries.
+Their core algorithms for clustering, classification and batch based collaborative filtering are implemented on top of Apache Hadoop using the MapReduce paradigm.
+The core libraries are so highly optimized that it also has good performance for non-distributed algorithms.
+Spark~\cite{zaharia2010spark} is a cluster computing system that aims to make data analytics fast.
+Spark provides support in-memory cluster computing. A job can load data into memory and query it repeatedly by creating and caching resilient distributed datasets (\textit{RDDs}).
+Moreover, RDDs achieve fault tolerance through lineage: RDDs always have enough information about how they were derived from other RDDs, and they are easy to be rebuilt if a certain partition is lost.
+Spark can run up to 100 times faster than Hadoop MapReduce for iterative algorithms.
 
-The Apache Mahout~\cite{mahoutscalable} machine learning library's goal is to build scalable machine learning libraries.
-It is scalable to reasonably large datasets.
-Their core algorithms for clustering, classification and batch based collaborative filtering are implemented on top of Apache Hadoop using the map/reduce paradigm.
-The core libraries are highly optimized to allow for good performance also for non-distributed algorithms.
-It is also scalable to support business cases. Mahout is distributed under a commercially friendly Apache Software license.
-Currently Mahout supports mainly four use cases: Recommendation mining takes users' behavior and from that tries to find items users might like.
-Clustering takes e.g.
-text documents and groups them into groups of topically related documents.
-Classification learns from existing categorized documents what documents of a specific category look like and is able to assign unlabeled documents to the correct category.
-Frequent itemset mining takes a set of item groups (terms in a query session, shopping cart content) and identifies, which individual items usually appear together.
-Mahout currently supports many machine learning algorithms including collaborative filtering, user and item based recommenders, K-Means, fuzzy K-Means clustering, mean shift clustering, dirichlet process clustering, Latent Dirichlet Allocation, singular value decomposition, parallel frequent pattern mining, complementary naive bayes classifier and random forest decision tree based classifier.
+In Table~\ref{tab:systemcmp}, we compare between Hadoop and Spark computing platforms.
+As Mahout is mainly built on Hadoop, it inherits most of Hadoop features.
+To better illustrate, we use short abbreviations in the table.
+Spark supports two types of operations on RDDs: Actions and Transformations (As and Ts).
+Actions include functions like \textbf{count}, \textbf{collect} and \textbf{save}. They usually return a result from input RDDs.
+Transformations include functions like \textbf{map}, \textbf{filter} and \textbf{join}. They normally build new RDDs from other RDDs, which are under the lineage rule.
+In the table, we use "NFS" to represent "Normal File System" and "Fault Tolerance" here is specifically for node failure situations.
+\begin{table}[h]
+\centering
+\caption{Platform Comparison: Hadoop VS Spark}\label{tab:systemcmp}
+\begin{tabular}{|c|c|c|}
+\hline
+           & Hadoop & Spark \\
+\hline
+Computational Paradigm  & MapReduce & As and Ts \\
+\hline
+File System Supported & HDFS & HDFS and NFS \\
+\hline
+Design Concept  & Key-value Pairs & RDD \\
+\hline
+Fault Tolerance Technique & Redundancy & Lineage \\
+\hline
+\end{tabular}
+\end{table}
 
-Spark~\cite{zaharia2010spark} is developed in the UC Berkeley AMPLab. It is an open source cluster computing system that aims to make data analytics fast: both fast to run and fast to write.
-To run programs faster, Spark provides primitives for in-memory cluster computing: a job can load data into memory and query it repeatedly much more quickly than with disk-based systems like Hadoop MapReduce.
-To make programming faster, Spark provides clean, concise APIs in Scala, Java and Python. Users can also use Spark interactively from the Scala and Python shells to rapidly query big datasets.
-Spark was initially developed for two applications where keeping data in memory helps: iterative algorithms, which are common in machine learning, and interactive data mining.
-In both cases, Spark can run up to 100x faster than Hadoop MapReduce.
-Spark is also the engine behind Shark, a fully Apache Hive-compatible data warehousing system that can run 100x faster than Hive.
-While Spark is a new engine, it can access any data source supported by Hadoop, making it easy to run over existing data.
-Spark is built on top of Mesos, a cluster operating system that lets multiple parallel applications share a cluster in a fine-grained manner and provides an API for applications to launch tasks on a cluster.
-This allows Spark to run alongside existing cluster computing frameworks, such as Mesos ports of Hadoop and MPI, and share data with them.
-In addition, building on Mesos greatly reduced the programming effort that had to go into Spark.
-The main abstraction in Spark is that of a resilient distributed dataset\textit{(RDD)}, which represents a read-only collection of objects partitioned across a set of machines that can be rebuilt if a partition is lost.
-Users can explicitly cache an RDD in memory across machines and reuse it in multiple MapReduce-like parallel operations.
-RDDs achieve fault tolerance through a notion of lineage: if a partition of an RDD is lost, the RDD has enough information about how it was derived from other RDDs to be able to rebuild just that partition.
+\subsection{Previous Research on Sublinear Method}
+Sublinear method is recently developed by many contributing researchers.
+Clarkson et al.~\cite{clarkson2010sublinear} first proposed the method of approximation algorithms in sublinear time.
+It is applied to optimization problems for linear classifiers and minimum enclosing balls.
+The algorithm employs a novel sampling technique along with a new multiplicative update procedure.
+Hazan et al.~\cite{hazanbeating} exploited the approach to linear SVM (\textit{Support Vector Machine}).
+Cotter et al.~\cite{cotter2012kernelized} continued to extend the method to kernelized SVM.
+In~\cite{hazan2011optimal}, Hazan et al. applied the sublinear approximation approach for solving linear regression with penalties.
+Garber and Hazan~\cite{garberapproximating} also developed it in SDP (\textit{Semidenfinite Programming}).
+Peng et al.~\cite{peng2012sublinear} utilized the method in LR model with penalties and developed sequential sublinear algorithms for both $\ell_1$-penalty and $\ell_2$-penalty separately.
 
-Recently, Clarkson et al.~\cite{clarkson2010sublinear} proposed a new method by taking advantage of randomized algorithms.
-They presented sublinear-time approximation algorithms for optimization problems arising in machine learning, such as linear classifiers and minimum enclosing balls.
-The algorithm uses a combination of a novel sampling techniques and a new multiplicative update algorithm.
-They also proved lower bounds which show the running times to be nearly optimal on the unit-cost RAM model.
-Hazan et al.~\cite{hazanbeating} exploited sublinear approximation approach to the linear SVM with $\ell_2$-penalty, from which we were inspired and borrowed some of the ideas.
-Later on, Cotter et al.~\cite{cotter2012kernelized} extended the work to kernelized SVM cases.
-In~\cite{hazan2011optimal}, Hazan et al.
-applied the sublinear approximation approach for solving ridge ($\ell_2$-regularized) and lasso ($\ell_1$-regularized) linear regression.
-Garber and Hazan~\cite{garberapproximating} developed the method in semidenfinite programming (SDP).
-Peng et al.~\cite{peng2012sublinear} applied the method in PLR and developed sequential sublinear algorithms for both $\ell_1$-penalty and $\ell_2$-penalty.
-% can change the style to have {items} to be more organized
+\section{Logistic Regression Model and Sequential Sublinear Algorithm} \label{sec:plr}
 
-\section{Penalized Logistic Regression Models and Sublinear Methods} \label{sec:plr}
-Logistic regression is a widely used method for solving classification problems.
+\subsection{Logistic Regression Model}
 In this paper, we are mainly concerned with the binary classification problem.  	
-Suppose that we are given a set of training data $\XM=\{(\x_i, y_i): i=1, \ldots, n\}$ where $\x_i \in \RB^d$ are input samples and $y_i \in \{-1, 1\}$ are the corresponding labels.
-For simplicity, we let $\X=[{\x}_{1}, {\x}_{2}, \ldots, {\x}_n]^{T}$ and $\y=(y_1, y_2, \ldots, y_n)^T$.
-In the logistic regression model, the expected value of $y_i$ is given by
+We define training dataset as $\XM=\{(\x_i, y_i): i=1, \ldots, n\}$, where $\x_i \in \RB^d$ are input samples and $y_i \in \{-1, 1\}$ are the corresponding labels.
+For simplicity, we will use the notation $\X=[{\x}_{1}, {\x}_{2}, \ldots, {\x}_n]^{T}$ and $\y=(y_1, y_2, \ldots, y_n)^T$ to represent training dataset in the following.
+Then to fit in the logistic regression model, the expected value of $y_i$ is given by
 \[
@@
 
-\subsection{Penalized Logistic Regression Models}
-We assume that $\w$ follows a Gaussian distribution with mean $\0$ and covariance matrix $\lambda \I_d$ where $\I_d$ is the $d{\times}d$ identity matrix, i.e. $\w \thicksim N(\0, \lambda \I_d)$.
-In this case, we can formulate the optimization problem as
-\begin{equation} \label{eqn:4}
+The learning process aims to optimize $\w$ and $b$.
+To make the optimization problem more practical to solve, a common practice is to add penalties to LR model.
+Typically, for $\ell_2$-penalty, we have to solve the following optimization problem:
+\begin{equation} \label{eqn:1}
 	\max_{\bw ,b} \; \Big\{F(\w, b| \XM) - \frac{\lambda}{2}  \|\bw\|_2^{2} \Big\}.
 \end{equation}
-(\ref{eqn:4}) shows us that the problem reduces to an optimization problem with an $\ell_2$-penalty.
-
-In another case, we impose a Laplace prior for $\w$, whose density is given by
-\[	
-\log\,p\lc\bw \rc=d\,\log\frac{\gamma}{2}-\gamma{\|\bw\|}_{1}.
-\]
-With this prior, we get an optimization problem with the $\ell_1$-penalty.
-\begin{equation} \label{eqn:5}
+For $\ell_1$-penalty, we are faced with the following optimization problem:
+\begin{equation} \label{eqn:2}
 	\max_{\bw ,b} \;  \big\{F(\w, b|\XM)- \gamma{\|\bw \|}_{1}\big\}.	
 \end{equation}
+Here, we have
+\[
+F(\w, b| \XM) = \sum_{i=1}^n \log g_i(y_i)
+\]
+in both (\ref{eqn:1}) and (\ref{eqn:2}).
+To be brief, we omit the derivation here.
 
-The advantage of $\ell_1$-penalty over $\ell_2$-penalty is its utility in sparsity modeling \cite{tibshirani1996regression}.
-Thus, $\ell_1$-penalty logistic regression can serve for both classification and feature selection simultaneously.
-
-\subsection{Sublinear Algorithms}
-The framework of sublinear algorithms is a hybrid method to handle hard margin and soft margin separately and simultaneously.
-It enjoys the property of fast convergence for both hard margin and soft margin.
-
-Each iteration of the method works in two steps.
-The first one is the \textit{stochastic primal update}:
-\begin{enumerate}
-\item[{(1)}] \; An instance $i\in \{1,\ldots, n\}$ is chosen according to a probability vector $\bp$;
-\item[{(2)}] \; The primal variable $\bw$ is updated according to the gradient computed based on the sampled instance $\textbf{x}_i$, via an online update with regret.
-\end{enumerate}
-
-The second one is the \textit{stochastic dual update}:
-\begin{enumerate}
-\item[{(1)}] \; A stochastic estimate of hard margin plus soft margin is obtained, which can be computed in $O(1)$ time per term;
-\item[{(2)}] \; The probability vector $\bp$ is updated based on the above computed terms by using the \textit{Multiplicative Updates} (MW) framework~\cite{arora2005multiplicative} for online optimization over the simplex.
-\end{enumerate}
-
-\subsection{Sequential Sublinear Algorithm for Logistic Regression} \label{sec:l2alg}
+\subsection{Sequential Sublinear Algorithm}
 We use the following notations to define sequential sublinear algorithm for penalized logistic regression.
 Much of them are borrowed from~\cite{peng2012sublinear}.
-We will also use these notations in other algorithm definitions in the following.
-
 $clip\lc \cdot \rc$ is a projection function defined as follows:
@@
 	7:	\tspace ${\bu}_{t}\leftarrow {\bu}_{t-1}+\frac{coef}{\sqrt{2T}}{\mathbf{x}}_{{i}_{t}}$ \\
-    8:  \tspace Update soft margin $\bxi_t$ if input $\nu$ for $\ell_2$-penalty \\
-    9:  \tspace Update $\bu_t$ by soft-thresholding operations if input $\gamma$ for $\ell_1$-penalty \\
+    8:  \tspace ${\bxi}_{t}\leftarrow \argmax_{\bxi\in \Lambda}\lc{{\bp}_{t}}^{T}\bxi\rc$, if input $\nu$ for $\ell_2$-penalty \\
+    9:  \tspace $\bu_t\leftarrow$ soft-thresholding operations, if input $\gamma$ for $\ell_1$-penalty \\
 	10:	\tspaces ${\bw}_{t}\leftarrow {\bu}_{t}/\max \left\{1,\|{\bu}_{t}\|_2 \right\}$ \\
@@
 	\end{table}
+Each iteration of the \textbf{SLLR} algorithm have two phases: \textit{stochastic primal update} and \textit{stochastic dual update}.
+In the pseudo-code of Algorithm 1, line 4 to line 11 is the primal part while line 12 to line 16 is the dual part.
+We show the sublinear algorithm in a uniform way for both $\ell_2$-penalty and $\ell_1$-penalty concisely.
+If we are dealing with $\ell_2$-penalty, we ignore line 9 and accomplish the computation in line 8 through a simple greedy algorithm.
+Here, $\Lambda$ represents a Euclidean space with following conditions:
+\[
+\Lambda=\left\{ \bxi\in\mathbb{R}_{n} \, | \, \forall i, \, 0\leq{\xi}_{i}\leq 2, \, {\|\xi \|}_{1}\leq \nu n  \right
+\}.
+\]
+If we are faced with $\ell_1$-penalty, we ignore line 8 and expand the procedure line 9 as following.
+\begin{table} [ht]
+\begin{tabular}{l}
+\hline\noalign{\smallskip}
+\textbf{Procedure} Line 9 in Algorithm 1\\
+\noalign{\smallskip}
+\hline
+\noalign{\smallskip}
+Iterations: $j=1 \sim d$ \\
+\tspace \textbf{if} $\buprev_t\lj>0$ \textbf{and} $\bu_t\lj>0$ \\
+\tspace\tspace $\bu_t\lj=\max \lc \bu_t\lj-\gamma ,0 \rc$ \\
+\tspace \textbf{if} $\buprev_t\lj<0$ \textbf{and} $\bu_t\lj<0$ \\
+\tspace\tspace $\bu_t\lj=\min \lc \bu_t\lj+\gamma ,0 \rc$ \\
+$\buprev_{t+1}\leftarrow\bu_t$ \\
+\hline
+\end{tabular}
+\end{table}
 
-In the pseudo-code of Algorithm 1, line 4 to line 11 is the primal part, where $coef$ is the estimator of the gradient.
-Line 12 to line 16 is the dual part, where $\sigma$ serves as an estimator of hard margin plus soft margin.
-$\sigma$ also serves as the derivative of $\bp(i)$.
-Although the computation of line 15 and 16 makes $\hat{\sigma}$ a biased approximation, it is critical to the stability of the algorithm. The resulting bias is negligible in our approach.
-We show the sublinear algorithm in a uniform way for both $\ell_2$-penalty and $\ell_1$-penalty concisely.
-For more details, you can refer to paper~\cite{peng2012sublinear} to expand on line 8 and line 9.
+In this sequential mode, each iteration takes $O(n+d)$ time, which is sublinear to the dataset size.
 
-In the sequential mode, the primal update contains a $\ell_1$-sampling process for the choice of $i_t$, which takes $O(n)$ time, and the update of $w_t$ takes $O(d)$ time.
-And the dual update contains a $\ell_2$-sampling process for the choice of $j_t$ in $O(d)$ time, and an update of $\bp$ in $O(n) time$.
-Altogether, each iteration takes $O(n+d)$ time, which is sublinear to the dataset size.
-
-\section{Parallel Framework of Learning Algorithms for PLR} \label{sec:framework}
+\section{Parallel Framework of Learning Algorithms for LR Model} \label{sec:framework}
 In this section, we will first describe our parallel sublinear algorithm implemented in Hadoop MapReduce.
@@
 
-The datasets are always sparse for PLR is when data dimensionally is high. This makes us focus on dealing with data sparsity issue when writing code.
+The datasets are always sparse when data dimensionally is high. This makes us focus on dealing with data sparsity issue when writing code.
 This is the third important thing for the algorithm, though it reflects nowhere from the pseudo-code.
@@
     4:  ~Iterations: $t=1 \sim T$ \\
-    5:  ~\tspace gradient $\leftarrow$ points.map($(\frac{1}{1+e^{-y((\bw^T \textbf{x})+b)}}-1) * y * \bp [index]$).reduce( \_ + \_ ) \\
+    5:  ~\tspace gradient $\leftarrow$ points.map($(\frac{1}{1+e^{-y((\bw_t^T \textbf{x})+b)}}-1) * y * \bp [index]$) \\
+        ~~~\tspace\tspace\tspace\tspace\tspace .reduce(sum()) \\
     6:  ~\tspace ($\bw_{t+1}, b_{t+1}$)$\leftarrow$PrimalUpdate($\bw_t, b_t$) \\
@@
 
-We can now study the running time of parallel sublinear method for PLR.
+We can now study the running time of parallel sublinear method for LR.
 In parallel mode, the primal update contains an update of $w_t$, which takes $O(n)$ time.
-And the dual update contains a $\ell_2$-sampling process for the choice of $j_t$ in $O(d)$ time, and an update of $\bp$ in $O(1) time$.
+And the dual update contains a $\ell_2$-sampling process for the choice of $j_t$ in $O(d)$ time, and an update of $\bp$ in $O(1)$ time.
 Altogether, each iteration takes $O(n+d)$ time, which is sublinear to the dataset size.
@@
 \subsection{Parallel Gradient Descent in Spark}
-The parallel gradient descent method to solve PLR in Spark is shown below.
+The parallel gradient descent method to solve LR in Spark is shown below.
     \begin{table}[ht]
@@
     4:  Iterations: $t=1 \sim T$ \\
-    5:  \tspace gradient $\leftarrow$ points.map($(\frac{1}{1+e^{-y((\bw^T \textbf{x})+b)}}-1) * y * \bp [index]$).reduce( \_ + \_ ) \\
+    5:  \tspace gradient $\leftarrow$ points.map($(\frac{1}{1+e^{-y((\bw_t^T \textbf{x})+b)}}-1)*y$) \\
+        ~~\tspace\tspace\tspace\tspace\tspace .reduce(sum()) \\
     6:  \tspace $\bw_{t+1} = \bw_t - gradient * \textbf{x}$ \\
@@
 
+In Table~\ref{tab:table1}, \textit{Density} is computed as
+\[
+Density(Dataset)~=~\frac{\#~of~Nonzeros}{Total~\#~of~entries},
+\]
+which is adopted from~\cite{sarwar2001item}.
+\textit{Balance} describes the binary distribution of labels.
+We compute it as following:
+\[
+Balance(Dataset)~=~\frac{\#~of~Positive~Instances}{\#~of~Negative~Instances}.
+\]
 \begin{table}[h]
@@
 \hline
-    Name           & \# of Feat. & \# of Inst. & Sparsity & \# of Nonzeros & \# of +1 Inst. / \# of -1 Inst.\\
+    Name           & $n$ & $d$ & Density & Nonzeros & Balance \\
 \hline
@@
 The Simulated \textbf{2d} dataset can be viewed for visual result and serves for initial test of correctness of implementation.
-The \textbf{20NewsGroup} dataset is best-known for the test of PLR model, which has a balanced distribution between positive and negative data instances.
+The \textbf{20NewsGroup} dataset is best-known for the test of LR model, which has a balanced distribution between positive and negative data instances.
 The \textbf{Gisette} dataset is relatively larger, and data is less sparse. Thus it requires more computation theoretically.
@@
 Online stochastic gradient descent method is run on Mahout in a sequential mode.
-Liblinear~\cite{fan2008liblinear} is the baseline test program we choose. It is sequential and it outperforms many other programs for PLR on a single machine.
+Liblinear~\cite{fan2008liblinear} is the baseline test program we choose. It is sequential and it outperforms many other programs for LR on a single machine.
 SLLR performs sequential sublinear algorithm on a single machine.
@@
 \begin{figure}[tb] \label{fig:02}
-\center \includegraphics[height=5cm,width=7cm]{img/2d-show.png}
+\center \includegraphics[height=5cm,width=6cm]{img/2d-show.eps}
 \caption{Visual Result on Simulated \textbf{2d} Dataset}
@@
 \hline
-Liblinear  & 93.0\% & 92.0\% & 97.4\% & 97.1\% & $96.2\%^*$ \\
+Liblinear  & 93.0\% & 92.0\% & 97.4\% & 97.1\% & \XSolid \\
 \hline
@@
 This proves the scalability issue of Liblinear.
-However, if we take in just $\frac{1}{3}$ of the \textbf{URL-Reputation} dataset, it can return result in a very short time.
-Because of the data instances are distributed randomly, the returned result can also enjoy a very high accuracy.
 
 \begin{figure}[tb] \label{fig:03}
-\center \includegraphics[height=4.5cm,width=6cm]{img/2d_accuracy_iteration.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/2d_accuracy_iteration.eps}
 \caption{Test error, as a function of iteration number on Simulated \textbf{2d} Dataset}
@@
 \begin{figure}[tb] \label{fig:04}
-\center \includegraphics[height=4.5cm,width=6cm]{img/20NewsGroup_accuracy_iteration.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/20NewsGroup_accuracy_iteration.eps}
 \caption{Test error, as a function of iteration number on \textbf{20NewsGroup} Dataset}
@@
 \begin{figure}[tb] \label{fig:05}
-\center \includegraphics[height=4.5cm,width=6cm]{img/Gisette_accuracy_iteration.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/Gisette_accuracy_iteration.eps}
 \caption{Test error, as a function of iteration number on \textbf{Gisette} Dataset}
@@
 \begin{figure}[tb] \label{fig:06}
-\center \includegraphics[height=4.5cm,width=6cm]{img/ECUESpam_accuracy_iteration.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/ECUESpam_accuracy_iteration.eps}
 \caption{Test error, as a function of iteration number on \textbf{ECUESpam} Dataset}
@@
 \begin{figure}[tb] \label{fig:07}
-\center \includegraphics[height=4.5cm,width=6cm]{img/URL-Reputation_accuracy_iteration.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/URL-Reputation_accuracy_iteration.eps}
 \caption{Test error, as a function of iteration number on \textbf{URL-Reputation} Dataset}
@@
 \hline
-Liblinear  & 0.078s & 0.793s & 2.364s & 13.161s & $519.115s^*$ \\
+Liblinear  & 0.078s & 0.793s & 2.364s & 13.161s & \XSolid \\
 \hline
@@
 \begin{figure}[tb] \label{fig:08}
-\center \includegraphics[height=5cm,width=10cm]{img/all_time.png}
+\center \includegraphics[height=4.5cm,width=9cm]{img/all_time.eps}
 \caption{All running times}
@@
           However, it is a representative of sequential algorithm that can train massive data in acceptable time.
-          When we monitor its memory when running, it is much lower than Liblinear. This is the advantage that the online algorithm brings.
+          When we monitor its memory when running, it is much lower than Liblinear. This is the advantage brought by both online algorithm and hashing operations on features.
           Thus, it provides good scalability guarantee. If you are in the situation of single machine and limited memory, sequential online training like Mahout is recommended.
     \item The precision of all sublinear methods is acceptable. The developed parallel sublinear algorithm only has a small drop in precision.
-    \item Hadoop system has a great drawback for running PLR optimization methods. Its cluster programming model is based on acyclic data flow from stable storage to stable storage.
+    \item Hadoop system has a great drawback for running LR optimization methods. Its cluster programming model is based on acyclic data flow from stable storage to stable storage.
           Though it has the benefits of deciding where to run tasks and can automatically recover from failures in runtime, acyclic data flow is inefficient for iterative algorithms.
@@
 \begin{figure}[tb] \label{fig:09}
-\center \includegraphics[height=5cm,width=10cm]{img/2d_time.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/2d_time.eps}
 \caption{Running time, as a function of used node number on Simulated \textbf{2d} Dataset}
@@
 \begin{figure}[tb] \label{fig:10}
-\center \includegraphics[height=5cm,width=10cm]{img/20NewsGroup_time.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/20NewsGroup_time.eps}
 \caption{Running time, as a function of used node number on \textbf{20NewsGroup} Dataset}
@@
 \begin{figure}[tb] \label{fig:11}
-\center \includegraphics[height=5cm,width=10cm]{img/Gisette_time.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/Gisette_time.eps}
 \caption{Running time, as a function of used node number on \textbf{Gisette} Dataset}
@@
 \begin{figure}[tb] \label{fig:12}
-\center \includegraphics[height=5cm,width=10cm]{img/ECUESpam_time.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/ECUESpam_time.eps}
 \caption{Running time, as a function of used node number on \textbf{ECUESpam} Dataset}
@@
 \begin{figure}[tb] \label{fig:13}
-\center \includegraphics[height=5cm,width=10cm]{img/URL-Reputation_time.png}
+\center \includegraphics[height=4.5cm,width=5cm]{img/URL-Reputation_time.eps}
 \caption{Running time, as a function of used node number on \textbf{URL-Reputation} Dataset}
@@
 \begin{figure}[tb] \label{fig:14}
-\center \includegraphics[height=5cm,width=10cm]{img/fault_tolerance.png}
+\center \includegraphics[height=4.5cm,width=9cm]{img/fault_tolerance.eps}
 \caption{Iteration time, as a function of percentage of failed maps, on \textbf{URL-Reputation} Dataset, run on 6 nodes}
@@
 \section{Conclusion} \label{sec:concl}
-%conclusion & contribution & future work
-In this paper we analyzed three approaches along with three systems to fitting PLR models for large-volume, high-dimensional data for classification.
-The dataset size ranges from KB to GB.
-Hadoop, Mahout and Spark are existing well-known parallel frameworks that can be implemented with large scale machine learning algorithms.
-Parallel gradient Descent stochastic gradient descent are two existing state-of-art algorithms for parameter optimization in PLR.
-We also present a novel parallel sublinear method and make a comparison between these algorithms implemented on different systems.
-As the outcome shows, we claim parallel sublinear method implemented on Spark is the most computational efficient way to solve PLR in parallel for massive datasets.
-Moreover, fault tolerance can be provided for those lengthy distributed computations both on algorithm level and system level.
-We discussed the balance between dataset size, choosing parallel system, and choosing parallel algorithm through concrete experimental results.
+In this paper we analyzed three optimization approaches along with three computing platforms to train LR model with large-volume, high-dimensional dataset for classification.
+We focus on both algorithm design and choosing of computing platforms.
+We tested correctness, learning accuracy, running time, scalability and fault tolerance of different programs.
+These tests are objective, as the carefully chosen datasets range from KB to GB in size.
+We also consider the sparsity issues in all real world datasets.
+Test results show that different algorithms and different computing platforms have their own advantages.
+We should choose wisely of the combination of algorithm and computing platform according to dataset situations and machine resources.
+A minor contribution in this paper is to present a novel parallel sublinear algorithm for LR implemented on both Hadoop and Spark.
+We realize this paper has its limitation in both machine resources and datasets.
+It is exactly we are heading for: More machines and larger datasets will bring more convincing results.
+We also plan to employ the research angle of combining algorithm design and computing platform to study other machine learning models, thus giving more valuable suggestions in practical applications.
 

### 2013-06-13 plot_script/src/draw_time_variation.m

@@ -1,19 +1,26 @@
 clc, clear
-%dataset = '2d';
+dataset = '2d';
 %dataset = '20NewsGroup';
 %dataset = 'Gisette';
 %dataset = 'ECUESpam';
-dataset = 'URL-Reputation';
+%dataset = 'URL-Reputation';
 mat = [dataset,'_time.mat'];
 load(mat);
 figure; 
-set(gcf,'Position',[10,10,1800,900], 'color','w');
+set(gcf,'Position',[100,100,1000,750], 'color','w');
+LineWidth=3;
+MarkerSize=8;
 x=y(4:6,:);
-x=x*4;
+t=1:6;
+%x=x*4;
 b=bar(x);
-grid on;
-set(gca,'XTickLabel',{'PSUBPLR-MR','PGDPLR-SPARK','PSUBPLR-SPARK'})
+plot(t,x(1,:),'-ok','LineWidth',LineWidth,'MarkerSize',MarkerSize);
+hold on;
+plot(t,x(2,:),'--xb','LineWidth',LineWidth,'MarkerSize',MarkerSize);
+hold on;
+plot(t,x(3,:),'-vr','LineWidth',LineWidth,'MarkerSize',MarkerSize);
+hold on;
 xlabel('Number of Nodes Used','Fontsize',25,'fontweight','b');
 ylabel('Running Time per Iteration/s','Fontsize',25,'fontweight','b');
-set(gca,'fontsize',18,'fontweight','b');
-legend('1 node','2 nodes','3 nodes','4 nodes','5 nodes','6 nodes');
+set(gca,'fontsize',25,'fontweight','b');
+legend('PSUBPLR-MR','PGDPLR-SPARK','PSUBPLR-SPARK');

### 2013-06-22 draft.tex
IEEE version revised

@@
 % edited by Haoruo Peng
-% Date: 2013.6.14
+% Date: 2013.6.21
 \documentclass[10pt, conference, compsocconf]{IEEEtran}
@@
 
-%\newtheorem{theorem}{Theorem}
-%\newtheorem{lemma}{Lemma}
-%\newtheorem{definition}{Definition}
-%\newtheorem{proposition}{Proposition}
-%\newtheorem{corollary}{Corollary}
-%\newtheorem{example}{Example}
+\begin{document}
 
-\begin{document}
-%\mainmatter  % start of an individual contribution
+\title{Learning for Logistic Regression Model in Parallel}
 
-% first the title is needed
-\title{Learning for Penalized Logistic Regression Model in Parallel}
+\author{
+\IEEEauthorblockN{Haoruo Peng}
+\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\penghaoruo@hotmail.com}
+\and
+\IEEEauthorblockN{Ding Liang}
+\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\Ding\_Liang@htc.com}
+\and
+\IEEEauthorblockN{Deli Zhao}
+\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\zhaodeli@gmail.com}
+\and
+\IEEEauthorblockN{Cyrus Choi}
+\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\Cyrus\_Choi@htc.com}
+\and
+\IEEEauthorblockN{Edward Y. Chang}
+\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\Edward\_Chang@htc.com}
+}
 
-% a short form should be given in case it is too long for the running head
-%\titlerunning{Learning for Penalized Logistic Regression Model in Parallel}
-
-\author{\IEEEauthorblockN{Authors Name/s per 1st Affiliation (Author)}
-\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
-line 2: name of organization, acronyms acceptable\\
-line 3: City, Country\\
-line 4: Email: name@xyz.com}
-\and
-\IEEEauthorblockN{Authors Name/s per 2nd Affiliation (Author)}
-\IEEEauthorblockA{line 1 (of Affiliation): dept. name of organization\\
-line 2: name of organization, acronyms acceptable\\
-line 3: City, Country\\
-line 4: Email: name@xyz.com}
-}
-%
-%\author{Haoruo Peng\inst{1, 2}  \and Ding Liang\inst{1} \and Cyrus Choi\inst{1} \and Edward Y. Chang\inst{1} \and Yin Zhao\inst{2}}
-%
-%\authorrunning{Haoruo Peng \and Ding Liang \and Cyrus Choi \and Edward Y. Chang \and Yin Zhao}
-% (feature abused for this document to repeat the title also on left hand pages)
-
-%\institute %
-%{
-%\inst{}
-%HTC Research, Beijing, China 100084 \\
-%\and
-%\inst{}
-%Department of Computer Science and Technology\\
-%Tsinghua University, Beijing, China 100084
-%\email{penghaoruo@hotmail.com ...}
-%}
-%
-%\toctitle{Lecture Notes in Computer Science}
-%\tocauthor{Authors' Instructions}
 \maketitle
@@
 \begin{abstract}
-Logistic regression (LR) model has a variety of applications in the field of machine learning.
-It is a supervised learning model, and can be extended to models with regularization, which enjoy the benefits of solid statistical base.
+Logistic regression (LR) model has various applications in machine learning.
+It is a supervised learning model for pattern classification and enjoys the benefits of statistical principles.
 This paper addresses the issue of computational efficiency for solving LR in big data scenario.
-We focus on both algorithm level and computation platform level of task parallelism.
-We study three different parallel computation platforms along with three different types of parallel algorithms to efficiently improve scalability.
-Hadoop, Mahout and Spark are three existing well-known parallel computing platforms that can be implemented with large scale machine learning algorithms.
-Parallel gradient Descent and stochastic gradient descent are two state-of-art algorithms for parameter optimization in LR.
-We also present a novel parallel sublinear method based on its sequential version.
-We then make a comparison between these algorithms implemented in different platforms.
-As the outcome shows, we can choose different algorithms in different situations in terms of datasets and machine resources for tradeoff between efficiency and precision.
-To enhance practicality, we provide fault tolerance for those  parallel distributed computations.
+We compare between different computing platforms and different parallel algorithms.
+Our goal is to offer valuable suggestions on choosing computing platforms and learning algorithms according to different application situations for specific datasets and machine resources.
+Three different parallel computing platforms along with three different types of parallel algorithms are carefully studied in this paper.
+In such process, we present a novel parallel sublinear method based on its sequential version as another contribution.
+%Hadoop, Mahout and Spark are three existing parallel computing platforms that can be implemented with large scale machine learning algorithms.
+%Parallel gradient Descent and stochastic gradient descent are two state-of-art algorithms for solving LR.
+To enhance practicality, we consider tradeoff between efficiency and precision.
+We also provide fault tolerance for parallel distributed computations.
 \end{abstract}
@@
 \section{Introduction} \label{sec:int}
-Logistic regression model~\cite{HastieBook:SL} plays a vital role in machine learning and data mining.
-It is a widely used model in algorithms like PageRank~\cite{page1999pagerank} and Anti-spam Filtering~\cite{androutsopoulos2000evaluation}.
-The model serves for classification problems, and enjoys a substantial body of supporting theories and algorithms.
-Thus, a binary classification problem modeled by LR can be easily extended to a multi-classification problem.
-Also, due to the strong statistical foundation of LR model, we can extend results into a deeper analysis which may apply to other classification models.
-We will focus on the binary LR model in the rest of the paper.
+Logistic regression model~\cite{HastieBook:SL} plays a vital role in machine learning.
+It is a widely used model in algorithms like PageRank~\cite{page1999pagerank} and anti-spam filtering~\cite{androutsopoulos2000evaluation}.
+The model serves for classification problems, and is supported by a substantial body of statistical theories and algorithms.
+A binary classification problem modeled by LR can be easily extended to a multi-class classification problem.
+Also, due to the strong statistical foundation of the LR model, we can extend achieved results into a deeper analysis which may apply to other classification models.
+We will focus on the binary LR model in this paper.
 
-In recent years, many modern massive datasets are getting larger and larger.
-A most identifiable characteristic of these datasets is that the size of their training data is very large and data dimensionality is very high.
+In recent years, many modern datasets are increasingly larger and larger.
+A most identifiable characteristic of these datasets is that data scale is very large and data dimensionality is very high.
 Large data volume and high data dimensionality bring unavoidable computational challenges to machine learning problems.
-For example, in social networks, we have datasets~\cite{lewis2008tastes} covering multiple dimensions like friendship relationship, share of common interests.
-They generally include of millions of records over millions of attributes.
-More evidently, for the task of text categorization, we usually have to face a dataset with data volume in the billion scale and each data instance is characterized by thousands of feature dimensions~\cite{lewis2004rcv1}.
+For example, in social networks, we have datasets~\cite{lewis2008tastes} covering multiple dimensions like friendship relationship and share of common interests.
+They generally include millions of records over millions of attributes.
+More evidently, for the task of text categorization, we usually have to handle datasets with data volumes in billion scales and each data instance is characterized by thousands of feature dimensions~\cite{lewis2004rcv1}.
 We tackle these challenges on both algorithm level and computing platform level via parallelization methods.
-For many applications, in order to have speedup in performance, we can employ not only task parallelism, but also data parallelism~\cite{subhlok1993exploiting}.
+For many applications, in order to attain speedup in performance, we can employ not only task parallelism, but also data parallelism~\cite{subhlok1993exploiting}.
 In this paper, we mainly discuss issues in task parallelism.
 
-When developing parallel algorithms for LR, it is unavoidable to come across the question of choosing which parallel computing platform to employ.
+When developing parallel algorithms for LR, it is inevitable to come across the question of choosing which parallel computing platform to employ.
 After a thorough survey, we choose three unique and best-known computing platforms to test: Hadoop~\cite{white2012hadoop}, Mahout~\cite{mahoutscalable} and Spark~\cite{zaharia2010spark}.
 Hadoop employs HDFS~\cite{borthakur2008hdfs} and MapReduce~\cite{dean2008mapreduce}.
-Mahout runs on Apache Hadoop and makes improvements in the low level code.
-Spark features for iterative algorithms and also supports HDFS.
-We will compare design features of them separately in related work section.
+Mahout runs on Apache Hadoop and makes improvements in low level code.
+Spark promotes efficiency of iterative algorithms and also supports HDFS.
+We will compare design features of these three computing platforms separately in Section~\ref{sec:platform}.
 
-In sequential parameter optimization algorithms for LR model, a classical way is to turn to stochastic approximation methods.
-Stochastic approximation methods, such as stochastic gradient descent~\cite{zhang2004solving} and stochastic dual averaging~\cite{xiao2010dual}, obtain optimal generalization guarantees with a small number of passes over the data with runtime linear to the dataset size.
-The stochastic gradient descent method can work in an online fashion, as we view the sampled data points as the come-in data stream.
+In sequential optimization algorithms for LR model, a classical way is to resort to stochastic approximation methods.
+Stochastic approximation methods, such as stochastic gradient descent~\cite{zhang2004solving} and stochastic dual averaging~\cite{xiao2010dual}, obtain optimal generalization guarantees with a small number of passes over data with runtime linear to the dataset size.
+The stochastic gradient descent method can work in an online fashion, as we view sampled data points as data stream over algorithmic iteration.
 It is hard to be changed to task-parallelism, but it is blazingly fast.
-If we take a step back and go back to the general gradient descent to solve LR model, we can find that it can be actually embarrassingly parallel.
-We can take in all the data at the same iteration and just compute the gradient in a MapReduce fashion.
-We can further speed up the runtime by employing sublinear algorithms~\cite{peng2012sublinear} via the use of stochastic approximation idea.
-This methods access a single feature of training vectors instead of entire training vectors at each iteration.
+If we take a step back to the general gradient descent to solve LR model, we can find that it can be actually embarrassingly parallel.
+We can take in all of the data at the same iteration and just compute the gradient in a MapReduce fashion.
+We can further speed up the runtime by employing sublinear algorithms~\cite{peng2012sublinear} via the application of the stochastic approximation idea.
+These methods access a single feature of feature vectors instead of entire feature vectors at each iteration.
 We propose a parallel version of this algorithm and achieve the result of comparable accuracy while being faster convergent.
-
-The rest of the paper is organized as follows:
-Section~\ref{sec:rew} discusses some related work.
-In Section~\ref{sec:plr}, we review the logistic regression model and the sequential sublinear algorithm.
-In Section~\ref{sec:framework}, we present the parallel framework of all three different algorithms for LR model.
-Section~\ref{sec:setup} describes the datasets and the baseline of our experiments and Section~\ref{sec:experiment} presents the experimental results.
-Finally, we offer our concluding remarks in Section~\ref{sec:concl}.
 
@@
 
-\subsection{Scalability Improvement in Big Data Research}
-In big data scenario, large datasets require us to develop machine learning algorithms towards a more efficient and more parallelized end.
+\subsection{Scalability Solutions}
+%
+In big data scenarios, large datasets require us to develop machine learning algorithms towards a more efficient and more parallelized end.
 Researchers have already done much work to cater for the needs of massive datasets.
-Early work like PSVM (\textit{Parallel Support Vector Machines})~\cite{chang2011psvm} employed an approximation matrix decomposition method based on row selections to reduce the memory when running the algorithm.
-It can then increase the number of participated parallel computation nodes to several hundreds.
-Later, the work of PLDA (\textit{Parallel Latent Dirichlet Allocation})~\cite{wang2009plda} further improve the computational efficiency of the LDA model through the use of sampling methods.
-The proposed parallel algorithm in Hadoop is robust, for it has fault tolerance of machine failures, taking the advantage of Hadoop.
-Recently, the work by Dean et al.\cite{le2011building} showed that the advantage of parallelization is fully taken in deep learning algorithms.
-It pushed the limits of parallel computational nodes to a hundred-million level, and in the meantime, achieved a best learning performance ever.
-GraphLab~\cite{kyrola2012graphchi}, a recent developed tool for large-scale machine learning. It tackles with efficiency and scalability problems of machine leaning algorithms when applied to graphs.
+Early work like Parallel Support Vector Machines (PSVM)~\cite{chang2011psvm} employed an approximation matrix decomposition method based on row selections to reduce memory usage.
+It can then increase the number of parallel computational nodes to several hundreds.
+Later, the work of Parallel Latent Dirichlet Allocation (PLDA)~\cite{wang2009plda} improves the computational efficiency of the LDA model by means of sampling methods.
+The parallel algorithm in Hadoop is robust, for it has fault tolerance of machine failures, thus taking advantage of Hadoop features.
+Recently, Dean \etal~\cite{le2011building} claimed that the advantage of parallelization is fully taken in deep learning algorithms.
+It pushed the limit of parallel computational nodes to a hundred-million level, and in the meantime, achieved the best learning performance ever.
+GraphLab~\cite{kyrola2012graphchi} is a recently developed tool for large-scale machine learning.
+It tackles efficiency and scalability problems of machine leaning algorithms by graph-theoretical models.
 
-\subsection{Three Computing Platforms}
-Three computing platforms we are working on each features for its own advantage in implementing machine learning algorithms.
+\subsection{Computing Platforms}\label{sec:platform}
+Three computing platforms that we are working on have their own advantages to implement machine learning algorithms.
 The Apache Hadoop~\cite{white2012hadoop} software library allows for distributed processing of large datasets across clusters of computers using simple programming models.
@@
 MapReduce paradigm takes a set of key-value pairs as its input.
-Then a user-defined \textit{map} function turns input key-value pairs into some intermediate key-value pairs.
-A user-defined \textit{reduce} function merges values for the same intermediate key to produce output.
-All of the processing is independent and it makes MapReduce paradigm easy to be parallelized.
-In addition, Hadoop provides a distributed file system (HDFS).
-Both MapReduce and HDFS are designed to handle node failures in an automatical way, making Hadoop support large clusters built on commodity hardware.
+Then a user-defined \textit{map} function turns the input into some intermediate key-value pairs.
+Another user-defined \textit{reduce} function merges values for the same intermediate pairs to produce output.
+All of the operations are independent, thereby making MapReduce paradigm easy to be parallelized.
+In addition, Hadoop provides a Distributed File System (HDFS).
+Both MapReduce and HDFS are designed to handle node failures in an automatic way, making Hadoop support large clusters that are built on commodity hardware.
 The goal of Apache Mahout~\cite{mahoutscalable} is to build scalable machine learning libraries.
-Their core algorithms for clustering, classification and batch based collaborative filtering are implemented on top of Apache Hadoop using the MapReduce paradigm.
-The core libraries are so highly optimized that it also has good performance for non-distributed algorithms.
-Spark~\cite{zaharia2010spark} is a cluster computing system that aims to make data analytics fast.
-Spark provides support in-memory cluster computing. A job can load data into memory and query it repeatedly by creating and caching resilient distributed datasets (\textit{RDDs}).
-Moreover, RDDs achieve fault tolerance through lineage: RDDs always have enough information about how they were derived from other RDDs, and they are easy to be rebuilt if a certain partition is lost.
-Spark can run up to 100 times faster than Hadoop MapReduce for iterative algorithms.
+Their core algorithms for clustering, classification and collaborative filtering are implemented on top of Apache Hadoop using the MapReduce paradigm.
+The core libraries are highly optimized so that Apache Mahout also has good performance for non-distributed algorithms.
+Spark~\cite{zaharia2010spark} is a cluster computing system that aims to make data analysis fast.
+Spark supports in-memory cluster computing. A job can load data into memory and query it repeatedly by creating and caching resilient distributed datasets (RDDs).
+Moreover, RDDs achieve fault tolerance through lineage: information about how RDDs are derived from other RDDs is stored in reliable storage, thus making RDDs easy to be rebuilt if a certain partition is lost.
+Spark can run up to 100 times faster than Hadoop for iterative algorithms.
 
-In Table~\ref{tab:systemcmp}, we compare between Hadoop and Spark computing platforms.
+In Table~\ref{tab:systemcmp}, we compare different features between Hadoop and Spark computing platforms.
 As Mahout is mainly built on Hadoop, it inherits most of Hadoop features.
-To better illustrate, we use short abbreviations in the table.
+For simplicity, we use short abbreviations in the table.
 Spark supports two types of operations on RDDs: Actions and Transformations (As and Ts).
-Actions include functions like \textbf{count}, \textbf{collect} and \textbf{save}. They usually return a result from input RDDs.
-Transformations include functions like \textbf{map}, \textbf{filter} and \textbf{join}. They normally build new RDDs from other RDDs, which are under the lineage rule.
+Actions include functions like \textit{count}, \textit{collect} and \textit{save}. They usually return a result from input RDDs.
+Transformations include functions like \textit{map}, \textit{filter} and \textit{join}. They normally build new RDDs from other RDDs, which comply with the lineage rule.
 In the table, we use "NFS" to represent "Normal File System" and "Fault Tolerance" here is specifically for node failure situations.
@@
 \centering
-\caption{Platform Comparison: Hadoop VS Spark}\label{tab:systemcmp}
+\caption{Platform Comparison: Hadoop vs. Spark}\label{tab:systemcmp}\vspace{-0.3cm}
 \begin{tabular}{|c|c|c|}
@@
 \hline
-\end{tabular}
+\end{tabular}\vspace{-0.5cm}
 \end{table}
 
-\subsection{Previous Research on Sublinear Method}
-Sublinear method is recently developed by many contributing researchers.
-Clarkson et al.~\cite{clarkson2010sublinear} first proposed the method of approximation algorithms in sublinear time.
+\subsection{Sublinear Methods}
+Sublinear methods are recently proposed by many researchers.
+Clarkson \etal~\cite{clarkson2010sublinear} first presented the solution of approximation algorithms in sublinear time.
 It is applied to optimization problems for linear classifiers and minimum enclosing balls.
 The algorithm employs a novel sampling technique along with a new multiplicative update procedure.
-Hazan et al.~\cite{hazanbeating} exploited the approach to linear SVM (\textit{Support Vector Machine}).
-Cotter et al.~\cite{cotter2012kernelized} continued to extend the method to kernelized SVM.
-In~\cite{hazan2011optimal}, Hazan et al. applied the sublinear approximation approach for solving linear regression with penalties.
-Garber and Hazan~\cite{garberapproximating} also developed it in SDP (\textit{Semidenfinite Programming}).
-Peng et al.~\cite{peng2012sublinear} utilized the method in LR model with penalties and developed sequential sublinear algorithms for both $\ell_1$-penalty and $\ell_2$-penalty separately.
+Hazan \etal~\cite{hazanbeating} exploited the approach to linear SVM.
+Cotter \etal~\cite{cotter2012kernelized} extended the method to kernelized SVM.
+In~\cite{hazan2011optimal}, Hazan \etal applied the sublinear approximation approach to solve linear regression with penalties.
+Garber and Hazan~\cite{garberapproximating} also developed it in Semi-Definite Programming (SDP).
+Peng \etal~\cite{peng2012sublinear} utilized the method in the LR model with penalties and developed sequential sublinear algorithms for both $\ell_1$-penalty and $\ell_2$-penalty.
 
@@
 
-\subsection{Logistic Regression Model}
+\subsection{Logistic Regression Model} \label{sec:def}
 In this paper, we are mainly concerned with the binary classification problem.  	
-We define training dataset as $\XM=\{(\x_i, y_i): i=1, \ldots, n\}$, where $\x_i \in \RB^d$ are input samples and $y_i \in \{-1, 1\}$ are the corresponding labels.
-For simplicity, we will use the notation $\X=[{\x}_{1}, {\x}_{2}, \ldots, {\x}_n]^{T}$ and $\y=(y_1, y_2, \ldots, y_n)^T$ to represent training dataset in the following.
-Then to fit in the logistic regression model, the expected value of $y_i$ is given by
+We define the training dataset as $\XM=\{(\x_i, y_i): i=1, \ldots, n\}$, where $\x_i \in \RB^d$ are input samples and $y_i \in \{-1, 1\}$ are the corresponding labels.
+For simplicity, we will use the notation $\X=[{\x}_{1}, {\x}_{2}, \ldots, {\x}_n]^{T}$ and $\y=(y_1, y_2, \ldots, y_n)^T$ to represent the training dataset in the following.
+To fit in the logistic regression model, the expected value of $y_i$ is given by\vspace{-0.2cm}
 \[
-P(y_i|\x_i)= \frac{1}{1+ \exp(- y_i(\x_i^T \w + b))} \triangleq g_i(y_i),
+P(y_i|\x_i)= \frac{1}{1+ \exp(- y_i(\x_i^T \w + b))} \triangleq g_i(y_i),\vspace{-0.2cm}
 \]
@@
 To make the optimization problem more practical to solve, a common practice is to add penalties to LR model.
-Typically, for $\ell_2$-penalty, we have to solve the following optimization problem:
+Typically, for $\ell_2$-penalty, we solve the following optimization problem:\vspace{-0.2cm}
 \begin{equation} \label{eqn:1}
-	\max_{\bw ,b} \; \Big\{F(\w, b| \XM) - \frac{\lambda}{2}  \|\bw\|_2^{2} \Big\}.
+	\max_{\bw ,b} \; \Big\{F(\w, b| \XM) - \frac{\lambda}{2}  \|\bw\|_2^{2} \Big\}.\vspace{-0.2cm}
 \end{equation}
-For $\ell_1$-penalty, we are faced with the following optimization problem:
+For $\ell_1$-penalty, we optimize the following criterion: \vspace{-0.2cm}
 \begin{equation} \label{eqn:2}
-	\max_{\bw ,b} \;  \big\{F(\w, b|\XM)- \gamma{\|\bw \|}_{1}\big\}.	
+	\max_{\bw ,b} \;  \big\{F(\w, b|\XM)- \gamma{\|\bw \|}_{1}\big\}.\vspace{-0.2cm}	
 \end{equation}
-Here, we have
-\[
-F(\w, b| \XM) = \sum_{i=1}^n \log g_i(y_i)
-\]
-in both (\ref{eqn:1}) and (\ref{eqn:2}).
-To be brief, we omit the derivation here.
+Here, we define $F(\w, b| \XM) = \sum_{i=1}^n \log g_i(y_i)$ in both (\ref{eqn:1}) and (\ref{eqn:2}). To be brief, we omit the derivation here.
 
 \subsection{Sequential Sublinear Algorithm}
-We use the following notations to define sequential sublinear algorithm for penalized logistic regression.
-Much of them are borrowed from~\cite{peng2012sublinear}.
-$clip\lc \cdot \rc$ is a projection function defined as follows:
-\[
-clip\lc a,b \rc \triangleq \max \lc \min \lc a,b \rc ,-b\rc \,\,\,\,\,\, a,b \in \mathbb{R}.
-\]
-
-$\sgn \lc \cdot \rc$ is the sign function; namely,
-\[
-\sgn \lc x \rc =
-\begin{cases}
-	+1 & \text{ if } x>0  \\
-	0  & \text{ if } x=0  \\
-	-1 & \text{ if } x<0.
-\end{cases}
-\]
-
-$g\lc \cdot \rc$ is the logistic function; namely,
-\[
-g \lc x \rc=\frac{1}{1+e^{-x}}
-\]
+We use the following notations to define sequential sublinear algorithm for penalized logistic regression. $clip\lc \cdot \rc$ is a projection function defined as $
+clip\lc a,b \rc \triangleq \max \lc \min \lc a,b \rc ,-b\rc,\,a,b\in \mathbb{R}$. $\sgn \lc \cdot \rc$ is the sign function; namely, $\sgn \lc \cdot \rc \in \{-1,0,1\}$.
+$g\lc \cdot \rc$ is the logistic function $g \lc x \rc=1/(1+e^{-x})$.
 
 In Algorithm~1, we give the sequential sublinear approximation procedure for logistic regression.
+The algorithm is mainly from~\cite{peng2012sublinear}.
+Symbols we use here comply with the definition in Section~\ref{sec:def}.
+$\varepsilon$ controls learning rate, $T$ determines iteration number, and $\eta$ defines approximation level.
 	\begin{table} [ht]
@@
 	\hline\noalign{\smallskip}
-	\textbf{Algorithm 1} SLLR \\
+	\textbf{Algorithm 1}: Sub-Linear Logistic Regression (SLLR) \\
 	\noalign{\smallskip}
@@
 	\end{table}
-Each iteration of the \textbf{SLLR} algorithm have two phases: \textit{stochastic primal update} and \textit{stochastic dual update}.
-In the pseudo-code of Algorithm 1, line 4 to line 11 is the primal part while line 12 to line 16 is the dual part.
-We show the sublinear algorithm in a uniform way for both $\ell_2$-penalty and $\ell_1$-penalty concisely.
-If we are dealing with $\ell_2$-penalty, we ignore line 9 and accomplish the computation in line 8 through a simple greedy algorithm.
-Here, $\Lambda$ represents a Euclidean space with following conditions:
-\[
+Each iteration of the SLLR algorithm has two phases: \textit{stochastic primal update} and \textit{stochastic dual update}.
+Steps from line 4 to line 11 consist of the primal part while the dual part is composed of steps from line 12 to line 16.
+We give the sublinear algorithm in a unified way for $\ell_2$-penalty and $\ell_1$-penalty.
+If we are dealing with $\ell_2$-penalty, we ignore line 9 and accomplish the computation in line 8 by a simple greedy algorithm.
+Here, $\Lambda$ represents a Euclidean space with conditions $
 \Lambda=\left\{ \bxi\in\mathbb{R}_{n} \, | \, \forall i, \, 0\leq{\xi}_{i}\leq 2, \, {\|\xi \|}_{1}\leq \nu n  \right
-\}.
-\]
-If we are faced with $\ell_1$-penalty, we ignore line 8 and expand the procedure line 9 as following.
+\}$.
+If we are faced with $\ell_1$-penalty, we ignore line 8 and expand the procedure of line 9 as following.
 \begin{table} [ht]
@@
 \hline\noalign{\smallskip}
-\textbf{Procedure} Line 9 in Algorithm 1\\
+\textbf{Procedure}: Line 9 in Algorithm 1\\
 \noalign{\smallskip}
@@
 
-\section{Parallel Framework of Learning Algorithms for LR Model} \label{sec:framework}
-In this section, we will first describe our parallel sublinear algorithm implemented in Hadoop MapReduce.
-Then we will show a slightly different version implemented in Spark.
-We will also formally introduce the traditional parallel gradient algorithm we use in Spark and describe the online stochastic gradient descent method used in Mahout.
-
-\subsection{Parallel Sublinear algorithms in Hadoop MapReduce}
-We develop an approach to solve sublinear learning for penalized logistic regression using the architecture of MapReduce.
-The pseudo-code of Algorithm 2, Procedure for Primal-Map, Procedure for Primal-Reduce, Procedure for PrimalUpdate, Procedure for Dual-Map, and Procedure for DualUpdate explain the critical parts of this algorithm.
+\section{Parallel Sublinear Logistic Regression} \label{sec:framework}
+In this section, we will describe our parallel sublinear algorithms implemented in Hadoop and Spark.
+We will also formally introduce the traditional parallel gradient algorithm used in Spark and the online stochastic gradient descent method used in Mahout.
+In all pseudo-code, we follow symbol notations defined in Section~\ref{sec:def}.
+\subsection{Parallel Sublinear Algorithms in Hadoop}
+We develop an algorithm to sublinear learning for logistic regression using the architecture of MapReduce.
+The pseudo-code of Algorithm 2, Procedure for Primal-Map, Procedure for Primal-Reduce, Procedure for Primal-Update, Procedure for Dual-Map, and Procedure for Dual-Update explain the critical parts of this algorithm.
 	\begin{table}[ht]
@@
 	\hline\noalign{\smallskip}
-	\textbf{Algorithm 2} PSUBPLR-MR \\
+	\textbf{Algorithm 2}: PSUBPLR-MR \\
 	\noalign{\smallskip}
@@
     11: \tspaces job\_primal.run() \\
-    12: \tspaces ($\bw_{t+1}, b_{t+1}$)$\leftarrow$PrimalUpdate($\bw_t, b_t$) \\
+    12: \tspaces ($\bw_{t+1}, b_{t+1}$)$\leftarrow$Primal-Update($\bw_t, b_t$) \\
     13: \tspaces Choose $j_t \leftarrow j$ with probability ${{\bw}_{t+1}\lj}^{2}/{\|{\bw}_{t+1}\|_2}^{2} $ \\
@@
     20: \tspaces job\_dual.run() \\	
-    21: \tspaces $\bp_{t+1}$$\leftarrow$DualUpdate($\bp_t$) \\
+    21: \tspaces $\bp_{t+1}$$\leftarrow$Dual-Update($\bp_t$) \\
     22: Output: $\bar{\bw}=\frac{1}{T}\sum_{t}{\bw}_{t},\bar{b}=\frac{1}{T}\sum_{t}{b}_{t}$ \\
@@
 	\end{table}
-
+     %
     \begin{table}[ht]
@@
 	\hline\noalign{\smallskip}
-	\textbf{Procedure} Primal-Map(inputfile) \\
+	\textbf{Procedure}: Primal-Map(inputfile) \\
 	\noalign{\smallskip}
@@
 	\end{table}
-
+    %
     \begin{table}[ht]
@@
 	\hline\noalign{\smallskip}
-	\textbf{Procedure} Primal-Reduce(key\_in, value\_in) \\
+	\textbf{Procedure}: Primal-Reduce(key\_in, value\_in) \\
 	\noalign{\smallskip}
@@
 	\hline\noalign{\smallskip}
-	\textbf{Procedure} PrimalUpdate($\bw_t, b_t$) \\
+	\textbf{Procedure}: Primal-Update($\bw_t, b_t$) \\
 	\noalign{\smallskip}
@@
 	\hline\noalign{\smallskip}
-	\textbf{Procedure} Dual-Map(inputfile) \\
+	\textbf{Procedure}: Dual-Map(inputfile) \\
 	\noalign{\smallskip}
@@
 	\hline\noalign{\smallskip}
-	\textbf{Procedure} DualUpdate($\bp_t$) \\
+	\textbf{Procedure}: Dual-Update($\bp_t$) \\
 	\noalign{\smallskip}
@@
 This parallel design generally follows the framework of sequential sublinear algorithm.
-It remains to have two computational components in each iteration: the primal update part from line 4 to line 12 and dual update part from line 13 to line 21.
-Within the primal update part, there has been a parallel implementation period from line 4 to line 11, and also a unavoidable sequential period as illustrated in line 12.
-Within the dual part, it is the same situation that a parallel implementation period from line 14 to 20 is surrounded by sequential periods for line 13 and line 21.
-Moreover, as the primal part and dual part are decoupled in the sense of the parameters that they affect. We can start these two separate MapReduce jobs in a iteration simultaneously.
-This brings us further parallelization and makes the algorithm more efficient.
+It remains to have two computational components in each iteration: the primal update part from line 4 to line 12 and the dual update part from line 13 to line 21.
+Within the primal update part, there is a parallel implementation period from line 4 to line 11, and also an unavoidable sequential period as illustrated in line 12.
+Within the dual part, it is the same situation that steps from line 14 to 20 employ parallel implementation while sequential operation is implemented in line 13 and line 21.
+As the primal part and dual part are decoupled in the sense of the parameters that they affect, these two separate MapReduce jobs can be performed simultaneously for each iteration, which brings us further parallelization and makes the algorithm more efficient.
 This framework is shown explicitly in Fig.~\ref{fig:frame}.
+%
+\begin{figure}[tb]
+\center \includegraphics[height=3.0cm,width=6.5cm]{img/framework.png}\vspace{-0.4cm}
+\caption{Parallel implementation flow chart for PSUBPLR-MR}\label{fig:frame}\vspace{-0.5cm}
+\end{figure}
+%
 
-\begin{figure}[tb] \label{fig:frame}
-\center \includegraphics[height=3.5cm,width=6cm]{img/framework.png}
-\caption{Parallel implementation flow chart for PSUBPLR-MR}
-\end{figure}
-
-For the parallelization period in the \textit{primal mapreduce job}, we take advantage of the MapReduce design that takes in every data instance in the training matrix.
-Instead of the fashion in the sequential algorithm that we only sample a data instance in the primal update step, we compute gradients from "almost" all data instances and make the weighted average value according to vector $\bp$ as the output gradient for update.
-The details of this algorithm design is shown in \textbf{Procedure Primal-Map(inputfile)} and \textbf{Procedure Primal-Reduce(key in, value in)}.
-Here, we employ a randomization when we compute those "almost" all gradients.
-As you can interpret from line 7 and 8 from \textbf{Procedure Primal-Map(inputfile)}, if $r=0$, then all data instances are computed.
+For the parallelization period in the \textit{primal mapreduce job}, we take advantage of the MapReduce design that takes in every data instance.
+Instead of the fashion in the sequential algorithm that we only sample one data instance in the primal update step, we compute gradients from ``almost" all data instances and make the weighted average value according to vector $\bp$ as the output gradient for update.
+The details of this algorithm design is shown in Procedure Primal-Map and Procedure Primal-Reduce.
+Here, we employ a randomization strategy when we compute those ``almost" all gradients.
+From line 7 to line 8 in Procedure Primal-Map, all data instances are computed if $r=0$.
 As the expectation value for $\bp_t(i_t)$ is $\frac{1}{n}$, we normally set $r$ to range from 0 to 1.
@@
 
-There are also three more things that have to be addressed here.
-First is the parameter passing issues. It critical to choose an efficient way to pass the updated parameters between iteration and even between different MapReduce jobs.
+There are also three more things that need to be handled here.
+First is the parameter passing issue. It is critical to choose an efficient way to pass the updated parameters between iterations and even between different MapReduce jobs.
 It is even more challenging when we have to deal with HDFS. It is clear that the fastest communication way is to pass parameters by \textit{Configuration()}.
-However, it always has memory buffer size limits, and will greatly impair scalability when the number of parameters is huge.
-Another way is to compress the parameter sequence in a string when sending and uncompress them when receiving.
-It has computational overhead and it still can not avoid the issue of memory buffer limit.
-Thinking back on the philosophy of the design of Hadoop, the natural thing is to pass parameters by file, the same way to pass all the data.
-We admit that it is inefficient, but it is the only way to support for large datasets.
+However, it always suffers from memory buffer limits, and will greatly impair scalability when the number of parameters is huge.
+Another way is to compress the parameter sequence in a string when sending and uncompress them when receiving. It has computational overhead and it still cannot avoid the issue of memory buffer limit.
+Considering the philosophy of the design of Hadoop, the natural thing to do is to pass parameters by file, the same way to pass all the data.
+Although such an operation is insufficiently efficient, it is the feasible way to support large datasets.
 
-The second issue is the small changes we make to cater for the $\ell_2$-penalty and $\ell_1$-penalty. The changes is only made in \textbf{Procedure PrimalUpdate}.
-It does not affect little for the implementation, and the extension is just the same as that in \textbf{Algorithm SLLR}.
-To have a brief and standard framework, we omit the explanation here.
+The second issue is the small changes that we make to cater for the $\ell_2$-penalty and $\ell_1$-penalty. The changes are only made in Procedure Primal-Update.
+It affects little for the implementation, and the extension is just the same as that in Algorithm~1.
+To make the framework brief and standard, we omit the explanation here.
 
-The datasets are always sparse when data dimensionally is high. This makes us focus on dealing with data sparsity issue when writing code.
-This is the third important thing for the algorithm, though it reflects nowhere from the pseudo-code.
-Instead of naively writing the simple code for data intensive situations, we assign the index value for each data value in the sparse vector, and all computations are changed accordingly.
-This gives us great efficiency improvement, and all results in section~\ref{sec:experiment} are using the code for sparsity.
+The datasets are generally sparse when data dimensionally is high. This characteristic makes us focus on dealing with data sparsity issue when writing code.
+This is the third important thing for the algorithm, although it is not reflected in the pseudo-code.
+Instead of naively writing the simple code in data intensive situations, we assign the \textit{index} for each data value in the sparse vector, and all computations are changed accordingly.
+This sparse format brings us great efficiency improvement, and all results in Section~\ref{sec:experiment} are obtained from the code for sparsity.
 
@@
 The algorithm to solve sublinear learning for penalized logistic regression in Spark is shown below.
-In the pseudo-code of Algorithm 3, Procedure for PrimalUpdate and Procedure for Dual-Map are the same as those in \textbf{Algorithm  PSUBPLR-MR}.
+In the pseudo-code of Algorithm 3, the procedure for Primal-Update and the procedure for Dual-Map are the same as those in Algorithm PSUBPLR-MR.
     \begin{table}[ht]
@@
     \hline\noalign{\smallskip}
-	\textbf{Algorithm 3} PSUBPLR-SPARK \\
+	\textbf{Algorithm 3}: PSUBPLR-SPARK \\
 	\noalign{\smallskip}
@@
         ~~~\tspace\tspace\tspace\tspace\tspace .reduce(sum()) \\
-    6:  ~\tspace ($\bw_{t+1}, b_{t+1}$)$\leftarrow$PrimalUpdate($\bw_t, b_t$) \\
+    6:  ~\tspace ($\bw_{t+1}, b_{t+1}$)$\leftarrow$Primal-Update($\bw_t, b_t$) \\
     7:  ~\tspace Choose $j_t \leftarrow j$ with probability ${{\bw}_{t+1}\lj}^{2}/{\|{\bw}_{t+1}\|_2}^{2} $ \\
     8:  ~\tspace pAdjust $\leftarrow$ points.map(MW-Update()).reduce(copy()) \\
-    9:  ~\tspace $\bp_{t+1}$$\leftarrow$DualUpdate($\bp_t$)  \\
+    9:  ~\tspace $\bp_{t+1}$$\leftarrow$Dual-Update($\bp_t$)  \\
     10: \textbf{Output}($\bw, b$) \\
@@
 
-This parallel design is very similar to that of \textbf{Algorithm  PSUBPLR-MR}.
+This parallel design is very similar to that of Algorithm PSUBPLR-MR.
 The most important difference is the \textit{cache()} operation in line 3.
-To make it work in Spark, we follow the rules to construct an RDD for each data instance.
-Also to cater for data sparsity, the design is the every data value correspond to its individual index. And the index also participate in the computation along with the value.
-We also omit the changes for $\ell_2$-penalty and $\ell_1$-penalty here to make the algorithm easier to be understood.
+To make it work in Spark, we follow the rule to construct an RDD for each data instance.
+Also to cater for data sparsity, the design is that every data value correspond to its individual \textit{index}. And the \textit{index} is also involved in the computation along with the value.
+We omit the changes for $\ell_2$-penalty and $\ell_1$-penalty here to make the algorithm easier to be understood.
 
-We can now study the running time of parallel sublinear method for LR.
-In parallel mode, the primal update contains an update of $w_t$, which takes $O(n)$ time.
-And the dual update contains a $\ell_2$-sampling process for the choice of $j_t$ in $O(d)$ time, and an update of $\bp$ in $O(1)$ time.
-Altogether, each iteration takes $O(n+d)$ time, which is sublinear to the dataset size.
-Compared to the analysis of sequential algorithm, parallelization does not change computational complexity.
-However, by reducing the constant coefficient from 2 to 1 in each iteration, it can be two times faster than sequential sublinear algorithm theoretically.
-Moreover, by starting two separate MapReduce jobs in a iteration simultaneously, the running time can be reduced to $O(max\{n,d\})$.
+In parallel mode, the primal update contains the update of $\bw_t$, which takes $O(n)$ time.
+The dual update contains the $\ell_2$-sampling process for the choice of $j_t$ in $O(d)$ time, and the update of $\bp$ in $O(1)$ time.
+Altogether, each iteration takes $O(n+d)$ time.
+Compared to the analysis of sequential algorithm, parallelization does not necessarily change computational complexity.
+Theoretically, by deeper analysis of constant coefficients of the obtained computational complexity, parallel sublinear algorithm can be two times faster than the sequential version.
+Moreover, by starting two separate MapReduce jobs in one iteration simultaneously, the running time can be reduced to $O(max\{n,d\})$.
 
@@
     \hline\noalign{\smallskip}
-	\textbf{Algorithm 4} PGDPLR-SPARK \\
+	\textbf{Algorithm 4}: PGDPLR-SPARK \\
 	\noalign{\smallskip}
@@
 
-In the pseudo-code of Algorithm 4, we can find that it is implemented in an embarrassingly parallel mode.
-We can take in all the data at the same iteration and just compute the gradient in a MapReduce fashion.
-As for the \textit{cache()} operation and RDD design for data sparsity, it is the same as \textbf{Algorithm PSUBPLR-SPARK}.
+In the pseudo-code of Algorithm 4, it is implemented in an embarrassingly parallel mode.
+We can take in all data at the same iteration and just compute the gradient in a MapReduce fashion.
+As for the \textit{cache()} operation and RDD design for data sparsity, it is the same with Algorithm PSUBPLR-SPARK.
 
 \subsection{Online Stochastic Gradient Descent in Mahout}
-Though SGD is an inherently sequential algorithm, it is blazingly fast and thus it is not a problem for Mahout's implementation to handle training sets of tens of millions of examples.
-With the down-sampling typical in many datasets, this is equivalent to a dataset with billions of raw training examples.
-The SGD system in Mahout is an online learning algorithm which means that you can learn models in an incremental fashion and that we can do performance testing as your system runs.
-This also means that we can stop training when a model reaches a target level of performance.
-The SGD framework includes classes to do online evaluation using cross validation (the \textit{CrossFoldLearner}) and an evolutionary system to do learning hyper-parameter optimization on the fly (the \textit{AdaptiveLogisticRegression}).
+Though SGD is an inherently sequential algorithm, it is blazingly fast. Thus Mahout's implementation can handle training sets of tens of millions of examples.
+The SGD system in Mahout is an online learning algorithm, implying that we can learn models in an incremental fashion and perform testing when the system runs.
+In addition, we can halt training when a model reaches a target level of performance.
+The SGD framework includes classes to do online evaluation using cross validation (the \textit{CrossFoldLearner}) and an evolutionary system to hyper-parameter optimization on the fly (the \textit{AdaptiveLogisticRegression}).
 The \textit{AdaptiveLogisticRegression} system makes heavy use of threads to increase machine utilization.
-The way it works is that it runs 20 \textit{CrossFoldLearners} in separate threads, each with slightly different learning parameters.
-As better settings are found, these new settings are propagating to the other learners.
+To do so, it runs 20 \textit{CrossFoldLearners} in separate threads, each with slightly different learning parameters.
+As better settings are found, these new settings propagate to the other learners.
 
-Because the SGD algorithms need to have fixed length feature vectors and because it is a pain to build a dictionary ahead of time, most SGD applications use the hashed feature vector encoding system that is rooted at \textit{FeatureVectorEncoder}.
+Because the SGD algorithms need feature vectors of fixed length and it is a pain to build a dictionary ahead of time, most SGD applications use the encoding system that is rooted at \textit{FeatureVectorEncoder} to derive hashed feature vectors.
 The basic idea is that you create a vector, typically a \textit{RandomAccessSparseVector}, and then you use various feature encoders to progressively add features to that vector.
@@
 There are specialized encoders for a variety of data types.
-You can normally encode either a string representation of the value you want to encode or you can encode a byte level representation to avoid string conversion.
-In the case of \textit{ContinuousValueEncoder} and \textit{ConstantValueEncoder}, it is also possible to encode a null value and pass the real value in as a weight.
+You can normally encode either a string representation of the value you want to encode or you can encode a byte representation to avoid string conversion.
+In the case of \textit{ContinuousValueEncoder} and \textit{ConstantValueEncoder}, it is also possible to encode a null value and pass the real value as a weight.
 
-In our implementation, we use \textit{RandomAccessSparseVector} for data sparsity and the function call by \textit{OnlineLogisticRegression} to train.
-We also do the cross validation part. However, to be synchronized with other methods, we write our own code to do cross validation.
+In our implementation, we use \textit{RandomAccessSparseVector} for data sparsity and the function call by \textit{OnlineLogisticRegression} to train the LR classifier.
+We also perform cross validation. However, to keep consistent with other methods, we write our own code to do cross validation.
 
@@
 \centering
-\caption{Datasets}\label{tab:table1}
-\begin{tabular}{|c|c|c|c|c|c|}
+\caption{Datasets}\label{tab:table1}\vspace{-0.3cm}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-    Name           & $n$ & $d$ & Density & Nonzeros & Balance \\
+    Name           & $n$ & $d$ & Density  & Balance \\
 \hline
-    2d             & 2             & 200            & 1.0                  & 400                 & 1.000 \\
+    2d             & 2             & 200            & 1.0                                & 1.000 \\
 \hline
-    20NewsGroup    & 16428         & 1988           & $7.384\times10^{-3}$ & 238511              & 1.006 \\
+    20NewsGroup    & 16428         & 1988           & $7.384\times10^{-3}$               & 1.006 \\
 \hline
-    Gisette        & 5000          & 7000           & 0.12998              & 4549319             & 1.000 \\
+    Gisette        & 5000          & 7000           & 0.12998                            & 1.000 \\
 \hline
-    ECUESpam       & 100249        & 10687          & $2.563\times10^{-3}$ & 2746159             & 5.882 \\
+    ECUESpam       & 100249        & 10687          & $2.563\times10^{-3}$               & 5.882 \\
 \hline
-    URL-Reputation & 3231961       & 2376130        & $3.608\times10^{-5}$ & 277058644           & 0.500 \\
+    URL-Reputation & 3231961       & 2376130        & $3.608\times10^{-5}$               & 0.500 \\
 \hline
@@
 The \textbf{Gisette} dataset is relatively larger, and data is less sparse. Thus it requires more computation theoretically.
-The \textbf{ECUESpam} dataset features for its inbalanced distribution between positive and negative data instances.
-It has a higher data dimensionality than textbf{Gisette} dataset.
+The \textbf{ECUESpam} dataset features for its imbalanced distribution between positive and negative data instances.
+It has a higher data dimensionality than \textbf{Gisette} dataset.
 However, because of data sparsity, it has fewer nonzero values involved in the computation.
@@
 \centering
-\caption{Cluster Information}\label{tab:table2}
+\caption{Cluster Information}\label{tab:table2}\vspace{-0.3cm}
 \begin{tabular}{|c|c|}
@@
 \section{Experimental Results} \label{sec:experiment}
-In this section, we conduct an empirical analysis of our algorithms.
+In this section, we conduct a thorough empirical analysis.
 
 \subsection{Results on Simulated 2d Dataset}
+%
 \begin{figure}[tb] \label{fig:02}
-\center \includegraphics[height=5cm,width=6cm]{img/2d-show.eps}
-\caption{Visual Result on Simulated \textbf{2d} Dataset}
+\center \includegraphics[height=4cm,width=5cm]{img/2d-show.eps}\vspace{-0.4cm}
+\caption{Visual Result on Simulated \textbf{2d} Dataset}\vspace{-0.5cm}
 \end{figure}
+%
 Fig.~\ref{fig:02} shows the visual result for Simulated \textbf{2d} Dataset.
@@
 \subsection{Results on Precision} \label{sec:precision}
+Accuracy of six test programs achieved on five datasets are shown in Table~\ref{tab:table3}.
+%
 \begin{table}[h]
 \centering
-\caption{Accuracy Results}\label{tab:table3}
-\begin{tabular}{|c|c|c|c|c|c|}
+\caption{Accuracy Results. The meaning of abbreviations are as follows: 20-N-G, 20 News Group; URL-R, URL-Reputation.}\label{tab:table3}\vspace{-0.3cm}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-           & 2d   & 20NewsGroup & Gisette & ECUESpam & URL-Reputation \\
+           & 20-N-G & Gisette & ECUESpam & URL-R \\
 \hline
-Mahout     & 93.5\% & 71.3\% & 91.5\% & 85.2\% & 91.5\% \\
+Mahout     & 71.3\% & 91.5\% & 85.2\% & 91.5\% \\
 \hline
-Liblinear  & 93.0\% & 92.0\% & 97.4\% & 97.1\% & \XSolid \\
+Liblinear  & 92.0\% & 97.4\% & 97.1\% & --- \\
 \hline
-SLLR       & 93.5\% & 91.5\% & 94.8\% & 92.3\% & 94.2\% \\
+SLLR       & 91.5\% & 94.8\% & 92.3\% & 94.2\% \\
 \hline
-PSUBPLR-MR & 93.5\% & 90.5\% & 94.6\% & 91.7\% & 93.8\% \\
+PSUBPLR-MR & 90.5\% & 94.6\% & 91.7\% & 93.8\% \\
 \hline
-PGDPLR-SPARK & 93.5\% & 92.0\% & 97.0\% & 93.7\% & 96.0\% \\
+PGDPLR-SPARK & 92.0\% & 97.0\% & 93.7\% & 96.0\% \\
 \hline
-PSUBPLR-SPARK & 93.5\% & 90.5\% & 95.8\% & 91.7\% & 94.0\% \\
+PSUBPLR-SPARK & 90.5\% & 95.8\% & 91.7\% & 94.0\% \\
 \hline
@@
 \end{table}
-Accuracy of six test programs achieved on five datasets are shown in Table~\ref{tab:table3}. These are averaged results of cross validation.
-From Fig.~\ref{fig:03} to Fig.~\ref{fig:07}, we show the test error as a function of iteration number on each dataset for all six test programs.
-Note that, Liblinear can not be fully implemented the \textbf{URL-Reputation} dataset on our machine due to memory limit.
+%
+These are averaged results of cross validation.
+In Figures~\ref{fig:accuracy} (a)-(d), we show the test error as a function of iteration number on each dataset for all six test programs.
+Note that, Liblinear can not be implemented with the full \textbf{URL-Reputation} dataset on our machine due to memory limit.
 This proves the scalability issue of Liblinear.
-
-\begin{figure}[tb] \label{fig:03}
-\center \includegraphics[height=4.5cm,width=5cm]{img/2d_accuracy_iteration.eps}
-\caption{Test error, as a function of iteration number on Simulated \textbf{2d} Dataset}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:04}
-\center \includegraphics[height=4.5cm,width=5cm]{img/20NewsGroup_accuracy_iteration.eps}
-\caption{Test error, as a function of iteration number on \textbf{20NewsGroup} Dataset}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:05}
-\center \includegraphics[height=4.5cm,width=5cm]{img/Gisette_accuracy_iteration.eps}
-\caption{Test error, as a function of iteration number on \textbf{Gisette} Dataset}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:06}
-\center \includegraphics[height=4.5cm,width=5cm]{img/ECUESpam_accuracy_iteration.eps}
-\caption{Test error, as a function of iteration number on \textbf{ECUESpam} Dataset}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:07}
-\center \includegraphics[height=4.5cm,width=5cm]{img/URL-Reputation_accuracy_iteration.eps}
-\caption{Test error, as a function of iteration number on \textbf{URL-Reputation} Dataset}
-\end{figure}
+In the tests, Liblinear can handle $33.3\%$ of the whole data volume at most, with a test accuracy of $96.2\%$ and running time of 519s.
+%
+\begin{figure*}[tb]
+\begin{center}
+\begin{tabular}{cccc}
+   %\includegraphics[height=4.5cm,width=5cm]{img/2d_accuracy_iteration.eps}&
+   \includegraphics[height=4.cm,width=4.5cm]{img/20NewsGroup_accuracy_iteration.eps}&
+   \hspace{-0.6cm}\includegraphics[height=4.cm,width=4.5cm]{img/Gisette_accuracy_iteration.eps}&
+   \hspace{-0.6cm}\includegraphics[height=4.cm,width=4.5cm]{img/ECUESpam_accuracy_iteration.eps}&
+   \hspace{-0.6cm}\includegraphics[height=4.cm,width=4.5cm]{img/URL-Reputation_accuracy_iteration.eps}\\
+   (a) \textbf{20NewsGroup}. & \hspace{-0.3cm}(b) \textbf{Gisette}. & \hspace{-0.3cm}(c) \textbf{ECUESpam}. & \hspace{-0.3cm}(d) \textbf{URL-Reputation}.\\
+   \end{tabular}
+\end{center}\vspace{-0.4cm}
+   \caption{Test error, as a function of iteration number.}\vspace{-0.5cm}
+\label{fig:accuracy}
+\end{figure*}
 
 \subsection{Results on Running Time} \label{sec:time}
+
+Running Time of six test programs used on five datasets are shown in Table~\ref{tab:table4}.
+These are averaged results corresponding to the accuracy we achieved in Table~\ref{tab:table3}.
+%
 \begin{table}[h]
 \centering
-\caption{Running Time Results}\label{tab:table4}
+\caption{Running Time Results. The meaning of abbreviations are as follows: 20-N-G, 20 News Group; URL-R, URL-Reputation.}\label{tab:table4}\vspace{-0.3cm}
 \begin{tabular}{|c|c|c|c|c|c|}
 \hline
-           & 2d   & 20NewsGroup & Gisette & ECUESpam & URL-Reputation \\
+           & 20-N-G & Gisette & ECUESpam & URL-R \\
 \hline
-Mahout     & 0.595s & 9.827s & 131.807s & 96.611s & 10100.209s \\
+Mahout     & 9.83s & 131.8s & 96s & 10100s \\
 \hline
-Liblinear  & 0.078s & 0.793s & 2.364s & 13.161s & \XSolid \\
+Liblinear  & 0.79s & 2.4s & 13s & --- \\
 \hline
-SLLR       & 1.761s & 20.046s & 130.451s & 1028.185s & 3248.473s \\
+SLLR       & 20.05s & 130.5s & 1028s & 3248s \\
 \hline
-PSUBPLR-MR & 120.186s & 1360.854s & 3687.941s & 11478.706s & 16098.260s \\
+PSUBPLR-MR & 1360.85s & 3687.9s & 11478s & 16098s \\
 \hline
-PGDPLR-SPARK & 0.681s & 10.517s & 99.156s & 924.020s & 3615.780s \\
+PGDPLR-SPARK & 10.52s & 99.2s & 924s & 3615s \\
 \hline
-PSUBPLR-SPARK & 1.325s & 8.571s & 89.094s & 796.802s & 2918.470s \\
+PSUBPLR-SPARK & 8.57s & 89.1s & 796s & 2918s \\
 \hline
@@
 \end{table}
-Running Time of six test programs used on five datasets are shown in Table~\ref{tab:table4}.
-These are averaged results corresponding to the accuracy we achieved in Table~\ref{tab:table3}.
 
+In another way, we show the running time results in Fig.~\ref{fig:08} for comparison.
 \begin{figure}[tb] \label{fig:08}
-\center \includegraphics[height=4.5cm,width=9cm]{img/all_time.eps}
-\caption{All running times}
+\center \includegraphics[height=4.5cm,width=9cm]{img/all_time.eps}\vspace{-0.4cm}
+\caption{All running times}\vspace{-0.5cm}
 \end{figure}
-In another way, we show the running time results in Fig.~\ref{fig:08} for comparison.
 
@@
 We can come up with following conclusions.
-\begin{enumerate}
-    \item Liblinear always performs the best. It fully utilizes memory and single machine implementation does not require any communication between machines, which causes overhead.
+
+1) Liblinear always performs the best. It fully utilizes memory and single machine implementation does not require any communication between machines, which causes overhead.
           However, its scalability is limited by the memory size of the single machine that it runs on. This prevents its use in massive datasets.
           Nevertheless, if the dataset can be fully loaded into a single machine's memory, this efficient and direct sequential way of implementation is still recommended.
-    \item Mahout's precision is not good, especially for those datasets in which positive and negative instances are not balanced.
+
+2) Mahout's precision is not good, especially for those datasets in which positive and negative instances are not balanced.
           However, it is a representative of sequential algorithm that can train massive data in acceptable time.
@@
           Thus, it provides good scalability guarantee. If you are in the situation of single machine and limited memory, sequential online training like Mahout is recommended.
-    \item The precision of all sublinear methods is acceptable. The developed parallel sublinear algorithm only has a small drop in precision.
-    \item Hadoop system has a great drawback for running LR optimization methods. Its cluster programming model is based on acyclic data flow from stable storage to stable storage.
+
+3) The precision of all sublinear methods is acceptable. The developed parallel sublinear algorithm only has a small drop in precision.
+
+4) Hadoop system has a great drawback for running LR optimization methods. Its cluster programming model is based on acyclic data flow from stable storage to stable storage.
           Though it has the benefits of deciding where to run tasks and can automatically recover from failures in runtime, acyclic data flow is inefficient for iterative algorithms.
@@
           We also identify the running of "Primal-Map" dominates the whole iteration time (more than 66\%). It is the same situation for PSUBPLR-SPARK.
-    \item Spark employs the "all-in-memory" strategy, and it constructs RDD on demand. We implement PGDPLR-SPARK and PSUBPLR-SPARK in normal file system instead of HDFS.
+
+5) Spark employs the ``all-in-memory" strategy, and it constructs RDD on demand. We implement PGDPLR-SPARK and PSUBPLR-SPARK in normal file system instead of HDFS.
           Current results on Spark show that it is much more efficient than Hadoop, and performs better than Mahout.
           In the parallel situation, and have massive data to process, we recommend using Spark, and can choose PSUBPLR-SPARK for less time in exchange for a little bit precision loss.
-          As the system is premature and still under developing process, we expect our running time results for PGDPLR-SPARK and PSUBPLR-SPARK can still be improved.
+          As the platform is premature and still under developing process, we expect our running time results for PGDPLR-SPARK and PSUBPLR-SPARK can still be improved.
           For example, Spark currently only supports for one reducer, thus it does not use full CPU power when doing reduce jobs.
-    \item Another interesting point we would like to raise is about dataset. If we compare \textbf{ECUESpam} dataset and \textbf{GISETTE} dataset.
+
+6) Another interesting point we would like to raise is about dataset. If we compare \textbf{ECUESpam} dataset and \textbf{GISETTE} dataset.
           The former has has higher data dimensionality but more sparse.
@@
           To sum up, to get a general sense of running time for individual dataset, we have to consider both data volume and sparsity.
-\end{enumerate}
 
 \subsection{Results on Changing Cluster}
-From Fig.~\ref{fig:09} to Fig.~\ref{fig:13}, we show the running time as a function of used node number on each dataset for all three parallel test programs.
-\begin{figure}[tb] \label{fig:09}
-\center \includegraphics[height=4.5cm,width=5cm]{img/2d_time.eps}
-\caption{Running time, as a function of used node number on Simulated \textbf{2d} Dataset}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:10}
-\center \includegraphics[height=4.5cm,width=5cm]{img/20NewsGroup_time.eps}
-\caption{Running time, as a function of used node number on \textbf{20NewsGroup} Dataset}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:11}
-\center \includegraphics[height=4.5cm,width=5cm]{img/Gisette_time.eps}
-\caption{Running time, as a function of used node number on \textbf{Gisette} Dataset}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:12}
-\center \includegraphics[height=4.5cm,width=5cm]{img/ECUESpam_time.eps}
-\caption{Running time, as a function of used node number on \textbf{ECUESpam} Dataset}
-\end{figure}
-
-\begin{figure}[tb] \label{fig:13}
-\center \includegraphics[height=4.5cm,width=5cm]{img/URL-Reputation_time.eps}
-\caption{Running time, as a function of used node number on \textbf{URL-Reputation} Dataset}
-\end{figure}
+In Figures~\ref{fig:time} (a)-(d), we show the running time as a function of used node number on each dataset for all three parallel test programs.
+%
+\begin{figure*}[tb]
+\begin{center}
+\begin{tabular}{cccc}
+   %\includegraphics[height=4.5cm,width=5cm]{img/2d_time.eps}&
+   \includegraphics[height=4.cm,width=4.5cm]{img/20NewsGroup_time.eps}&
+   \hspace{-0.6cm}\includegraphics[height=4.cm,width=4.5cm]{img/Gisette_time.eps}&
+   \hspace{-0.6cm}\includegraphics[height=4.cm,width=4.5cm]{img/ECUESpam_time.eps}&
+   \hspace{-0.6cm}\includegraphics[height=4.cm,width=4.5cm]{img/URL-Reputation_time.eps}\\
+   (a) \textbf{20NewsGroup}. & \hspace{-0.3cm}(b) \textbf{Gisette}. & \hspace{-0.3cm}(c) \textbf{ECUESpam}. & \hspace{-0.3cm}(d) \textbf{URL-Reputation}.\\
+   \end{tabular}
+\end{center}\vspace{-0.4cm}
+   \caption{Running time, as a function of used node number.}\vspace{-0.5cm}
+\label{fig:time}
+\end{figure*}
+%
 
@@
 \centering
-\caption{Fault Tolerance Analysis}\label{tab:table5}
+\caption{Fault Tolerance Analysis}\label{tab:table5}\vspace{-0.3cm}
 \begin{tabular}{|c|c|c|}
@@
            & System Level & Algorithm Level \\
-\hline
-Mahout     & \XSolid & \XSolid  \\
-\hline
-Liblinear  & \XSolid & \XSolid \\
-\hline
-SLLR  & \XSolid & \Checkmark \\
 \hline
@@
 \end{table}
-Here, randomization is employed in all sublinear methods, thus provides algorithm level fault tolerance for SLLR, PSUBPLR-MR and PSUBPLR-SPARK.
-Hadoop and Spark can both provide fault tolerance, but in different ways. Hadoop employs HDFS while Spark has RDDs.
+Here, randomization is employed in all sublinear methods, thus provides algorithm level fault tolerance for PSUBPLR-MR and PSUBPLR-SPARK.
+Hadoop and Spark can both provide system level fault tolerance, but in different ways. Hadoop employs HDFS while Spark has RDDs.
 Of all six test programs, PSUBPLR-MR and PSUBPLR-SPARK are fault tolerant in both system level and algorithm level.
@@
 \begin{figure}[tb] \label{fig:14}
-\center \includegraphics[height=4.5cm,width=9cm]{img/fault_tolerance.eps}
-\caption{Iteration time, as a function of percentage of failed maps, on \textbf{URL-Reputation} Dataset, run on 6 nodes}
+\center \includegraphics[height=4.5cm,width=9cm]{img/fault_tolerance.eps}\vspace{-0.4cm}
+\caption{Iteration time, as a function of percentage of failed maps, on \textbf{URL-Reputation} Dataset, run on 6 nodes}\vspace{-0.5cm}
 \end{figure}
@@
 In this paper we analyzed three optimization approaches along with three computing platforms to train LR model with large-volume, high-dimensional dataset for classification.
-We focus on both algorithm design and choosing of computing platforms.
-We tested correctness, learning accuracy, running time, scalability and fault tolerance of different programs.
-These tests are objective, as the carefully chosen datasets range from KB to GB in size.
-We also consider the sparsity issues in all real world datasets.
 Test results show that different algorithms and different computing platforms have their own advantages.
-We should choose wisely of the combination of algorithm and computing platform according to dataset situations and machine resources.
-A minor contribution in this paper is to present a novel parallel sublinear algorithm for LR implemented on both Hadoop and Spark.
+We can intelligently choose between them according our needs and resources.
+Another contribution of this paper is to present a novel parallel sublinear algorithm for LR implemented on both Hadoop and Spark.
 We realize this paper has its limitation in both machine resources and datasets.

### 2013-06-23 draft.tex
version for proofread

@@
 It is a supervised learning model for pattern classification and enjoys the benefits of statistical principles.
-This paper addresses the issue of computational efficiency for solving LR in big data scenario.
-We compare between different computing platforms and different parallel algorithms.
-Our goal is to offer valuable suggestions on choosing computing platforms and learning algorithms according to different application situations for specific datasets and machine resources.
+This paper addresses the issue of computational efficiency for solving LR in the big data scenario.
+We compare the performance between different computing platforms and different parallel algorithms.
+Our goal is to provide valuable suggestions on choosing computing platforms and learning algorithms according to different application situations for specific datasets and machine resources.
 Three different parallel computing platforms along with three different types of parallel algorithms are carefully studied in this paper.
-In such process, we present a novel parallel sublinear method based on its sequential version as another contribution.
+In addition, we present a novel parallel sublinear method to optimize the solution of LR.
 %Hadoop, Mahout and Spark are three existing parallel computing platforms that can be implemented with large scale machine learning algorithms.
 %Parallel gradient Descent and stochastic gradient descent are two state-of-art algorithms for solving LR.
-To enhance practicality, we consider tradeoff between efficiency and precision.
-We also provide fault tolerance for parallel distributed computations.
+To enhance capability, we consider the tradeoff between efficiency and accuracy. Extensive experimental results verify the effective performance of proposed algorithms.
 \end{abstract}
@@
 \begin{figure}[tb]
-\center \includegraphics[height=3.0cm,width=6.5cm]{img/framework.png}\vspace{-0.4cm}
+\center \includegraphics[height=3.0cm,width=6.5cm]{img/framework.png}\vspace{-0.3cm}
 \caption{Parallel implementation flow chart for PSUBPLR-MR}\label{fig:frame}\vspace{-0.5cm}
@@
 
-\section{Experiments Setup} \label{sec:setup}
-In this section, we explains details of the datasets information, cluster information, and the test programs of our experiments.
+\section{Experimental Setup} \label{sec:setup}
+In this section, we present the details of the dataset information, cluster information, and the test programs of our experiments.
 
-\subsection{Datasets Information}
-We choose five open datasets to run all six test programs:	
-The	Simulated \textbf{2d} dataset has 2 features and 200 instances.
-The	\textbf{20NewsGroup} dataset has 16428 features and 1988 instances. We split it into a training set of 1800 instances and a test set of 188 instances.	
-The	third test dataset is the \textbf{Gisette}~\cite{guyon2004result} dataset, which has 5000 features and 7000 instances.
-We split it into a training set of 6000 instances and a test set of 1000 instances.
-The	fourth test dataset is the \textbf{ECUESpam}~\cite{DelanyKBS05} dataset, which has 100249 features and 10678 instances (after proper preprocessing).
-We split it into a training set of 9000 instances and a test set of 1687 instances.
-Finally, we have the \textbf{URL-Reputation}~\cite{ma2009identifying} dataset, which has 3231961 features and 2376130 instances.
-We split it into a training set of 2356130 instances and a test set of 20000 instances.
-Apart from the Simulated \textbf{2d} dataset, other four datasets are all sparse. Details are shown in Table~\ref{tab:table1}.
+\subsection{Dataset Information}
+We choose five open datasets to run all six test programs. Details are shown in Table~\ref{tab:table1}.	
+Different from the simulated \textbf{2d} dataset, the other four datasets are all sparse.
+We split each dataset into the training set and the testing set.
 We randomly repeat such split 20 times and our analysis is based on the average performance of 20 repetitions.
-
 In Table~\ref{tab:table1}, \textit{Density} is computed as
 \[
-Density(Dataset)~=~\frac{\#~of~Nonzeros}{Total~\#~of~entries},
+Density(Dataset)~=~\frac{\#~of~Nonzeros}{\#~of~all~entries},
 \]
-which is adopted from~\cite{sarwar2001item}.
+which stems from~\cite{sarwar2001item}.
 \textit{Balance} describes the binary distribution of labels.
@@
 \]
-\begin{table}[h]
+\begin{table*}%[h]
 \centering
 \caption{Datasets}\label{tab:table1}\vspace{-0.3cm}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|c|c|c|}
 \hline
-    Name           & $n$ & $d$ & Density  & Balance \\
+    Name           & Dimension & \# of instances & Density  & \# of nonzero values & Balance & \# of training & \# of testing\\
 \hline
-    2d             & 2             & 200            & 1.0                                & 1.000 \\
+    2d             & 2             & 200            & 1.0                      & 400          & 1.000 & --- & --- \\
 \hline
-    20NewsGroup    & 16428         & 1988           & $7.384\times10^{-3}$               & 1.006 \\
+    20NewsGroup    & 16428         & 1988           & $7.384\times10^{-3}$     & 238511          & 1.006 & 1800 & 188\\
 \hline
-    Gisette        & 5000          & 7000           & 0.12998                            & 1.000 \\
+    Gisette        & 5000          & 7000           & 0.12998                  & 4549319          & 1.000 & 6000 & 1000\\
 \hline
-    ECUESpam       & 100249        & 10687          & $2.563\times10^{-3}$               & 5.882 \\
+    ECUESpam       & 100249        & 10687          & $2.563\times10^{-3}$     & 2746159          & 5.882 & 9000 & 1687\\
 \hline
-    URL-Reputation & 3231961       & 2376130        & $3.608\times10^{-5}$               & 0.500 \\
+    URL-Reputation & 3231961       & 2376130        & $3.608\times10^{-5}$     & 277058644          & 0.500 & 2356130 & 20000\\
 \hline
-\end{tabular}
-\end{table}
-We carefully select these five datasets.
-The Simulated \textbf{2d} dataset can be viewed for visual result and serves for initial test of correctness of implementation.
+\end{tabular}\vspace{-0.3cm}
+\end{table*}
+These five datasets are carefully selected.
+The simulated \textbf{2d} dataset can be viewed as visual result and serves for the initial test of correctness of classifiers.
 The \textbf{20NewsGroup} dataset is best-known for the test of LR model, which has a balanced distribution between positive and negative data instances.
-The \textbf{Gisette} dataset is relatively larger, and data is less sparse. Thus it requires more computation theoretically.
-The \textbf{ECUESpam} dataset features for its imbalanced distribution between positive and negative data instances.
-It has a higher data dimensionality than \textbf{Gisette} dataset.
+The \textbf{Gisette} dataset~\cite{guyon2004result} is relatively larger, and feature vectors are less sparse. Thus it requires more computation theoretically.
+The \textbf{ECUESpam} dataset~\cite{DelanyKBS05} is selected due to its imbalanced distribution between positive and negative data instances.
+It has a higher data dimensionality than the \textbf{Gisette} dataset.
 However, because of data sparsity, it has fewer nonzero values involved in the computation.
-Finally, the \textbf{URL-Reputation} dataset contains millions of data instances and features.
-The raw data is stored in the svmlight format, which has the size of more than 2GB.
-It achieves the current level for massive dataset, and exceed the scalability of Liblinear, which will be shown below.
+Finally, the \textbf{URL-Reputation} dataset~\cite{ma2009identifying} contains millions of data instances and features.
+The raw data are stored in the svmlight format, which has the volume of more than 2GB.
+It can be seen as a representative of massive datasets in the sense that it exceeds the scalability of Liblinear, which will be shown below.
 
 \subsection{Cluster Information}
-The cluster that we implement on has the following configurations shown in Table~\ref{tab:table2}.
+The cluster that we implement on has the configurations shown in Table~\ref{tab:table2}.
 \begin{table}[h]
@@
 Online stochastic gradient descent method is run on Mahout in a sequential mode.
-Liblinear~\cite{fan2008liblinear} is the baseline test program we choose. It is sequential and it outperforms many other programs for LR on a single machine.
-SLLR performs sequential sublinear algorithm on a single machine.
-PSUBPLR-MR performs parallel sublinear algorithm on Hadoop on cluster.
-PGDPLR-SPARK is the test program for parallel gradient descent run on Spark.
-PSUBPLR-SPARK implements parallel sublinear algorithm run on Spark.
+Liblinear~\cite{fan2008liblinear} is the baseline test program we choose. It is sequential and outperforms many other programs for LR on a single machine.
+SLLR performs the sequential sublinear algorithm on a single machine.
+PSUBPLR-MR performs the parallel sublinear algorithm on Hadoop on cluster.
+PGDPLR-SPARK is the test program for the parallel gradient descent run on Spark.
+PSUBPLR-SPARK implements the parallel sublinear algorithm run on Spark.
 
 \section{Experimental Results} \label{sec:experiment}
-In this section, we conduct a thorough empirical analysis.
+In this section, we conduct the empirical analysis.
 
@@
 %
-\begin{figure}[tb] \label{fig:02}
-\center \includegraphics[height=4cm,width=5cm]{img/2d-show.eps}\vspace{-0.4cm}
-\caption{Visual Result on Simulated \textbf{2d} Dataset}\vspace{-0.5cm}
+\begin{figure}[tb]
+\center \includegraphics[height=4cm,width=5.14cm]{img/2d-show.eps}\vspace{-0.3cm}
+\caption{Visual result on simulated \textbf{2d} dataset}\label{fig:02}\vspace{-0.5cm}
 \end{figure}
 %
-Fig.~\ref{fig:02} shows the visual result for Simulated \textbf{2d} Dataset.
+Fig.~\ref{fig:02} shows the visual result for the simulated \textbf{2d} dataset.
 Here we use all data for training and testing, thus "Test Error" here can be interpreted as "Training Error".
-The blue line represents the learned separation vector of Mahout.
-The black line indicates the result for Liblinear.
 The green line shows the result for all sublinear methods, including SLLR, PSUBPLR-MR and PSUBPLR-SPARK.
-The red line is the result for PGDPLR-SPARK.
-The results on the Simulated \textbf{2d} Dataset proves the correctness of all test programs.
+The results on the simulated \textbf{2d} dataset proves the correctness of all test programs.
 
 \subsection{Results on Precision} \label{sec:precision}
-Accuracy of six test programs achieved on five datasets are shown in Table~\ref{tab:table3}.
+The results of six test programs achieved on five datasets are shown in Table~\ref{tab:table3}.
 %
@@
 \centering
-\caption{Accuracy Results. The meaning of abbreviations are as follows: 20-N-G, 20 News Group; URL-R, URL-Reputation.}\label{tab:table3}\vspace{-0.3cm}
+\caption{Accuracy Results. The meanings of abbreviations are as follows: 20-N-G, 20 News Group; URL-R, URL-Reputation.}\label{tab:table3}\vspace{-0.3cm}
 \begin{tabular}{|c|c|c|c|c|}
@@
 %
-These are averaged results of cross validation.
+These are the averaged results of cross validation.
 In Figures~\ref{fig:accuracy} (a)-(d), we show the test error as a function of iteration number on each dataset for all six test programs.
-Note that, Liblinear can not be implemented with the full \textbf{URL-Reputation} dataset on our machine due to memory limit.
+Note that Liblinear cannot be implemented with the full \textbf{URL-Reputation} dataset on our machine due to memory limit.
 This proves the scalability issue of Liblinear.
-In the tests, Liblinear can handle $33.3\%$ of the whole data volume at most, with a test accuracy of $96.2\%$ and running time of 519s.
+In the tests, Liblinear can handle $33.3\%$ of the whole data volume at most, with the test accuracy of $96.2\%$ and the running time of 519s.
 %
@@
    \end{tabular}
-\end{center}\vspace{-0.4cm}
+\end{center}\vspace{-0.3cm}
    \caption{Test error, as a function of iteration number.}\vspace{-0.5cm}
@@
 
-Running Time of six test programs used on five datasets are shown in Table~\ref{tab:table4}.
-These are averaged results corresponding to the accuracy we achieved in Table~\ref{tab:table3}.
+The running time of six test programs used on five datasets is shown in Table~\ref{tab:table4}.
+These are the averaged results corresponding to the accuracies we achieved in Table~\ref{tab:table3}.
 %
@@
 \centering
-\caption{Running Time Results. The meaning of abbreviations are as follows: 20-N-G, 20 News Group; URL-R, URL-Reputation.}\label{tab:table4}\vspace{-0.3cm}
+\caption{Running Time. The meanings of abbreviations are as follows: 20-N-G, 20 News Group; URL-R, URL-Reputation.}\label{tab:table4}\vspace{-0.3cm}
 \begin{tabular}{|c|c|c|c|c|c|}
@@
 In another way, we show the running time results in Fig.~\ref{fig:08} for comparison.
-\begin{figure}[tb] \label{fig:08}
-\center \includegraphics[height=4.5cm,width=9cm]{img/all_time.eps}\vspace{-0.4cm}
-\caption{All running times}\vspace{-0.5cm}
+\begin{figure}[tb]
+\center \includegraphics[height=4.5cm,width=9cm]{img/all_time.eps}\vspace{-0.3cm}
+\caption{Running time.}\label{fig:08}\vspace{-0.5cm}
 \end{figure}
 
-From the accuracy results in section~\ref{sec:precision} and running time results in section~\ref{sec:time}.
+From the accuracy results in Section~\ref{sec:precision} and the running time results in Section~\ref{sec:time}.
 We can come up with following conclusions.
 
-1) Liblinear always performs the best. It fully utilizes memory and single machine implementation does not require any communication between machines, which causes overhead.
-          However, its scalability is limited by the memory size of the single machine that it runs on. This prevents its use in massive datasets.
-          Nevertheless, if the dataset can be fully loaded into a single machine's memory, this efficient and direct sequential way of implementation is still recommended.
+1) Liblinear performs best. It fully utilizes memory and the single machine implementation does not require any communication between machines.
+          However, its scalability is limited by the memory size of the single machine that it runs on, which prevents its use for massive datasets.
+          Nevertheless, if the dataset can be fully loaded into the memory of a single machine, this efficient and direct sequential way of implementation is still recommended.
 
-2) Mahout's precision is not good, especially for those datasets in which positive and negative instances are not balanced.
-          However, it is a representative of sequential algorithm that can train massive data in acceptable time.
+2) Mahout's precision is not good, especially for those datasets in which positive and negative instances are imbalanced.
+          However, it is a representative example of sequential algorithm that can train massive data in acceptable time.
           When we monitor its memory when running, it is much lower than Liblinear. This is the advantage brought by both online algorithm and hashing operations on features.
-          Thus, it provides good scalability guarantee. If you are in the situation of single machine and limited memory, sequential online training like Mahout is recommended.
+          Therefore, it provides good scalability guarantee. If you are in the situation of single machine and limited memory, sequential online training like Mahout is recommended.
 
@@
 
-4) Hadoop system has a great drawback for running LR optimization methods. Its cluster programming model is based on acyclic data flow from stable storage to stable storage.
+4) Hadoop system has a drawback for running LR optimization methods. Its cluster programming model is based on acyclic data flow from stable storage to stable storage.
           Though it has the benefits of deciding where to run tasks and can automatically recover from failures in runtime, acyclic data flow is inefficient for iterative algorithms.
-          All six test programs contains a number of iterations, thus making PSUBPLR-MR performs poorly, even worse than sequential algorithms.
-          When we study the details of Hadoop implementation, we find the MapReduce job starting time in PSUBPLR-MR is about 20s. It consists of task configuration time and parameter passing time.
+          All six test programs contain a number of iterations, thus making PSUBPLR-MR performs poorly, even worse than sequential algorithms.
+          When we study the details of Hadoop implementation, we find that the MapReduce job starting time in PSUBPLR-MR is about 20s.
+It consists of task configuration time and parameter passing time.
           This running time overhead is not negligible, especially when dataset is relatively small.
-          We also identify the running of "Primal-Map" dominates the whole iteration time (more than 66\%). It is the same situation for PSUBPLR-SPARK.
+          We also identify that the running of "Primal-Map" dominates the whole iteration time (more than 66\%). It is the same situation for PSUBPLR-SPARK.
 
@@
           Current results on Spark show that it is much more efficient than Hadoop, and performs better than Mahout.
-          In the parallel situation, and have massive data to process, we recommend using Spark, and can choose PSUBPLR-SPARK for less time in exchange for a little bit precision loss.
-          As the platform is premature and still under developing process, we expect our running time results for PGDPLR-SPARK and PSUBPLR-SPARK can still be improved.
-          For example, Spark currently only supports for one reducer, thus it does not use full CPU power when doing reduce jobs.
+          In the parallel situation, we recommend Spark to process massive data. Further, we recommend to choose PSUBPLR-SPARK for less running time in exchange for a little bit precision loss.
+          As the platform is still under developing process, we expect that our running time results for PGDPLR-SPARK and PSUBPLR-SPARK can still be improved.
+          For example, Spark currently only supports for one reducer, thus it does not use full CPU power when performing reduce.
 
 6) Another interesting point we would like to raise is about dataset. If we compare \textbf{ECUESpam} dataset and \textbf{GISETTE} dataset.
-          The former has has higher data dimensionality but more sparse.
-          We can find that algorithms on \textbf{ECUESpam} dataset enjoy less running time per iteration as the dataset has fewer nonzero values involved in the computation.
-          However, algorithms on \textbf{ECUESpam} dataset need more iteration number, which is related to its higher data dimensionality. This even causes more running time in total.
-          To sum up, to get a general sense of running time for individual dataset, we have to consider both data volume and sparsity.
+          The former has higher data dimensionality but more sparse.
+          We can find that algorithms on \textbf{ECUESpam} dataset enjoy less running time per iteration than on \textbf{GISETTE} dataset as \textbf{ECUESpam} has fewer nonzero values involved in the computation.
+          However, algorithms on \textbf{ECUESpam} dataset need more iterations than on \textbf{GISETTE} dataset, which is related to higher data dimensionality of \textbf{ECUESpam} dataset.
+This even causes more running time in total.
+          To sum up, to get a general sense of running time for individual dataset, we need to consider both data volume and sparsity.
 
@@
    \end{tabular}
-\end{center}\vspace{-0.4cm}
+\end{center}\vspace{-0.3cm}
    \caption{Running time, as a function of used node number.}\vspace{-0.5cm}
@@
 %
-
 As we can see from the results, fewer computation resources provided, longer the implementation process will take.
-However, this trend is not in a consistent fashion. When number of machines gets higher, the less impact it will make.
-We may reach a point for every algorithm when running time stops decreasing as machine number increases.
+However, this trend is not in a consistent fashion. When the number of machines gets higher, it will make the less impact.
+We may reach a point for every algorithm when running time halts to decrease as machine number increases.
 This shows the true scalability of the designed algorithm, which we can study in our future work.
@@
 \end{table}
-Here, randomization is employed in all sublinear methods, thus provides algorithm level fault tolerance for PSUBPLR-MR and PSUBPLR-SPARK.
+Here, randomization is employed in all sublinear methods, thus providing algorithm level fault tolerance for PSUBPLR-MR and PSUBPLR-SPARK.
 Hadoop and Spark can both provide system level fault tolerance, but in different ways. Hadoop employs HDFS while Spark has RDDs.
-Of all six test programs, PSUBPLR-MR and PSUBPLR-SPARK are fault tolerant in both system level and algorithm level.
+Of all six test programs, PSUBPLR-MR and PSUBPLR-SPARK are fault-tolerant in both system level and algorithm level.
 
@@
 This is tested on 6 nodes.
-\begin{figure}[tb] \label{fig:14}
-\center \includegraphics[height=4.5cm,width=9cm]{img/fault_tolerance.eps}\vspace{-0.4cm}
-\caption{Iteration time, as a function of percentage of failed maps, on \textbf{URL-Reputation} Dataset, run on 6 nodes}\vspace{-0.5cm}
+\begin{figure}[tb]
+\center \includegraphics[height=4.5cm,width=9cm]{img/fault_tolerance.eps}\vspace{-0.3cm}
+\caption{Iteration time, as a function of percentage of failed maps, on \textbf{URL-Reputation} Dataset, run on 6 nodes}\label{fig:14}\vspace{-0.5cm}
 \end{figure}
-As the outcome shows, PSUBPLR-MR suffers no running time increase per iteration when maps failed. But it takes the cost of precision loss if we enforce no additional iterations are implemented.
-PGDPLR-SPARK and PSUBPLR-SPARK will increase iteration time right after the maps failed. It is due to RDD reconstruction. The increase is not significant.
-This difference also proves the different mechanism of fault tolerance between Hadoop and Spark.
+As Fig.~\ref{fig:14} shows, iteration time of PSUBPLR-MR remains unaffected when maps fail. But it takes the cost of precision loss if we enforce that no additional iterations are implemented.
+PGDPLR-SPARK and PSUBPLR-SPARK will increase iteration time when the maps fail. It is due to RDD reconstruction. The increase is not significant.
+This difference also reveals the different mechanism of fault tolerance between Hadoop and Spark.
 
 \section{Conclusion} \label{sec:concl}
-In this paper we analyzed three optimization approaches along with three computing platforms to train LR model with large-volume, high-dimensional dataset for classification.
-Test results show that different algorithms and different computing platforms have their own advantages.
-We can intelligently choose between them according our needs and resources.
-Another contribution of this paper is to present a novel parallel sublinear algorithm for LR implemented on both Hadoop and Spark.
-We realize this paper has its limitation in both machine resources and datasets.
-It is exactly we are heading for: More machines and larger datasets will bring more convincing results.
-We also plan to employ the research angle of combining algorithm design and computing platform to study other machine learning models, thus giving more valuable suggestions in practical applications.
+In this paper we analyzed three optimization approaches along with three computing platforms to train LR model on large-scale, high-dimensional datasets for classification.
+In addition, we presented a novel parallel sublinear algorithm for LR implemented on both Hadoop and Spark.
+Based on extensive experiments, we summarized key features of each algorithm implemented on different computing platforms.
+Our future work will focus on combining algorithm design and computing platforms to optimize classifiers in machine learning.
 

### 2013-06-24 draft.tex
version after proofread

@@
 Logistic regression (LR) model has various applications in machine learning.
-It is a supervised learning model for pattern classification and enjoys the benefits of statistical principles.
+LR is a supervised learning model for pattern classification and enjoys the benefits of statistical principles.
 This paper addresses the issue of computational efficiency for solving LR in the big data scenario.
@@
 
-In recent years, many modern datasets are increasingly larger and larger.
-A most identifiable characteristic of these datasets is that data scale is very large and data dimensionality is very high.
+In recent years, many modern datasets grow drastically in both data volume and data dimensionality.
 Large data volume and high data dimensionality bring unavoidable computational challenges to machine learning problems.
@@
 They generally include millions of records over millions of attributes.
-More evidently, for the task of text categorization, we usually have to handle datasets with data volumes in billion scales and each data instance is characterized by thousands of feature dimensions~\cite{lewis2004rcv1}.
+More evidently, for the task of text and multimedia categorization, we usually have to handle datasets with data volumes in billion scales and each data instance is characterized by thousands of feature dimensions~\cite{chang2011foundations}.
 We tackle these challenges on both algorithm level and computing platform level via parallelization methods.
@@
 It can then increase the number of parallel computational nodes to several hundreds.
-Later, the work of Parallel Latent Dirichlet Allocation (PLDA)~\cite{wang2009plda} improves the computational efficiency of the LDA model by means of sampling methods.
+Later, the work of Parallel Latent Dirichlet Allocation (PLDA)~\cite{wang2009plda}~\cite{newman2007distributed} improves the computational efficiency of the LDA model by means of sampling methods.
 The parallel algorithm in Hadoop is robust, for it has fault tolerance of machine failures, thus taking advantage of Hadoop features.
@@
 \subsection{Computing Platforms}\label{sec:platform}
+In this paper, we specifically compares parallelization efforts of LR in two dimensions: platform and algorithm.
+
 Three computing platforms that we are working on have their own advantages to implement machine learning algorithms.
@@
 Transformations include functions like \textit{map}, \textit{filter} and \textit{join}. They normally build new RDDs from other RDDs, which comply with the lineage rule.
-In the table, we use "NFS" to represent "Normal File System" and "Fault Tolerance" here is specifically for node failure situations.
+In the table, we use ``NFS" to represent ``Normal File System" and "Fault Tolerance" here is specifically for node failure situations.
 \begin{table}[h]
@@
 Cotter \etal~\cite{cotter2012kernelized} extended the method to kernelized SVM.
-In~\cite{hazan2011optimal}, Hazan \etal applied the sublinear approximation approach to solve linear regression with penalties.
+%In~\cite{hazan2011optimal}, Hazan \etal applied the sublinear approximation approach to solve linear regression with penalties.
 Garber and Hazan~\cite{garberapproximating} also developed it in Semi-Definite Programming (SDP).
@@
 \section{Experimental Setup} \label{sec:setup}
-In this section, we present the details of the dataset information, cluster information, and the test programs of our experiments.
+This section presents the details of the dataset information, cluster information, and the test programs of our experiments.
 
@@
 \section{Experimental Results} \label{sec:experiment}
-In this section, we conduct the empirical analysis.
+In this section, we conduct empirical analysis on experimental results.
+We show three things: 1) correctness of our test program, 2) accuracy comparison, and 3) speedup comparison.
 
@@
 \hline
-Liblinear  & 92.0\% & 97.4\% & 97.1\% & --- \\
+Liblinear  & \textbf{92.0\%} & \textbf{97.4\%} & \textbf{97.1\%} & --- \\
 \hline
@@
 \hline
-PSUBPLR-MR & 90.5\% & 94.6\% & 91.7\% & 93.8\% \\
+PSUBPLR-MR & 90.5\% & 94.6\ & 91.7\% & 93.8\% \\
 \hline
-PGDPLR-SPARK & 92.0\% & 97.0\% & 93.7\% & 96.0\% \\
+PGDPLR-SPARK & \textbf{92.0\%} & 97.0\% & 93.7\% & \textbf{96.0\%} \\
 \hline
@@
 \hline
-Liblinear  & 0.79s & 2.4s & 13s & --- \\
+Liblinear  & \textbf{0.79s} & \textbf{2.4s} & \textbf{13s} & --- \\
 \hline
@@
 \hline
-PSUBPLR-SPARK & 8.57s & 89.1s & 796s & 2918s \\
+PSUBPLR-SPARK & 8.57s & 89.1s & 796s & \textbf{2918s} \\
 \hline
@@
           As the platform is still under developing process, we expect that our running time results for PGDPLR-SPARK and PSUBPLR-SPARK can still be improved.
-          For example, Spark currently only supports for one reducer, thus it does not use full CPU power when performing reduce.
 
@@
    %\includegraphics[height=4.5cm,width=5cm]{img/2d_time.eps}&
-   \includegraphics[height=4.cm,width=4.5cm]{img/20NewsGroup_time.eps}&
-   \hspace{-0.6cm}\includegraphics[height=4.cm,width=4.5cm]{img/Gisette_time.eps}&
-   \hspace{-0.6cm}\includegraphics[height=4.cm,width=4.5cm]{img/ECUESpam_time.eps}&
-   \hspace{-0.6cm}\includegraphics[height=4.cm,width=4.5cm]{img/URL-Reputation_time.eps}\\
+   \includegraphics[height=3.9cm,width=4.5cm]{img/20NewsGroup_time.eps}&
+   \hspace{-0.6cm}\includegraphics[height=3.9cm,width=4.5cm]{img/Gisette_time.eps}&
+   \hspace{-0.6cm}\includegraphics[height=3.9cm,width=4.5cm]{img/ECUESpam_time.eps}&
+   \hspace{-0.6cm}\includegraphics[height=3.9cm,width=4.5cm]{img/URL-Reputation_time.eps}\\
    (a) \textbf{20NewsGroup}. & \hspace{-0.3cm}(b) \textbf{Gisette}. & \hspace{-0.3cm}(c) \textbf{ECUESpam}. & \hspace{-0.3cm}(d) \textbf{URL-Reputation}.\\
@@
 \begin{figure}[tb]
-\center \includegraphics[height=4.5cm,width=9cm]{img/fault_tolerance.eps}\vspace{-0.3cm}
+\center \includegraphics[height=4cm,width=8cm]{img/fault_tolerance.eps}\vspace{-0.3cm}
 \caption{Iteration time, as a function of percentage of failed maps, on \textbf{URL-Reputation} Dataset, run on 6 nodes}\label{fig:14}\vspace{-0.5cm}
@@
 Based on extensive experiments, we summarized key features of each algorithm implemented on different computing platforms.
+We can conclude that sequential algorithms with memory intensive operations like Liblinear can perform very well if datasets can fit in memory.
+For massive datasets, if limited by machine resources, Mahout with its online algorithm is a choice with relatively low precision.
+If we have enough machines, as Spark outperforms Hadoop for LR model training, we recommend to choose between parallel sublinear method and parallel gradient descent method (both implemented in Spark) to trade off between running time and precision.
 Our future work will focus on combining algorithm design and computing platforms to optimize classifiers in machine learning.

### 2013-06-24 draft.tex
final edtion on conclusion and citation

@@
 It can then increase the number of parallel computational nodes to several hundreds.
-Later, the work of Parallel Latent Dirichlet Allocation (PLDA)~\cite{wang2009plda}~\cite{newman2007distributed} improves the computational efficiency of the LDA model by means of sampling methods.
+Later, the work of Parallel Latent Dirichlet Allocation (PLDA)~\cite{Liu:2011:PPL:1961189.1961198}~\cite{newman2007distributed} improves the computational efficiency of the LDA model by means of sampling methods.
 The parallel algorithm in Hadoop is robust, for it has fault tolerance of machine failures, thus taking advantage of Hadoop features.
@@
 We can conclude that sequential algorithms with memory intensive operations like Liblinear can perform very well if datasets can fit in memory.
-For massive datasets, if limited by machine resources, Mahout with its online algorithm is a choice with relatively low precision.
-If we have enough machines, as Spark outperforms Hadoop for LR model training, we recommend to choose between parallel sublinear method and parallel gradient descent method (both implemented in Spark) to trade off between running time and precision.
+For massive datasets, if limited by machine resources, Mahout with its online algorithm is a good choice with a slightly lower precision.
+If machine resources are abundant, as Spark outperforms Hadoop for LR model training, we recommend to choose between parallel sublinear method and parallel gradient descent method (both implemented in Spark) to trade off between speedup and precision.
 Our future work will focus on combining algorithm design and computing platforms to optimize classifiers in machine learning.

### 2013-09-06 draft-backup.tex
revised once

--- 2013-06-24 draft.tex
@@
 % edited by Haoruo Peng
-% Date: 2013.6.21
+% Date: 2013.9.5
 \documentclass[10pt, conference, compsocconf]{IEEEtran}
@@
 \and
-\IEEEauthorblockN{Deli Zhao}
-\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\zhaodeli@gmail.com}
-\and
+%\IEEEauthorblockN{Deli Zhao}
+%\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\zhaodeli@gmail.com}
+%\and
 \IEEEauthorblockN{Cyrus Choi}
@@
 LR is a supervised learning model for pattern classification and enjoys the benefits of statistical principles.
-This paper addresses the issue of computational efficiency for solving LR in the big data scenario.
+This paper addresses the issue of computational efficiency for solving LR in big data scenario.
 We compare the performance between different computing platforms and different parallel algorithms.
 Our goal is to provide valuable suggestions on choosing computing platforms and learning algorithms according to different application situations for specific datasets and machine resources.
-Three different parallel computing platforms along with three different types of parallel algorithms are carefully studied in this paper.
-In addition, we present a novel parallel sublinear method to optimize the solution of LR.
-%Hadoop, Mahout and Spark are three existing parallel computing platforms that can be implemented with large scale machine learning algorithms.
-%Parallel gradient Descent and stochastic gradient descent are two state-of-art algorithms for solving LR.
-To enhance capability, we consider the tradeoff between efficiency and accuracy. Extensive experimental results verify the effective performance of proposed algorithms.
+We also present a novel parallel sublinear method to optimize the solution of LR.
+Overall, two different parallel computing platforms along with three different types of parallel algorithms are carefully studied in this paper.
+To enhance capability, we consider the tradeoff between efficiency and accuracy.
+Extensive experimental results verify the effective performance of proposed algorithms.
 \end{abstract}
@@
 Large data volume and high data dimensionality bring unavoidable computational challenges to machine learning problems.
-For example, in social networks, we have datasets~\cite{lewis2008tastes} covering multiple dimensions like friendship relationship and share of common interests.
+For example, in social networks, we have datasets covering multiple dimensions like friendship relationship and share of common interests.
 They generally include millions of records over millions of attributes.
-More evidently, for the task of text and multimedia categorization, we usually have to handle datasets with data volumes in billion scales and each data instance is characterized by thousands of feature dimensions~\cite{chang2011foundations}.
+More evidently, for the task of text and multimedia categorization, we usually have to handle datasets with data volumes in billion scales and each data instance is characterized by thousands of feature dimensions.
 We tackle these challenges on both algorithm level and computing platform level via parallelization methods.
@@
 When developing parallel algorithms for LR, it is inevitable to come across the question of choosing which parallel computing platform to employ.
-After a thorough survey, we choose three unique and best-known computing platforms to test: Hadoop~\cite{white2012hadoop}, Mahout~\cite{mahoutscalable} and Spark~\cite{zaharia2010spark}.
+After a thorough survey, we choose two unique and best-known computing platforms to test: Hadoop~\cite{white2012hadoop} and Spark~\cite{zaharia2010spark}.
 Hadoop employs HDFS~\cite{borthakur2008hdfs} and MapReduce~\cite{dean2008mapreduce}.
-Mahout runs on Apache Hadoop and makes improvements in low level code.
 Spark promotes efficiency of iterative algorithms and also supports HDFS.
-We will compare design features of these three computing platforms separately in Section~\ref{sec:platform}.
+We will compare design features of these two computing platforms in Section~\ref{sec:platform}.
 
@@
 
-\subsection{Scalability Solutions}
+%\subsection{Scalability Solutions}
 %
-In big data scenarios, large datasets require us to develop machine learning algorithms towards a more efficient and more parallelized end.
+%In big data scenarios, large datasets require us to develop machine learning algorithms towards a more efficient and more parallelized end.
 Researchers have already done much work to cater for the needs of massive datasets.
@@
 
+In this paper, we specifically compares parallelization efforts of LR in two dimensions: platform and algorithm.
 \subsection{Computing Platforms}\label{sec:platform}
-In this paper, we specifically compares parallelization efforts of LR in two dimensions: platform and algorithm.
-
-Three computing platforms that we are working on have their own advantages to implement machine learning algorithms.
-The Apache Hadoop~\cite{white2012hadoop} software library allows for distributed processing of large datasets across clusters of computers using simple programming models.
-Hadoop utilizes MapReduce~\cite{dean2008mapreduce} as its computational paradigm.
-MapReduce paradigm takes a set of key-value pairs as its input.
-Then a user-defined \textit{map} function turns the input into some intermediate key-value pairs.
-Another user-defined \textit{reduce} function merges values for the same intermediate pairs to produce output.
-All of the operations are independent, thereby making MapReduce paradigm easy to be parallelized.
+Two computing platforms that we are working on have their own advantages to implement machine learning algorithms.
+The Hadoop~\cite{white2012hadoop} platform allows for distributed processing of large datasets across clusters of computers using simple programming models.
+It utilizes MapReduce~\cite{dean2008mapreduce} as its computational paradigm, which is easy to be parallelized.
 In addition, Hadoop provides a Distributed File System (HDFS).
 Both MapReduce and HDFS are designed to handle node failures in an automatic way, making Hadoop support large clusters that are built on commodity hardware.
-The goal of Apache Mahout~\cite{mahoutscalable} is to build scalable machine learning libraries.
-Their core algorithms for clustering, classification and collaborative filtering are implemented on top of Apache Hadoop using the MapReduce paradigm.
-The core libraries are highly optimized so that Apache Mahout also has good performance for non-distributed algorithms.
 Spark~\cite{zaharia2010spark} is a cluster computing system that aims to make data analysis fast.
-Spark supports in-memory cluster computing. A job can load data into memory and query it repeatedly by creating and caching resilient distributed datasets (RDDs).
+It supports in-memory cluster computing.
+A job can load data into memory and query it repeatedly by creating and caching resilient distributed datasets (RDDs).
 Moreover, RDDs achieve fault tolerance through lineage: information about how RDDs are derived from other RDDs is stored in reliable storage, thus making RDDs easy to be rebuilt if a certain partition is lost.
@@
 In Table~\ref{tab:systemcmp}, we compare different features between Hadoop and Spark computing platforms.
-As Mahout is mainly built on Hadoop, it inherits most of Hadoop features.
 For simplicity, we use short abbreviations in the table.
@@
 
+It is worth mentioning that Apache Mahout~\cite{mahoutscalable} runs on Hadoop, and it is a scalable machine learning library.
+It integrates many core algorithms for clustering, classification and collaborative filtering in its package.
+It is highly optimized so that Mahout also has good performance for non-distributed algorithms.
+We will use it as a baseline in the experiments.
+
 \subsection{Sublinear Methods}
@@
 %In~\cite{hazan2011optimal}, Hazan \etal applied the sublinear approximation approach to solve linear regression with penalties.
-Garber and Hazan~\cite{garberapproximating} also developed it in Semi-Definite Programming (SDP).
+%Garber and Hazan~\cite{garberapproximating} also developed it in Semi-Definite Programming (SDP).
 Peng \etal~\cite{peng2012sublinear} utilized the method in the LR model with penalties and developed sequential sublinear algorithms for both $\ell_1$-penalty and $\ell_2$-penalty.
@@
 The learning process aims to optimize $\w$ and $b$.
-To make the optimization problem more practical to solve, a common practice is to add penalties to LR model.
+It is a common practice to add penalties to LR model in order to avoid overfitting and make the optimization result more practical.
 Typically, for $\ell_2$-penalty, we solve the following optimization problem:\vspace{-0.2cm}
@@
 $\varepsilon$ controls learning rate, $T$ determines iteration number, and $\eta$ defines approximation level.
+Details of the parameter initialization step is studied in~\cite{peng2012sublinear}.
+To be concise, we omit them in this paper.
 	\begin{table} [ht]
@@
     20: \tspaces job\_dual.run() \\	
-    21: \tspaces $\bp_{t+1}$$\leftarrow$Dual-Update($\bp_t$) \\
+    21: \tspaces $\bp_{t+1}\leftarrow$Dual-Update($\bp_t$) \\
     22: Output: $\bar{\bw}=\frac{1}{T}\sum_{t}{\bw}_{t},\bar{b}=\frac{1}{T}\sum_{t}{b}_{t}$ \\
@@
 There are also three more things that need to be handled here.
-First is the parameter passing issue. It is critical to choose an efficient way to pass the updated parameters between iterations and even between different MapReduce jobs.
-It is even more challenging when we have to deal with HDFS. It is clear that the fastest communication way is to pass parameters by \textit{Configuration()}.
-However, it always suffers from memory buffer limits, and will greatly impair scalability when the number of parameters is huge.
-Another way is to compress the parameter sequence in a string when sending and uncompress them when receiving. It has computational overhead and it still cannot avoid the issue of memory buffer limit.
+First is the parameter passing issue.
+It is critical to choose an efficient way to pass the updated parameters between iterations and even between different MapReduce jobs.
 Considering the philosophy of the design of Hadoop, the natural thing to do is to pass parameters by file, the same way to pass all the data.
+We use a single file to pass all parameters each time when a job starts or finishes separately.
 Although such an operation is insufficiently efficient, it is the feasible way to support large datasets.
 
-The second issue is the small changes that we make to cater for the $\ell_2$-penalty and $\ell_1$-penalty. The changes are only made in Procedure Primal-Update.
+The second issue is the small changes that we make to cater for the $\ell_2$-penalty and $\ell_1$-penalty.
+The changes are only made in Procedure Primal-Update.
 It affects little for the implementation, and the extension is just the same as that in Algorithm~1.
@@
 
-The datasets are generally sparse when data dimensionally is high. This characteristic makes us focus on dealing with data sparsity issue when writing code.
-This is the third important thing for the algorithm, although it is not reflected in the pseudo-code.
-Instead of naively writing the simple code in data intensive situations, we assign the \textit{index} for each data value in the sparse vector, and all computations are changed accordingly.
+The datasets are generally sparse when data dimensionally is high.
+This characteristic makes us focus on dealing with data sparsity issue when writing code.
+Instead of naively writing the simple code in data intensive situations, we only store pairs of \textit{index} and \textit{value} in a data vector.
+Then all computations are changed accordingly.
 This sparse format brings us great efficiency improvement, and all results in Section~\ref{sec:experiment} are obtained from the code for sparsity.
@@
     8:  ~\tspace pAdjust $\leftarrow$ points.map(MW-Update()).reduce(copy()) \\
-    9:  ~\tspace $\bp_{t+1}$$\leftarrow$Dual-Update($\bp_t$)  \\
+    9:  ~\tspace $\bp_{t+1}\leftarrow$Dual-Update($\bp_t$)  \\
     10: \textbf{Output}($\bw, b$) \\
@@
 Compared to the analysis of sequential algorithm, parallelization does not necessarily change computational complexity.
-Theoretically, by deeper analysis of constant coefficients of the obtained computational complexity, parallel sublinear algorithm can be two times faster than the sequential version.
+Theoretically, parallel sublinear algorithm can be two times faster than the sequential version as the time for both update procedures in each iteraion is reduced to $O(1)$.
 Moreover, by starting two separate MapReduce jobs in one iteration simultaneously, the running time can be reduced to $O(max\{n,d\})$.
@@
 In addition, we can halt training when a model reaches a target level of performance.
-The SGD framework includes classes to do online evaluation using cross validation (the \textit{CrossFoldLearner}) and an evolutionary system to hyper-parameter optimization on the fly (the \textit{AdaptiveLogisticRegression}).
-The \textit{AdaptiveLogisticRegression} system makes heavy use of threads to increase machine utilization.
-To do so, it runs 20 \textit{CrossFoldLearners} in separate threads, each with slightly different learning parameters.
-As better settings are found, these new settings propagate to the other learners.
-
-Because the SGD algorithms need feature vectors of fixed length and it is a pain to build a dictionary ahead of time, most SGD applications use the encoding system that is rooted at \textit{FeatureVectorEncoder} to derive hashed feature vectors.
-The basic idea is that you create a vector, typically a \textit{RandomAccessSparseVector}, and then you use various feature encoders to progressively add features to that vector.
-The size of the vector should be large enough to avoid feature collisions as features are hashed.
-There are specialized encoders for a variety of data types.
-You can normally encode either a string representation of the value you want to encode or you can encode a byte representation to avoid string conversion.
-In the case of \textit{ContinuousValueEncoder} and \textit{ConstantValueEncoder}, it is also possible to encode a null value and pass the real value as a weight.
+Because the SGD algorithms need feature vectors of fixed length and it is very costly to build a dictionary ahead of time, most SGD applications use an encoding system to derive hashed feature vectors.
+We can create a \textit{RandomAccessSparseVector}, and then use various feature encoders to progressively add features to this vector.
 
@@
 \end{table*}
-These five datasets are carefully selected.
-The simulated \textbf{2d} dataset can be viewed as visual result and serves for the initial test of correctness of classifiers.
+These five datasets are carefully selected with an incremental trend in size.
+The simulated \textbf{2d} dataset represents toy data situations and serves for the initial test of correctness of classifiers.
 The \textbf{20NewsGroup} dataset is best-known for the test of LR model, which has a balanced distribution between positive and negative data instances.
-The \textbf{Gisette} dataset~\cite{guyon2004result} is relatively larger, and feature vectors are less sparse. Thus it requires more computation theoretically.
+It also shows the application towards topic classification.
+The \textbf{Gisette} dataset~\cite{guyon2004result} is relatively larger, and feature vectors are less sparse.
 The \textbf{ECUESpam} dataset~\cite{DelanyKBS05} is selected due to its imbalanced distribution between positive and negative data instances.
@@
 Online stochastic gradient descent method is run on Mahout in a sequential mode.
-Liblinear~\cite{fan2008liblinear} is the baseline test program we choose. It is sequential and outperforms many other programs for LR on a single machine.
+Liblinear~\cite{fan2008liblinear} is also a baseline test program we choose. It is sequential and outperforms many other programs for LR on a single machine.
 SLLR performs the sequential sublinear algorithm on a single machine.
@@
 In this section, we conduct empirical analysis on experimental results.
-We show three things: 1) correctness of our test program, 2) accuracy comparison, and 3) speedup comparison.
-
-\subsection{Results on Simulated 2d Dataset}
-%
-\begin{figure}[tb]
-\center \includegraphics[height=4cm,width=5.14cm]{img/2d-show.eps}\vspace{-0.3cm}
-\caption{Visual result on simulated \textbf{2d} dataset}\label{fig:02}\vspace{-0.5cm}
-\end{figure}
-%
-Fig.~\ref{fig:02} shows the visual result for the simulated \textbf{2d} dataset.
-Here we use all data for training and testing, thus "Test Error" here can be interpreted as "Training Error".
-The green line shows the result for all sublinear methods, including SLLR, PSUBPLR-MR and PSUBPLR-SPARK.
-The results on the simulated \textbf{2d} dataset proves the correctness of all test programs.
+We show four things: 1) accuracy, 2) efficiency, 3) scalability and 4) robustness.
 
@@
           This running time overhead is not negligible, especially when dataset is relatively small.
-          We also identify that the running of "Primal-Map" dominates the whole iteration time (more than 66\%). It is the same situation for PSUBPLR-SPARK.
+          We also identify that the running of ``Primal-Map" dominates the whole iteration time (more than 66\%). It is the same situation for PSUBPLR-SPARK.
 
@@
           The former has higher data dimensionality but more sparse.
-          We can find that algorithms on \textbf{ECUESpam} dataset enjoy less running time per iteration than on \textbf{GISETTE} dataset as \textbf{ECUESpam} has fewer nonzero values involved in the computation.
+          Compare the data point between Figure~\ref{fig:time}(b) and~\ref{fig:time}(c) We can find that algorithms on \textbf{ECUESpam} dataset enjoy less running time per iteration than on \textbf{GISETTE} dataset as \textbf{ECUESpam} has fewer nonzero values involved in the computation.
           However, algorithms on \textbf{ECUESpam} dataset need more iterations than on \textbf{GISETTE} dataset, which is related to higher data dimensionality of \textbf{ECUESpam} dataset.
@@
 \section{Conclusion} \label{sec:concl}
-In this paper we analyzed three optimization approaches along with three computing platforms to train LR model on large-scale, high-dimensional datasets for classification.
-In addition, we presented a novel parallel sublinear algorithm for LR implemented on both Hadoop and Spark.
+In this paper we analyzed three optimization approaches along with two computing platforms to train LR model on large-scale, high-dimensional datasets for classification.
+A novel parallel sublinear algorithm for LR implemented on both Hadoop and Spark is presented.
 Based on extensive experiments, we summarized key features of each algorithm implemented on different computing platforms.
@@
 For massive datasets, if limited by machine resources, Mahout with its online algorithm is a good choice with a slightly lower precision.
-If machine resources are abundant, as Spark outperforms Hadoop for LR model training, we recommend to choose between parallel sublinear method and parallel gradient descent method (both implemented in Spark) to trade off between speedup and precision.
-Our future work will focus on combining algorithm design and computing platforms to optimize classifiers in machine learning.
+If machine resources are abundant, as Spark outperforms Hadoop for LR model training, we recommend choosing between parallel sublinear method and parallel gradient descent method (both on Spark) to trade off between speedup and precision.
+
+In future work, we will continue to explore the situations of even bigger dataset, and extend the results to multi-calss classification models of LR.
+We also would like to focus on combining algorithm design and computing platforms to optimize classifiers in machine learning.
 

### 2013-09-10 draft.tex
final workshop version

@@
 
-\title{Learning for Logistic Regression Model in Parallel}
+\title{Evaluating Parallel Logistic Regression Models}
 
@@
 \IEEEauthorblockN{Haoruo Peng}
-\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\penghaoruo@hotmail.com}
+\IEEEauthorblockA{HTC Research Center\\Beijing, China\\penghaoruo@hotmail.com}
 \and
 \IEEEauthorblockN{Ding Liang}
-\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\Ding\_Liang@htc.com}
+\IEEEauthorblockA{HTC Research Center\\Beijing, China\\Ding\_Liang@htc.com}
 \and
-\IEEEauthorblockN{Deli Zhao}
-\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\zhaodeli@gmail.com}
-\and
+%\IEEEauthorblockN{Deli Zhao}
+%\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\zhaodeli@gmail.com}
+%\and
 \IEEEauthorblockN{Cyrus Choi}
-\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\Cyrus\_Choi@htc.com}
-\and
-\IEEEauthorblockN{Edward Y. Chang}
-\IEEEauthorblockA{HTC Research Lab\\Beijing, China\\Edward\_Chang@htc.com}
+\IEEEauthorblockA{HTC Research Center\\Beijing, China\\Cyrus\_Choi@htc.com}
 }
@@
 \begin{abstract}
-Logistic regression (LR) model has various applications in machine learning.
-LR is a supervised learning model for pattern classification and enjoys the benefits of statistical principles.
-This paper addresses the issue of computational efficiency for solving LR in the big data scenario.
-We compare the performance between different computing platforms and different parallel algorithms.
-Our goal is to provide valuable suggestions on choosing computing platforms and learning algorithms according to different application situations for specific datasets and machine resources.
-Three different parallel computing platforms along with three different types of parallel algorithms are carefully studied in this paper.
-In addition, we present a novel parallel sublinear method to optimize the solution of LR.
-%Hadoop, Mahout and Spark are three existing parallel computing platforms that can be implemented with large scale machine learning algorithms.
-%Parallel gradient Descent and stochastic gradient descent are two state-of-art algorithms for solving LR.
-To enhance capability, we consider the tradeoff between efficiency and accuracy. Extensive experimental results verify the effective performance of proposed algorithms.
+Logistic regression (LR)  has been widely used in applications of machine learning, thanks to its linear model.
+However, when the size of training data is very large, even such a linear model can consume excessive memory and computation time.
+To tackle both resource and computation scalability in a big-data setting, we evaluate and compare different approaches in distributed platform, parallel algorithm, and sublinear approximation.
+Our empirical study provides design guidelines for choosing the most effective combination for the performance requirement of a given application.
 \end{abstract}
@@
 \section{Introduction} \label{sec:int}
-Logistic regression model~\cite{HastieBook:SL} plays a vital role in machine learning.
-It is a widely used model in algorithms like PageRank~\cite{page1999pagerank} and anti-spam filtering~\cite{androutsopoulos2000evaluation}.
-The model serves for classification problems, and is supported by a substantial body of statistical theories and algorithms.
+The logistic regression model~\cite{HastieBook:SL} plays a pivotal role in machine learning tasks.
+%It is a widely used model in applications such as PageRank~\cite{page1999pagerank} and anti-spam %filtering~\cite{androutsopoulos2000evaluation}.
+The model is suited for classification problems and is supported by a substantial body of statistical theories.
 A binary classification problem modeled by LR can be easily extended to a multi-class classification problem.
-Also, due to the strong statistical foundation of the LR model, we can extend achieved results into a deeper analysis which may apply to other classification models.
-We will focus on the binary LR model in this paper.
+We focus our study on the binary LR model in this paper (and the conclusions can be extended to a multi-class setting).
 
-In recent years, many modern datasets grow drastically in both data volume and data dimensionality.
-Large data volume and high data dimensionality bring unavoidable computational challenges to machine learning problems.
-For example, in social networks, we have datasets~\cite{lewis2008tastes} covering multiple dimensions like friendship relationship and share of common interests.
-They generally include millions of records over millions of attributes.
-More evidently, for the task of text and multimedia categorization, we usually have to handle datasets with data volumes in billion scales and each data instance is characterized by thousands of feature dimensions~\cite{chang2011foundations}.
-We tackle these challenges on both algorithm level and computing platform level via parallelization methods.
-For many applications, in order to attain speedup in performance, we can employ not only task parallelism, but also data parallelism~\cite{subhlok1993exploiting}.
-In this paper, we mainly discuss issues in task parallelism.
+In recent years, many modern datasets have grown drastically in both data volume and data dimensionality.
+Large data volume and high data dimensionality bring both resource and computational challenges to machine learning algorithms.
+For example, a social networking site such as Facebook consists of tens of millions of records, each is composed of hundreds of attributes.
+For text and multimedia categorization, we usually have to deal with billion-scale datasets in a feature space of thousands of dimensions.
+In this work, we evaluate approaches to scale up LR in a big-data setting.
+The approaches we evaluate include three aspects: 1) distributed platform, 2) parallel algorithm, and 3) sublinear approximation.
 
-When developing parallel algorithms for LR, it is inevitable to come across the question of choosing which parallel computing platform to employ.
-After a thorough survey, we choose three unique and best-known computing platforms to test: Hadoop~\cite{white2012hadoop}, Mahout~\cite{mahoutscalable} and Spark~\cite{zaharia2010spark}.
+In the platform aspect, we compare two well known distributed systems:
+ Hadoop~\cite{white2012hadoop} and Spark~\cite{zaharia2010spark}.
 Hadoop employs HDFS~\cite{borthakur2008hdfs} and MapReduce~\cite{dean2008mapreduce}.
-Mahout runs on Apache Hadoop and makes improvements in low level code.
-Spark promotes efficiency of iterative algorithms and also supports HDFS.
-We will compare design features of these three computing platforms separately in Section~\ref{sec:platform}.
-
-In sequential optimization algorithms for LR model, a classical way is to resort to stochastic approximation methods.
-Stochastic approximation methods, such as stochastic gradient descent~\cite{zhang2004solving} and stochastic dual averaging~\cite{xiao2010dual}, obtain optimal generalization guarantees with a small number of passes over data with runtime linear to the dataset size.
-The stochastic gradient descent method can work in an online fashion, as we view sampled data points as data stream over algorithmic iteration.
-It is hard to be changed to task-parallelism, but it is blazingly fast.
-If we take a step back to the general gradient descent to solve LR model, we can find that it can be actually embarrassingly parallel.
-We can take in all of the data at the same iteration and just compute the gradient in a MapReduce fashion.
-We can further speed up the runtime by employing sublinear algorithms~\cite{peng2012sublinear} via the application of the stochastic approximation idea.
-These methods access a single feature of feature vectors instead of entire feature vectors at each iteration.
-We propose a parallel version of this algorithm and achieve the result of comparable accuracy while being faster convergent.
+Spark promotes the efficiency of iterative algorithms and also supports HDFS.
+In the parallel algorithm aspect, we compare the sequential optimization algorithms: stochastic gradient descent~\cite{zhang2004solving}, which can
+obtain optimal generalization guarantees with a small number of passes over the data.
+ The algorithm can easily be parallelized on either Hadoop or Spark, and it can also be used in an online setting, at which a data instance is seen only once in a streaming fashion.
+Finally, to further speed up computation, we compare aforementioned platform/algorithm combinations with our previously proposed sublinear algorithms~\cite{peng2012sublinear}.
+These sublinear algorithms access a single feature of a feature vector instead of all features at each iteration to reduce computation time.
+Our evaluation and comparisons provide insights to facilitate an application designer for selecting a solution that best meets the performance requirement of the machine-learning task at hand.
 
@@
 
+We present related work in the two aspects: platform and algorithm.
 \subsection{Computing Platforms}\label{sec:platform}
-In this paper, we specifically compares parallelization efforts of LR in two dimensions: platform and algorithm.
+The two distributed platforms that we work with have their
+own advantages in the implementation of machine learning algorithms.
+The Hadoop~\cite{white2012hadoop} platform allows for distributed processing of large datasets across clusters of computers using simple programming models.
+It utilizes MapReduce~\cite{dean2008mapreduce} as its computational paradigm, which is easily parallelized.
+Additionally, Hadoop provides a Distributed File System (HDFS).
+Both MapReduce and HDFS are designed to handle node failures in an automatic way, allowing Hadoop to support large clusters that are built on commodity hardware.
+Spark~\cite{zaharia2010spark} is a cluster computing system that aims to make data analysis fast.
+It supports the in-memory cluster computing.
+A job can load data into memory and query it repeatedly by creating and caching resilient distributed datasets (RDDs).
+Moreover, RDDs achieve fault tolerance through lineage: information about how RDDs are derived from other RDDs is stored in reliable storage, thus making RDDs easy to be rebuilt if a certain partition is lost.
+Spark can execute up to be two orders faster than Hadoop for iterative algorithms.
 
-Three computing platforms that we are working on have their own advantages to implement machine learning algorithms.
-The Apache Hadoop~\cite{white2012hadoop} software library allows for distributed processing of large datasets across clusters of computers using simple programming models.
-Hadoop utilizes MapReduce~\cite{dean2008mapreduce} as its computational paradigm.
-MapReduce paradigm takes a set of key-value pairs as its input.
-Then a user-defined \textit{map} function turns the input into some intermediate key-value pairs.
-Another user-defined \textit{reduce} function merges values for the same intermediate pairs to produce output.
-All of the operations are independent, thereby making MapReduce paradigm easy to be parallelized.
-In addition, Hadoop provides a Distributed File System (HDFS).
-Both MapReduce and HDFS are designed to handle node failures in an automatic way, making Hadoop support large clusters that are built on commodity hardware.
-The goal of Apache Mahout~\cite{mahoutscalable} is to build scalable machine learning libraries.
-Their core algorithms for clustering, classification and collaborative filtering are implemented on top of Apache Hadoop using the MapReduce paradigm.
-The core libraries are highly optimized so that Apache Mahout also has good performance for non-distributed algorithms.
-Spark~\cite{zaharia2010spark} is a cluster computing system that aims to make data analysis fast.
-Spark supports in-memory cluster computing. A job can load data into memory and query it repeatedly by creating and caching resilient distributed datasets (RDDs).
-Moreover, RDDs achieve fault tolerance through lineage: information about how RDDs are derived from other RDDs is stored in reliable storage, thus making RDDs easy to be rebuilt if a certain partition is lost.
-Spark can run up to 100 times faster than Hadoop for iterative algorithms.
-
-In Table~\ref{tab:systemcmp}, we compare different features between Hadoop and Spark computing platforms.
-As Mahout is mainly built on Hadoop, it inherits most of Hadoop features.
-For simplicity, we use short abbreviations in the table.
+Table~\ref{tab:systemcmp} compares different features between Hadoop and Spark platforms.
 Spark supports two types of operations on RDDs: Actions and Transformations (As and Ts).
@@
 Transformations include functions like \textit{map}, \textit{filter} and \textit{join}. They normally build new RDDs from other RDDs, which comply with the lineage rule.
-In the table, we use ``NFS" to represent ``Normal File System" and "Fault Tolerance" here is specifically for node failure situations.
+In the table, we use ``NFS" to denote ``Normal File System".\
+
 \begin{table}[h]
@@
 \hline
-\end{tabular}\vspace{-0.5cm}
+\end{tabular}
+%\vspace{-0.5cm}
 \end{table}
 
+It is worth mentioning that Apache Mahout~\cite{mahoutscalable} runs on Hadoop and is a scalable machine learning library.
+Mahout integrates many important algorithms for clustering, classification and collaborative filtering in its package.
+It is highly optimized so that Mahout also achieves good performance for non-distributed algorithms.
+We use Mahout as the baseline in our experiments.
+
 \subsection{Sublinear Methods}
-Sublinear methods are recently proposed by many researchers.
+
+Sublinear methods have recently been proposed by several researchers.
 Clarkson \etal~\cite{clarkson2010sublinear} first presented the solution of approximation algorithms in sublinear time.
-It is applied to optimization problems for linear classifiers and minimum enclosing balls.
 The algorithm employs a novel sampling technique along with a new multiplicative update procedure.
-Hazan \etal~\cite{hazanbeating} exploited the approach to linear SVM.
-Cotter \etal~\cite{cotter2012kernelized} extended the method to kernelized SVM.
-%In~\cite{hazan2011optimal}, Hazan \etal applied the sublinear approximation approach to solve linear regression with penalties.
-Garber and Hazan~\cite{garberapproximating} also developed it in Semi-Definite Programming (SDP).
+Hazan \etal~\cite{hazanbeating} exploited the approach to speed up linear SVMs.
+Cotter \etal~\cite{cotter2012kernelized} extended the method to kernelized SVMs.
+In~\cite{hazan2011optimal}, Hazan \etal applied the sublinear approximation approach to solve linear regression with penalties.
+Garber and Hazan~\cite{garberapproximating} also developed sublinear method with Semi-Definite Programming (SDP).
 Peng \etal~\cite{peng2012sublinear} utilized the method in the LR model with penalties and developed sequential sublinear algorithms for both $\ell_1$-penalty and $\ell_2$-penalty.
+
+\subsection{Other Related Work}
+
+LR is fairly straightforward to be parallelized.
+Parallelization efforts on several machine learning algorithms such as SVMs~\cite{chang2011psvm}, LDA~\cite{Liu:2011:PPL:1961189.1961198}, Spectral Clustering~\cite{Chen5444877}, and frequent itemset mining~\cite{Li:2008:PPF:1454008.1454027} require much more sophisticated sharding work to divide a computational task evenly onto distributed subtasks.
+For a comprehensive survey, please consult~\cite{chang2011foundations} and~\cite{Bekkerman2012}.
 
@@
 \subsection{Logistic Regression Model} \label{sec:def}
-In this paper, we are mainly concerned with the binary classification problem.  	
+In this paper, we mainly concern the binary classification problem.  	
 We define the training dataset as $\XM=\{(\x_i, y_i): i=1, \ldots, n\}$, where $\x_i \in \RB^d$ are input samples and $y_i \in \{-1, 1\}$ are the corresponding labels.
-For simplicity, we will use the notation $\X=[{\x}_{1}, {\x}_{2}, \ldots, {\x}_n]^{T}$ and $\y=(y_1, y_2, \ldots, y_n)^T$ to represent the training dataset in the following.
+For simplicity, we will use the notation $\X=[{\x}_{1}, {\x}_{2}, \ldots, {\x}_n]^{T}$ and $\y=(y_1, y_2, \ldots, y_n)^T$ to represent the training dataset in this paper.
 To fit in the logistic regression model, the expected value of $y_i$ is given by\vspace{-0.2cm}
@@
 
-The learning process aims to optimize $\w$ and $b$.
-To make the optimization problem more practical to solve, a common practice is to add penalties to LR model.
+The learning process aims to derive $\w$ and $b$ by solving an optimization problem.
+It is a common practice to add penalties to LR model in order to avoid overfitting and make the optimization result more practical.
 Typically, for $\ell_2$-penalty, we solve the following optimization problem:\vspace{-0.2cm}
@@
 \subsection{Sequential Sublinear Algorithm}
-We use the following notations to define sequential sublinear algorithm for penalized logistic regression. $clip\lc \cdot \rc$ is a projection function defined as $
-clip\lc a,b \rc \triangleq \max \lc \min \lc a,b \rc ,-b\rc,\,a,b\in \mathbb{R}$. $\sgn \lc \cdot \rc$ is the sign function; namely, $\sgn \lc \cdot \rc \in \{-1,0,1\}$.
+We use the following notations to define sequential sublinear algorithm for penalized logistic regression. Function $clip\lc \cdot \rc$ is a projection function defined as $
+clip\lc a,b \rc \triangleq \max \lc \min \lc a,b \rc ,-b\rc,\,a,b\in \mathbb{R}$.
+Function $\sgn \lc \cdot \rc$ is the sign function; namely, $\sgn \lc \cdot \rc \in \{-1,0,1\}$.
 $g\lc \cdot \rc$ is the logistic function $g \lc x \rc=1/(1+e^{-x})$.
@@
 In Algorithm~1, we give the sequential sublinear approximation procedure for logistic regression.
-The algorithm is mainly from~\cite{peng2012sublinear}.
-Symbols we use here comply with the definition in Section~\ref{sec:def}.
-$\varepsilon$ controls learning rate, $T$ determines iteration number, and $\eta$ defines approximation level.
+The algorithm is from our previous work~\cite{peng2012sublinear}.
+Mathematical symbols we use here comply with definitions in Section~\ref{sec:def}.
+Parameter $\varepsilon$ controls learning rate, $T$ determines iteration number, and $\eta$ defines approximation level.
+Details of the parameter initialization step are documented in~\cite{peng2012sublinear}.
+
 	\begin{table} [ht]
@@
 	\end{table}
+
 Each iteration of the SLLR algorithm has two phases: \textit{stochastic primal update} and \textit{stochastic dual update}.
-Steps from line 4 to line 11 consist of the primal part while the dual part is composed of steps from line 12 to line 16.
+Steps from line $4$ to line $11$ consist of the primal part while the dual part is composed of steps from line $12$ to line $16$.
 We give the sublinear algorithm in a unified way for $\ell_2$-penalty and $\ell_1$-penalty.
@@
 \}$.
-If we are faced with $\ell_1$-penalty, we ignore line 8 and expand the procedure of line 9 as following.
+If we are faced with $\ell_1$-penalty, we ignore line $8$ and expand the procedure of line $9$ as the following:
+
 \begin{table} [ht]
@@
 \section{Parallel Sublinear Logistic Regression} \label{sec:framework}
-In this section, we will describe our parallel sublinear algorithms implemented in Hadoop and Spark.
-We will also formally introduce the traditional parallel gradient algorithm used in Spark and the online stochastic gradient descent method used in Mahout.
+In this section, we describe our parallel sublinear algorithms implemented on Hadoop and Spark, respectively.
+We also formally introduce the traditional parallel gradient algorithm used in Spark and the online stochastic gradient descent method used in Mahout.
 In all pseudo-code, we follow symbol notations defined in Section~\ref{sec:def}.
-\subsection{Parallel Sublinear Algorithms in Hadoop}
-We develop an algorithm to sublinear learning for logistic regression using the architecture of MapReduce.
-The pseudo-code of Algorithm 2, Procedure for Primal-Map, Procedure for Primal-Reduce, Procedure for Primal-Update, Procedure for Dual-Map, and Procedure for Dual-Update explain the critical parts of this algorithm.
+\subsection{Parallel Sublinear Algorithms on Hadoop}
+We develop an algorithm to achieve sublinear performance for learning logistic regression parameters using the architecture of MapReduce.
+The pseudo-code of Algorithm 2, together with auxiliary procedures, explains the critical parts of this algorithm.
+
 	\begin{table}[ht]
@@
 This parallel design generally follows the framework of sequential sublinear algorithm.
-It remains to have two computational components in each iteration: the primal update part from line 4 to line 12 and the dual update part from line 13 to line 21.
-Within the primal update part, there is a parallel implementation period from line 4 to line 11, and also an unavoidable sequential period as illustrated in line 12.
-Within the dual part, it is the same situation that steps from line 14 to 20 employ parallel implementation while sequential operation is implemented in line 13 and line 21.
-As the primal part and dual part are decoupled in the sense of the parameters that they affect, these two separate MapReduce jobs can be performed simultaneously for each iteration, which brings us further parallelization and makes the algorithm more efficient.
-This framework is shown explicitly in Fig.~\ref{fig:frame}.
+It has two computational components in each iteration: the primal update part from lines $4$ to $12$ and the dual update part from lines $13$ to $21$.
+In the primal update part, there is a parallel implementation segment from lines $4$ to $11$, and also an unavoidable sequential segment as on line $12$.
+In the dual part, it is the same situation that steps from lines $14$ to 20 employ parallel implementation, whereas the sequential bottleneck is from lines $13$ to $21$.
+As the primal part and the dual part do not exhibit any inter-dependency, they can be executed simultaneously in each computation iteration.  This halves the computation time.
+This framework is shown in Fig.~\ref{fig:frame}.
 %
@@
 
-For the parallelization period in the \textit{primal mapreduce job}, we take advantage of the MapReduce design that takes in every data instance.
-Instead of the fashion in the sequential algorithm that we only sample one data instance in the primal update step, we compute gradients from ``almost" all data instances and make the weighted average value according to vector $\bp$ as the output gradient for update.
+In the parallelization segment of the \textit{primal mapreduce job}, we process all data instances in parallel.
+In the primal update step, we compute gradients from ``almost" all data instances and make the weighted average value according to vector $\bp$ as the output gradient for update.
 The details of this algorithm design is shown in Procedure Primal-Map and Procedure Primal-Reduce.
 Here, we employ a randomization strategy when we compute those ``almost" all gradients.
-From line 7 to line 8 in Procedure Primal-Map, all data instances are computed if $r=0$.
-As the expectation value for $\bp_t(i_t)$ is $\frac{1}{n}$, we normally set $r$ to range from 0 to 1.
-For the parallelization period in the \textit{dual mapreduce job}, we actually implement an embarrassingly parallel operation.
-It simply computes an individual value for each data instance in a parallel mode. It does not even need a reduce session.
+From lines $7$ to $8$ in Procedure Primal-Map, all data instances are computed if $r=0$.
+As the expectation value for $\bp_t(i_t)$ is $\frac{1}{n}$, we normally set $r$ to range between zero to one.
 
-There are also three more things that need to be handled here.
-First is the parameter passing issue. It is critical to choose an efficient way to pass the updated parameters between iterations and even between different MapReduce jobs.
-It is even more challenging when we have to deal with HDFS. It is clear that the fastest communication way is to pass parameters by \textit{Configuration()}.
-However, it always suffers from memory buffer limits, and will greatly impair scalability when the number of parameters is huge.
-Another way is to compress the parameter sequence in a string when sending and uncompress them when receiving. It has computational overhead and it still cannot avoid the issue of memory buffer limit.
-Considering the philosophy of the design of Hadoop, the natural thing to do is to pass parameters by file, the same way to pass all the data.
-Although such an operation is insufficiently efficient, it is the feasible way to support large datasets.
+Two more issues must be taken care of by the algorithm.
+The first issue is parameter passing.
+It is critical to choose an efficient way to pass the updated parameters between iterations and even between different MapReduce jobs.
+The design of Hadoop requires passing parameters between computation iterations through files.
+This IO step between iterations is clearly a bottleneck.
 
-The second issue is the small changes that we make to cater for the $\ell_2$-penalty and $\ell_1$-penalty. The changes are only made in Procedure Primal-Update.
-It affects little for the implementation, and the extension is just the same as that in Algorithm~1.
-To make the framework brief and standard, we omit the explanation here.
+%The second issue is the small changes that we make to cater for the $\ell_2$-penalty and $\ell_1$-penalty.
+%The changes are only made in Procedure Primal-Update.
+It affects little for the implementation, and the %extension is just the same as that in Algorithm~1.
+To make the framework brief and standard, we omit the %explanation here.
 
-The datasets are generally sparse when data dimensionally is high. This characteristic makes us focus on dealing with data sparsity issue when writing code.
-This is the third important thing for the algorithm, although it is not reflected in the pseudo-code.
-Instead of naively writing the simple code in data intensive situations, we assign the \textit{index} for each data value in the sparse vector, and all computations are changed accordingly.
-This sparse format brings us great efficiency improvement, and all results in Section~\ref{sec:experiment} are obtained from the code for sparsity.
+The second issue is that datasets are generally sparse when the data dimension is high.
+This characteristic makes us focus on dealing with data sparsity issue in our code.
+Instead of naively writing the simple code in data intensive situations, we only store pairs of \textit{index} and \textit{value} in a data vector.
+This sparse format brings us great memory-use efficiency improvement.
 
-\subsection{Parallel Sublinear algorithms in Spark}
+\subsection{Parallel Sublinear algorithms on Spark}
 The algorithm to solve sublinear learning for penalized logistic regression in Spark is shown below.
@@
 To make it work in Spark, we follow the rule to construct an RDD for each data instance.
-Also to cater for data sparsity, the design is that every data value correspond to its individual \textit{index}. And the \textit{index} is also involved in the computation along with the value.
+Also to cater for data sparsity, the design is that every data \textit{value} correspond to its individual \textit{index}.
+And the \textit{index} is also involved in the computation along with the \textit{value}.
 We omit the changes for $\ell_2$-penalty and $\ell_1$-penalty here to make the algorithm easier to be understood.
@@
 Compared to the analysis of sequential algorithm, parallelization does not necessarily change computational complexity.
-Theoretically, by deeper analysis of constant coefficients of the obtained computational complexity, parallel sublinear algorithm can be two times faster than the sequential version.
+Theoretically, parallel sublinear algorithm can be two times faster than the sequential version as the time for both update procedures in each iteration is reduced to $O(1)$.
 Moreover, by starting two separate MapReduce jobs in one iteration simultaneously, the running time can be reduced to $O(max\{n,d\})$.
@@
 
-In the pseudo-code of Algorithm 4, it is implemented in an embarrassingly parallel mode.
-We can take in all data at the same iteration and just compute the gradient in a MapReduce fashion.
+The pseudo-code of Algorithm 4 shows that the algorithm is naturally parallelizable.
+We can take in all data in the same iteration and just compute the gradient in a MapReduce fashion.
 As for the \textit{cache()} operation and RDD design for data sparsity, it is the same with Algorithm PSUBPLR-SPARK.
@@
 \subsection{Online Stochastic Gradient Descent in Mahout}
-Though SGD is an inherently sequential algorithm, it is blazingly fast. Thus Mahout's implementation can handle training sets of tens of millions of examples.
-The SGD system in Mahout is an online learning algorithm, implying that we can learn models in an incremental fashion and perform testing when the system runs.
-In addition, we can halt training when a model reaches a target level of performance.
-The SGD framework includes classes to do online evaluation using cross validation (the \textit{CrossFoldLearner}) and an evolutionary system to hyper-parameter optimization on the fly (the \textit{AdaptiveLogisticRegression}).
-The \textit{AdaptiveLogisticRegression} system makes heavy use of threads to increase machine utilization.
-To do so, it runs 20 \textit{CrossFoldLearners} in separate threads, each with slightly different learning parameters.
-As better settings are found, these new settings propagate to the other learners.
-
-Because the SGD algorithms need feature vectors of fixed length and it is a pain to build a dictionary ahead of time, most SGD applications use the encoding system that is rooted at \textit{FeatureVectorEncoder} to derive hashed feature vectors.
-The basic idea is that you create a vector, typically a \textit{RandomAccessSparseVector}, and then you use various feature encoders to progressively add features to that vector.
-The size of the vector should be large enough to avoid feature collisions as features are hashed.
-There are specialized encoders for a variety of data types.
-You can normally encode either a string representation of the value you want to encode or you can encode a byte representation to avoid string conversion.
-In the case of \textit{ContinuousValueEncoder} and \textit{ConstantValueEncoder}, it is also possible to encode a null value and pass the real value as a weight.
-
+Though SGD is an inherently sequential algorithm, it is blazingly fast. Thus Mahout's implementation can handle training sets of tens of millions of instances.
+The SGD system in Mahout is an online learning algorithm, implying that we can learn models in an incremental fashion instead of traditional batching.
+In addition, we can halt training when a model reaches target performance.
+Because the SGD algorithms need feature vectors of fixed length and it is very costly to build a dictionary ahead of time, most SGD applications use an encoding system to derive hashed feature vectors.
+We can create a \textit{RandomAccessSparseVector}, and then use various feature encoders to progressively add features to this vector.
 In our implementation, we use \textit{RandomAccessSparseVector} for data sparsity and the function call by \textit{OnlineLogisticRegression} to train the LR classifier.
-We also perform cross validation. However, to keep consistent with other methods, we write our own code to do cross validation.
+We also perform cross validation.
+However, to maintain consistency with other methods for a fair comparison, we write our own code to ensure the same cross validation scheme is applied to all algorithms being evaluated.
 
 \section{Experimental Setup} \label{sec:setup}
-This section presents the details of the dataset information, cluster information, and the test programs of our experiments.
+This section presents the details of the dataset information and testing environment of our experiments.
 
@@
 \hline
-\end{tabular}\vspace{-0.3cm}
+\end{tabular}
+％\vspace{-0.3cm}
 \end{table*}
-These five datasets are carefully selected.
-The simulated \textbf{2d} dataset can be viewed as visual result and serves for the initial test of correctness of classifiers.
+These five datasets are carefully selected with an incremental trend in size.
+The simulated \textbf{2d} dataset represents toy data situations and serves for the initial test of correctness of classifiers.
 The \textbf{20NewsGroup} dataset is best-known for the test of LR model, which has a balanced distribution between positive and negative data instances.
-The \textbf{Gisette} dataset~\cite{guyon2004result} is relatively larger, and feature vectors are less sparse. Thus it requires more computation theoretically.
+It also shows the application towards topic classification.
+The \textbf{Gisette} dataset~\cite{guyon2004result} is relatively larger, and feature vectors are less sparse.
 The \textbf{ECUESpam} dataset~\cite{DelanyKBS05} is selected due to its imbalanced distribution between positive and negative data instances.
@@
 Finally, the \textbf{URL-Reputation} dataset~\cite{ma2009identifying} contains millions of data instances and features.
-The raw data are stored in the svmlight format, which has the volume of more than 2GB.
+The raw data are stored in the SVM-light format, which has the volume of more than 2GB.
 It can be seen as a representative of massive datasets in the sense that it exceeds the scalability of Liblinear, which will be shown below.
 
-\subsection{Cluster Information}
-The cluster that we implement on has the configurations shown in Table~\ref{tab:table2}.
+\subsection{Testing Environment}
+There are all together 6 test programs for comparison.
+Online stochastic gradient descent method is run on Mahout in the sequential mode.
+Liblinear~\cite{fan2008liblinear} is also a baseline test program we choose. It is sequential and outperforms many other programs for LR on a single machine.
+SLLR performs the sequential sublinear algorithm on a single machine.
+PSUBPLR-MR performs the parallel sublinear algorithm on Hadoop.
+PGDPLR-SPARK is the test program for the parallel gradient descent run on Spark.
+PSUBPLR-SPARK implements the parallel sublinear algorithm run on Spark.
+
+We run our test programs on a six-node cluster, confiured as shown in Table~\ref{tab:table2}.
+This computing cluster is considered small in size.
+Nevertheless, past works (documented in \cite{chang2011foundations} and~\cite{Bekkerman2012}) in parallelization show that this configuration suffices to tell the trend of scalability.
+Our future work will use a  larger cluster to run on much larger scale datasets in production settings to validate our conjecture.
+
 \begin{table}[h]
@@
 \end{table}
-This kind of cluster configuration is now more and more common in research labs. Hence our results reported in the following can have a real impact in the research community.
-
-\subsection{Test Programs}
-There are all together 6 test programs for comparison.
-Online stochastic gradient descent method is run on Mahout in a sequential mode.
-Liblinear~\cite{fan2008liblinear} is the baseline test program we choose. It is sequential and outperforms many other programs for LR on a single machine.
-SLLR performs the sequential sublinear algorithm on a single machine.
-PSUBPLR-MR performs the parallel sublinear algorithm on Hadoop on cluster.
-PGDPLR-SPARK is the test program for the parallel gradient descent run on Spark.
-PSUBPLR-SPARK implements the parallel sublinear algorithm run on Spark.
 
 \section{Experimental Results} \label{sec:experiment}
-In this section, we conduct empirical analysis on experimental results.
-We show three things: 1) correctness of our test program, 2) accuracy comparison, and 3) speedup comparison.
-
-\subsection{Results on Simulated 2d Dataset}
-%
-\begin{figure}[tb]
-\center \includegraphics[height=4cm,width=5.14cm]{img/2d-show.eps}\vspace{-0.3cm}
-\caption{Visual result on simulated \textbf{2d} dataset}\label{fig:02}\vspace{-0.5cm}
-\end{figure}
-%
-Fig.~\ref{fig:02} shows the visual result for the simulated \textbf{2d} dataset.
-Here we use all data for training and testing, thus "Test Error" here can be interpreted as "Training Error".
-The green line shows the result for all sublinear methods, including SLLR, PSUBPLR-MR and PSUBPLR-SPARK.
-The results on the simulated \textbf{2d} dataset proves the correctness of all test programs.
+This section conducts analysis on experimental results.
+We report and analyze results in 1) accuracy, 2) efficiency, 3) scalability and 4) robustness.
 
@@
 %
-These are the averaged results of cross validation.
+These are the average results of running cross validation. Note that Liblinear cannot be implemented with the full \textbf{URL-Reputation} dataset on our machines due to memory limitation.
 In Figures~\ref{fig:accuracy} (a)-(d), we show the test error as a function of iteration number on each dataset for all six test programs.
-Note that Liblinear cannot be implemented with the full \textbf{URL-Reputation} dataset on our machine due to memory limit.
-This proves the scalability issue of Liblinear.
-In the tests, Liblinear can handle $33.3\%$ of the whole data volume at most, with the test accuracy of $96.2\%$ and the running time of 519s.
+
 %
@@
    \end{tabular}
-\end{center}\vspace{-0.3cm}
+\end{center}
+％\vspace{-0.3cm}
    \caption{Test error, as a function of iteration number.}\vspace{-0.5cm}
@@
 The running time of six test programs used on five datasets is shown in Table~\ref{tab:table4}.
-These are the averaged results corresponding to the accuracies we achieved in Table~\ref{tab:table3}.
+The reported running time is the average of our corss-validation executions. Fig.~\ref{fig:08} reports the same results graphically.
 %
@@
 
-In another way, we show the running time results in Fig.~\ref{fig:08} for comparison.
 \begin{figure}[tb]
-\center \includegraphics[height=4.5cm,width=9cm]{img/all_time.eps}\vspace{-0.3cm}
-\caption{Running time.}\label{fig:08}\vspace{-0.5cm}
+\center \includegraphics[height=4.8cm,width=9cm]{img/all_time.eps}
+\vspace{-0.3cm}
+\caption{Running time.}\label{fig:08}
+\vspace{-0.2cm}
 \end{figure}
 
-From the accuracy results in Section~\ref{sec:precision} and the running time results in Section~\ref{sec:time}.
-We can come up with following conclusions.
+\noindent
+\underline{\bf Observations}
 
-1) Liblinear performs best. It fully utilizes memory and the single machine implementation does not require any communication between machines.
-          However, its scalability is limited by the memory size of the single machine that it runs on, which prevents its use for massive datasets.
-          Nevertheless, if the dataset can be fully loaded into the memory of a single machine, this efficient and direct sequential way of implementation is still recommended.
+From the above results, we reach the following conclusions.
 
-2) Mahout's precision is not good, especially for those datasets in which positive and negative instances are imbalanced.
+\begin{enumerate}
+\item Liblinear performs best. It fully utilizes memory, and the single machine implementation does not require any communication between machines.
+          However, its scalability is limited by the memory size of the single machine that it runs on.
+          Nevertheless, if the dataset can be fully loaded into the memory of a single machine, this efficient and direct sequential way of implementation is highly recommended for both fast speed and high accuracy.
+
+\item Mahout's precision is not good, especially on those datasets where positive and negative instances are imbalanced.
           However, it is a representative example of sequential algorithm that can train massive data in acceptable time.
-          When we monitor its memory when running, it is much lower than Liblinear. This is the advantage brought by both online algorithm and hashing operations on features.
-          Therefore, it provides good scalability guarantee. If you are in the situation of single machine and limited memory, sequential online training like Mahout is recommended.
+          We monitor the memory when running Mahout and find that its memory use is much lower than Liblinear.
+This is the advantage brought by both online algorithm and hashing operations on features.
+          Therefore, Mahout offers good scalability guarantee. When only single machine with limited memory is available, sequential online training like Mahout is recommended.
 
-3) The precision of all sublinear methods is acceptable. The developed parallel sublinear algorithm only has a small drop in precision.
+\item The precision of all sublinear methods is acceptable. The developed parallel sublinear algorithm only has a small drop in precision.
 
-4) Hadoop system has a drawback for running LR optimization methods. Its cluster programming model is based on acyclic data flow from stable storage to stable storage.
-          Though it has the benefits of deciding where to run tasks and can automatically recover from failures in runtime, acyclic data flow is inefficient for iterative algorithms.
-          All six test programs contain a number of iterations, thus making PSUBPLR-MR performs poorly, even worse than sequential algorithms.
-          When we study the details of Hadoop implementation, we find that the MapReduce job starting time in PSUBPLR-MR is about 20s.
-It consists of task configuration time and parameter passing time.
-          This running time overhead is not negligible, especially when dataset is relatively small.
-          We also identify that the running of "Primal-Map" dominates the whole iteration time (more than 66\%). It is the same situation for PSUBPLR-SPARK.
+\item  Hadoop system suffers from a drawback for running LR optimization methods. Its cluster programming model is based on an acyclic data flow from a stable storage to a stable storage.
+          Though it has the benefits of deciding where to run tasks and can automatically recover from failures in runtime, the acyclic data flow is inefficient for iterative algorithms.
+          All six test programs involve a number of iterations, thus making PSUBPLR-MR perform poorly, worse than sequential algorithms.
+          When we study the details of Hadoop implementation, we find that the starting time of MapReduce job in PSUBPLR-MR is about 20s, including time for task configuration and parameter passing.
+          This running time overhead is not negligible, especially when a dataset is relatively small.
+          We also identify that the running of ``Primal-Map" dominates one iteration time (more than 66\%). It is the same situation for PSUBPLR-SPARK.
 
-5) Spark employs the ``all-in-memory" strategy, and it constructs RDD on demand. We implement PGDPLR-SPARK and PSUBPLR-SPARK in normal file system instead of HDFS.
+\item Spark employs the ``all-in-memory" strategy, and it constructs RDD on demand. We implement PGDPLR-SPARK and PSUBPLR-SPARK in the normal file system instead of HDFS.
           Current results on Spark show that it is much more efficient than Hadoop, and performs better than Mahout.
-          In the parallel situation, we recommend Spark to process massive data. Further, we recommend to choose PSUBPLR-SPARK for less running time in exchange for a little bit precision loss.
-          As the platform is still under developing process, we expect that our running time results for PGDPLR-SPARK and PSUBPLR-SPARK can still be improved.
+          As a distributed platform, we recommend Spark to process massive data. Further, we recommend to choose PSUBPLR-SPARK for shorter running time in exchange for a slight precision degradation.
+          As the Spark platform is still under development, we expect that our running time results for PGDPLR-SPARK and PSUBPLR-SPARK can still be improved.
 
-6) Another interesting point we would like to raise is about dataset. If we compare \textbf{ECUESpam} dataset and \textbf{GISETTE} dataset.
-          The former has higher data dimensionality but more sparse.
-          We can find that algorithms on \textbf{ECUESpam} dataset enjoy less running time per iteration than on \textbf{GISETTE} dataset as \textbf{ECUESpam} has fewer nonzero values involved in the computation.
-          However, algorithms on \textbf{ECUESpam} dataset need more iterations than on \textbf{GISETTE} dataset, which is related to higher data dimensionality of \textbf{ECUESpam} dataset.
-This even causes more running time in total.
-          To sum up, to get a general sense of running time for individual dataset, we need to consider both data volume and sparsity.
+\item Another interesting point we would like to raise is about dataset size versus sparsity.
+When comparing \textbf{ECUESpam} dataset and \textbf{GISETTE} dataset, the former has higher data dimensionality but it is more sparse.
+          Comparing the data point between Figures~\ref{fig:time} (b) and (c), we can find that algorithms on \textbf{ECUESpam} dataset enjoy shorter running time per iteration than on \textbf{GISETTE} dataset as \textbf{ECUESpam} has fewer nonzero values involved in the computation.
+          However, algorithms on \textbf{ECUESpam} dataset require more iterations than on \textbf{GISETTE} dataset, which is because of higher data dimensionality of \textbf{ECUESpam} dataset.
+This high dimensionality even causes \textbf{ECUESpam} to take longer execution time in total.
+          In summary, to get a general sense of running time for a dataset, we must consider both data volume and sparsity.
+\end{enumerate}
 
-\subsection{Results on Changing Cluster}
-In Figures~\ref{fig:time} (a)-(d), we show the running time as a function of used node number on each dataset for all three parallel test programs.
+\subsection{Results on Cluster Size}
+In Figures~\ref{fig:time} (a)-(d), we show the running time as a function of number of nodes.
 %
@@
 %
-As we can see from the results, fewer computation resources provided, longer the implementation process will take.
-However, this trend is not in a consistent fashion. When the number of machines gets higher, it will make the less impact.
-We may reach a point for every algorithm when running time halts to decrease as machine number increases.
-This shows the true scalability of the designed algorithm, which we can study in our future work.
+It is evident, as prior work (e.g., \cite{chang2011psvm}), has pointed out, that due to IO and communication overheads, the benefit of adding more nodes would eventually be wahed out.
+Though we have only employed six nodes in this study, the figures already indicate speedup slows down when more nodes are used.
+Therefore, to deal with big data, future work should pay more attention on reducing IO and communication overheads.
 
@@
 Here, randomization is employed in all sublinear methods, thus providing algorithm level fault tolerance for PSUBPLR-MR and PSUBPLR-SPARK.
-Hadoop and Spark can both provide system level fault tolerance, but in different ways. Hadoop employs HDFS while Spark has RDDs.
+Hadoop and Spark can both provide system level fault tolerance, but in different ways. Hadoop employs HDFS, whereas Spark has RDDs.
 Of all six test programs, PSUBPLR-MR and PSUBPLR-SPARK are fault-tolerant in both system level and algorithm level.
 
-We show the iteration time as a function of percentage of failed maps on \textbf{URL-Reputation} dataset for all three parallel test programs in Fig.~\ref{fig:14}.
-This is tested on 6 nodes.
+Fig.~\ref{fig:14} shows the iteration time as a function of percentage of failed maps on \textbf{URL-Reputation} dataset for all three parallel test programs running on six nodes.
+The number of iterations of PSUBPLR-MR remains unaffected when {\em maps} fail.
+Both PGDPLR-SPARK and PSUBPLR-SPARK increase number of iterations when {\em maps} fail,  because of RDD reconstruction. However, the increase is not significant.
+In general, Hadoop spends more overhead than Spark to support fault tolerance, and hence Hadoop enjoys less impact during failure recovery.
+
 \begin{figure}[tb]
@@
 \end{figure}
-As Fig.~\ref{fig:14} shows, iteration time of PSUBPLR-MR remains unaffected when maps fail. But it takes the cost of precision loss if we enforce that no additional iterations are implemented.
-PGDPLR-SPARK and PSUBPLR-SPARK will increase iteration time when the maps fail. It is due to RDD reconstruction. The increase is not significant.
-This difference also reveals the different mechanism of fault tolerance between Hadoop and Spark.
 
 \section{Conclusion} \label{sec:concl}
-In this paper we analyzed three optimization approaches along with three computing platforms to train LR model on large-scale, high-dimensional datasets for classification.
-In addition, we presented a novel parallel sublinear algorithm for LR implemented on both Hadoop and Spark.
-Based on extensive experiments, we summarized key features of each algorithm implemented on different computing platforms.
+In this paper we analyzed three optimization approaches along with two computing platforms to train the LR model on large-scale, high-dimensional datasets for classification.
+Based on extensive experiments, we summarized key features of each algorithm implemented on Hadoop and Spark.
 We can conclude that sequential algorithms with memory intensive operations like Liblinear can perform very well if datasets can fit in memory.
 For massive datasets, if limited by machine resources, Mahout with its online algorithm is a good choice with a slightly lower precision.
-If machine resources are abundant, as Spark outperforms Hadoop for LR model training, we recommend to choose between parallel sublinear method and parallel gradient descent method (both implemented in Spark) to trade off between speedup and precision.
-Our future work will focus on combining algorithm design and computing platforms to optimize classifiers in machine learning.
+If machine resources are abundant, as Spark outperforms Hadoop for LR model training, we recommend choosing between parallel sublinear method and parallel gradient descent method (both on Spark) to trade off between speedup and precision.
+
+Though we used only a six-node cluster to conduct experiments, our conclusions are expected to hold for larger datasets and more computing nodes.
+We will validate this conjecture when we evaluate these algorithms in a production setting with a substantial larger cluster to deal with much larger application datasets.
 
